---
title: "Data_Analysis_H3_H4"
author: "Susanne_Rehorst"
date: "3-6-2022"
output: html_document
---

# Data Analysis H3 & H4
In the documents Data_Processing_Regulations.Rmd and Data_Processing_Metrics.Rmd, the data was cleaned and processed. In this markdown, analysis will be performed on this processed data for Hypothesis 3 (Document similarity) and Hypothesis 4 (Keyword analysis).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load or install packages:
```{r warning=FALSE}
library(dplyr)
library(stringr)
library(stargazer)
```

Set Working Directory
```{r}
setwd("~/Thesis")
```

## Load in the data
There are 3 data files used for this analysis. The first one is Descriptive_Data.RData, which contains the meta data for each regulation document and descriptive statistics, like the amount of words and the readability of the regulation document. The second data file that is used is Processed_Data.RData. This data file contains the regulation data, split into tokens. The third data file that is used is Metrics_Data.RData. This file contains the text describing ESG metrics. This data is in a tokenized data format. The metrics data is used to benchmark the content of the regulations document (measuring how many ESG topics are covered by the regulations).  
```{r}
load("Descriptive_Data.RData")
load("Processed_Data.RData")
load("Metrics_Data.RData")
```

# Hypothesis 3: Document Similarity
The first hypothesis that is covered in this document is Hypothesis 3. This involves measuring document similarity and comparing this similarity between mandatory and voluntary regulation documents.

## Merging on group level
In order to correctly compare regulations documents, the documents are first merged in groups. Documents are merged into the same group if they apply to the same region, have the same compliance level (both mandatory or both voluntary), and refer to each other (either because a document amends another, or indirectly if one regulatory document refers to the other). Categorizing documents on a group level is done manually. The Descriptive Data contains both the Document ID and the Group ID, and is merged with the Processed Data by Document ID (the Metrics Data will be used later on for Hypothesis 4).
```{r}
# Create subset of descriptive data to get meta data for groups
Group_Data <- Descriptive_Data[,c("DOC_ID", "ESG_LISTING_RULE","GROUP_ID","GROUP_TYPE","REGION","M")]

# Transform to factor
Group_Data <- lapply(Group_Data, as.character)
Group_Data <- lapply(Group_Data, factor)
Group_Data <- data.frame(Group_Data)
Processed_Data$doc_id <- as.factor(Processed_Data$doc_id)

# Merge data sets
Processed_Data <- merge(Processed_Data,Group_Data,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)

# Reduce group data to group level instead of document level
Group_Data <- Group_Data[,c("ESG_LISTING_RULE","GROUP_ID","GROUP_TYPE","REGION","M")]
Group_Data <- Group_Data %>% distinct(GROUP_ID, .keep_all = TRUE)

# Final removal of special characters within lemma (as an additional check)
Processed_Data$lemma <- gsub('[\'’]','', Processed_Data$lemma)
Processed_Data$lemma <- gsub("[^A-Za-z]","", Processed_Data$lemma)
Processed_Data$lemma <- as.factor(Processed_Data$lemma)
Processed_Data <- Processed_Data[!(is.na(Processed_Data$lemma) | Processed_Data$lemma==""), ]
```

## Prepare sub-samples
Sub-samples need to be created, as document similarity can only be calculated between documents that belong to the same group. These groups are ESG Mandatory, ESG Voluntary, E Voluntary, and G Mandatory. For all 4 groups, an additional corpus is created that adds text of a document with E, S,and/or G key metrics, depending on the group. This allows to calculate the average similarity between a group and documents with ESG key metrics. After similarities are calculated, average similarities are compared across groups and tested for significance.  
```{r}
# Subsets (1 is without ESG metrics, and 2 is with ESG metrics)
# ESG Mandatory 
ESG_Mandatory_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="ESG" & Processed_Data$M=="1" | Processed_Data$GROUP_ID=="42" 
                                  | Processed_Data$GROUP_ID=="43" | Processed_Data$GROUP_ID=="44", ] 
ESG_Mandatory_1 <- ESG_Mandatory_2[ESG_Mandatory_2$GROUP_ID!="42" & ESG_Mandatory_2$GROUP_ID!="43" & ESG_Mandatory_2$GROUP_ID!="44", ]
  
# G Mandatory
G_Mandatory_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="G" & Processed_Data$M=="1" | Processed_Data$GROUP_ID=="42", ] 
G_Mandatory_1 <- G_Mandatory_2[G_Mandatory_2$GROUP_ID!="42", ]

# ESG Voluntary
ESG_Voluntary_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="ESG" & Processed_Data$M=="0" | Processed_Data$GROUP_ID=="42" 
                                  | Processed_Data$GROUP_ID=="43" | Processed_Data$GROUP_ID=="44", ] 
ESG_Voluntary_1 <- ESG_Voluntary_2[ESG_Voluntary_2$GROUP_ID!="42" & ESG_Voluntary_2$GROUP_ID!="43" & ESG_Voluntary_2$GROUP_ID!="44", ]
  
# E Voluntary
E_Voluntary_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="E" & Processed_Data$M=="0" | Processed_Data$GROUP_ID=="43", ] 
E_Voluntary_1 <- E_Voluntary_2[E_Voluntary_2$GROUP_ID!="43", ]

# ESG Mandatory + ESG Voluntary
ESG_Both1 <- rbind(ESG_Mandatory_1, ESG_Voluntary_1)
ESG_Both2 <- rbind(ESG_Mandatory_2, ESG_Voluntary_2)

# Sample for Hypothesis 4 (includes all documents except the ESG keyword documents, as ESG key word matching is done at later stage)
Total_Sample <- Processed_Data[Processed_Data$GROUP_ID!="42" & Processed_Data$GROUP_ID!="43" & Processed_Data$GROUP_ID!="44", ]

# Drop levels for completeness
Total_Sample <- droplevels(Total_Sample)
ESG_Mandatory_1 <- droplevels(ESG_Mandatory_1)
ESG_Mandatory_2 <- droplevels(ESG_Mandatory_2)
G_Mandatory_1 <- droplevels(G_Mandatory_1)
G_Mandatory_2 <- droplevels(G_Mandatory_2)
ESG_Voluntary_1 <- droplevels(ESG_Voluntary_1)
ESG_Voluntary_2 <- droplevels(ESG_Voluntary_2)
E_Voluntary_1 <- droplevels(E_Voluntary_1)
E_Voluntary_2 <- droplevels(E_Voluntary_2)
ESG_Both1 <- droplevels(ESG_Both1)
ESG_Both2 <- droplevels(ESG_Both2)
```

## Local and Global weighting function
First, it is counted within each group, how many times a term occurs. Several local weighting functions are calculated, including Term frequency (TF), Total term frequency (Total_TF), Maximum term frequency (Max_TF), Relative term frequency (R_TF), Augmented term frequency (A_TF), and log term frequency (L_TF). In the first part of hypothesis 1(Quantity), it was concluded that there is a wide variation in the length of documents. To control for different lengths of documents, normalization should be applied. This can be in the form of relative, log, or augmented form. Subsequently, a global weight factor is calculated. This results in words that appear very frequently in all of the documents to get a lower weight. Note: Log2 is used for all log transformations instead of log10 as the range of data is within 0 and 3 powers of 10.  
```{r}
ESG_Mandatory_1 <- ESG_Mandatory_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Mandatory_1 <- ESG_Mandatory_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))
                        
ESG_Mandatory_2 <- ESG_Mandatory_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Mandatory_2 <- ESG_Mandatory_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

G_Mandatory_1 <- G_Mandatory_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
G_Mandatory_1 <- G_Mandatory_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

G_Mandatory_2 <- G_Mandatory_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
G_Mandatory_2 <- G_Mandatory_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Voluntary_1 <- ESG_Voluntary_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Voluntary_1 <- ESG_Voluntary_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Voluntary_2 <- ESG_Voluntary_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Voluntary_2 <- ESG_Voluntary_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

E_Voluntary_1 <- E_Voluntary_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
E_Voluntary_1 <- E_Voluntary_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

E_Voluntary_2 <- E_Voluntary_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
E_Voluntary_2 <- E_Voluntary_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Both1 <- ESG_Both1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

ESG_Both1 <- ESG_Both1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Both2 <- ESG_Both2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

ESG_Both2 <- ESG_Both2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

Total_Sample <- Total_Sample %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

Total_Sample <- Total_Sample %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

```

## Document Term Matrix
A document term matrix is created. There are 6 different weighting schemes used. This is done as a robustness check, to see the influence of using different weighting schemes on the results. Weighting schemes 0 and 1 are only locally weighted (TF and Log TF). Schemes 2, 3, and 4 are the product of local weight with global weight (with global weight being IDF). Scheme 5 and 6 multiply log TF with entropy as global weight. Entropy is calculated as real entropy (scheme 5) and entropy+1 (scheme 6). Missing values in the matrix indicate that a certain term does not appear in a document. These missing values are replaced with 0, except for the augmented weighting scheme because this schema uses 0.5 as base value. 
```{r}
library(reshape2)
library(lsa)
# ESG Mandatory 1
ESG_M_1_0 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var ="TF")
ESG_M_1_1 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="L_TF")
ESG_M_1_2 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_M_1_3 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_M_1_4 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_M_1_0[is.na(ESG_M_1_0)] <- 0
ESG_M_1_1[is.na(ESG_M_1_1)] <- 0
ESG_M_1_2[is.na(ESG_M_1_2)] <- 0
ESG_M_1_3[is.na(ESG_M_1_3)] <- 0
ESG_M_1_4[is.na(ESG_M_1_4)] <- 0.5

ESG_M_1_5 <- lw_tf(ESG_M_1_1)*entropy(ESG_M_1_0)
ESG_M_1_6 <- lw_tf(ESG_M_1_1)*gw_entropy(ESG_M_1_0)

ESG_M_1_5[is.na(ESG_M_1_5)] <- 0
ESG_M_1_6[is.na(ESG_M_1_6)] <- 0

# ESG Mandatory 2
ESG_M_2_0 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var ="TF")
ESG_M_2_1 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="L_TF")
ESG_M_2_2 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_M_2_3 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_M_2_4 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_M_2_0[is.na(ESG_M_2_0)] <- 0
ESG_M_2_1[is.na(ESG_M_2_1)] <- 0
ESG_M_2_2[is.na(ESG_M_2_2)] <- 0
ESG_M_2_3[is.na(ESG_M_2_3)] <- 0
ESG_M_2_4[is.na(ESG_M_2_4)] <- 0.5

ESG_M_2_5 <- lw_tf(ESG_M_2_1)*entropy(ESG_M_2_0)
ESG_M_2_6 <- lw_tf(ESG_M_2_1)*gw_entropy(ESG_M_2_0)

ESG_M_2_5[is.na(ESG_M_2_5)] <- 0
ESG_M_2_6[is.na(ESG_M_2_6)] <- 0

# ESG Voluntary 1
ESG_V_1_0 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var ="TF")
ESG_V_1_1 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="L_TF")
ESG_V_1_2 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_V_1_3 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_V_1_4 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_V_1_0[is.na(ESG_V_1_0)] <- 0
ESG_V_1_1[is.na(ESG_V_1_1)] <- 0
ESG_V_1_2[is.na(ESG_V_1_2)] <- 0
ESG_V_1_3[is.na(ESG_V_1_3)] <- 0
ESG_V_1_4[is.na(ESG_V_1_4)] <- 0.5

ESG_V_1_5 <- lw_tf(ESG_V_1_1)*entropy(ESG_V_1_0)
ESG_V_1_6 <- lw_tf(ESG_V_1_1)*gw_entropy(ESG_V_1_0)

ESG_V_1_5[is.na(ESG_V_1_5)] <- 0
ESG_V_1_6[is.na(ESG_V_1_6)] <- 0

# ESG Voluntary 2
ESG_V_2_0 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var ="TF")
ESG_V_2_1 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="L_TF")
ESG_V_2_2 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_V_2_3 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_V_2_4 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_V_2_0[is.na(ESG_V_2_0)] <- 0
ESG_V_2_1[is.na(ESG_V_2_1)] <- 0
ESG_V_2_2[is.na(ESG_V_2_2)] <- 0
ESG_V_2_3[is.na(ESG_V_2_3)] <- 0
ESG_V_2_4[is.na(ESG_V_2_4)] <- 0.5

ESG_V_2_5 <- lw_tf(ESG_V_2_1)*entropy(ESG_V_2_0)
ESG_V_2_6 <- lw_tf(ESG_V_2_1)*gw_entropy(ESG_V_2_0)

ESG_V_2_5[is.na(ESG_V_2_5)] <- 0
ESG_V_2_6[is.na(ESG_V_2_6)] <- 0

# G Mandatory 1
G_M_1_0 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var ="TF")
G_M_1_1 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="L_TF")
G_M_1_2 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
G_M_1_3 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="R_TFIDF")
G_M_1_4 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="A_TFIDF")

G_M_1_0[is.na(G_M_1_0)] <- 0
G_M_1_1[is.na(G_M_1_1)] <- 0
G_M_1_2[is.na(G_M_1_2)] <- 0
G_M_1_3[is.na(G_M_1_3)] <- 0
G_M_1_4[is.na(G_M_1_4)] <- 0.5

G_M_1_5 <- lw_tf(G_M_1_1)*entropy(G_M_1_0)
G_M_1_6 <- lw_tf(G_M_1_1)*gw_entropy(G_M_1_0)

G_M_1_5[is.na(G_M_1_5)] <- 0
G_M_1_6[is.na(G_M_1_6)] <- 0

# G Mandatory 2
G_M_2_0 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var ="TF")
G_M_2_1 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="L_TF")
G_M_2_2 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
G_M_2_3 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="R_TFIDF")
G_M_2_4 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="A_TFIDF")

G_M_2_0[is.na(G_M_2_0)] <- 0
G_M_2_1[is.na(G_M_2_1)] <- 0
G_M_2_2[is.na(G_M_2_2)] <- 0
G_M_2_3[is.na(G_M_2_3)] <- 0
G_M_2_4[is.na(G_M_2_4)] <- 0.5

G_M_2_5 <- lw_tf(G_M_2_1)*entropy(G_M_2_0)
G_M_2_6 <- lw_tf(G_M_2_1)*gw_entropy(G_M_2_0)

G_M_2_5[is.na(G_M_2_5)] <- 0
G_M_2_6[is.na(G_M_2_6)] <- 0

# E Voluntary 1
E_V_1_0 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var ="TF")
E_V_1_1 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="L_TF")
E_V_1_2 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
E_V_1_3 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="R_TFIDF")
E_V_1_4 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="A_TFIDF")

E_V_1_0[is.na(E_V_1_0)] <- 0
E_V_1_1[is.na(E_V_1_1)] <- 0
E_V_1_2[is.na(E_V_1_2)] <- 0
E_V_1_3[is.na(E_V_1_3)] <- 0
E_V_1_4[is.na(E_V_1_4)] <- 0.5

E_V_1_5 <- lw_tf(E_V_1_1)*entropy(E_V_1_0)
E_V_1_6 <- lw_tf(E_V_1_1)*gw_entropy(E_V_1_0)

E_V_1_5[is.na(E_V_1_5)] <- 0
E_V_1_6[is.na(E_V_1_6)] <- 0

# E Voluntary 2
E_V_2_0 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var ="TF")
E_V_2_1 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="L_TF")
E_V_2_2 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
E_V_2_3 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="R_TFIDF")
E_V_2_4 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="A_TFIDF")

E_V_2_0[is.na(E_V_2_0)] <- 0
E_V_2_1[is.na(E_V_2_1)] <- 0
E_V_2_2[is.na(E_V_2_2)] <- 0
E_V_2_3[is.na(E_V_2_3)] <- 0
E_V_2_4[is.na(E_V_2_4)] <- 0.5

E_V_2_5 <- lw_tf(E_V_2_1)*entropy(E_V_2_0)
E_V_2_6 <- lw_tf(E_V_2_1)*gw_entropy(E_V_2_0)

E_V_2_5[is.na(E_V_2_5)] <- 0
E_V_2_6[is.na(E_V_2_6)] <- 0

# ESG Both 1
ESG_B_1_0 <- acast(ESG_Both1, lemma~GROUP_ID, value.var ="TF")
ESG_B_1_1 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="L_TF")
ESG_B_1_2 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_B_1_3 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_B_1_4 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_B_1_0[is.na(ESG_B_1_0)] <- 0
ESG_B_1_1[is.na(ESG_B_1_1)] <- 0
ESG_B_1_2[is.na(ESG_B_1_2)] <- 0
ESG_B_1_3[is.na(ESG_B_1_3)] <- 0
ESG_B_1_4[is.na(ESG_B_1_4)] <- 0.5

ESG_B_1_5 <- lw_tf(ESG_B_1_1)*entropy(ESG_B_1_0)
ESG_B_1_6 <- lw_tf(ESG_B_1_1)*gw_entropy(ESG_B_1_0)

ESG_B_1_5[is.na(ESG_B_1_5)] <- 0
ESG_B_1_6[is.na(ESG_B_1_6)] <- 0

# ESG Both 2
ESG_B_2_0 <- acast(ESG_Both2, lemma~GROUP_ID, value.var ="TF")
ESG_B_2_1 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="L_TF")
ESG_B_2_2 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_B_2_3 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_B_2_4 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="A_TFIDF")

ESG_B_2_0[is.na(ESG_B_2_0)] <- 0
ESG_B_2_1[is.na(ESG_B_2_1)] <- 0
ESG_B_2_2[is.na(ESG_B_2_2)] <- 0
ESG_B_2_3[is.na(ESG_B_2_3)] <- 0
ESG_B_2_4[is.na(ESG_B_2_4)] <- 0.5

ESG_B_2_5 <- lw_tf(ESG_B_2_1)*entropy(ESG_B_2_0)
ESG_B_2_6 <- lw_tf(ESG_B_2_1)*gw_entropy(ESG_B_2_0)

ESG_B_2_5[is.na(ESG_B_2_5)] <- 0
ESG_B_2_6[is.na(ESG_B_2_6)] <- 0
```

# Cosine similarity Matrix
Now, the cosine similarity is calculated between the documents in each matrix. Cosine similarity ranges between 0 and 1. Value of 1 indicates a perfect similar document. And the more towards 0, the more dissimilar the documents are. 
```{r}
# ESG Mandatory 1
ESG_MS1 <- cosine(ESG_M_1_1)
ESG_MS2 <- cosine(ESG_M_1_2)
ESG_MS3 <- cosine(ESG_M_1_3)
ESG_MS4 <- cosine(ESG_M_1_4)
ESG_MS5 <- cosine(ESG_M_1_5)
ESG_MS6 <- cosine(ESG_M_1_6)

# ESG Mandatory 2
ESG_MS12 <- cosine(ESG_M_2_1)
ESG_MS22 <- cosine(ESG_M_2_2)
ESG_MS32 <- cosine(ESG_M_2_3)
ESG_MS42 <- cosine(ESG_M_2_4)
ESG_MS52 <- cosine(ESG_M_2_5)
ESG_MS62 <- cosine(ESG_M_2_6)

# ESG Voluntary 1
ESG_VS1 <- cosine(ESG_V_1_1)
ESG_VS2 <- cosine(ESG_V_1_2)
ESG_VS3 <- cosine(ESG_V_1_3)
ESG_VS4 <- cosine(ESG_V_1_4)
ESG_VS5 <- cosine(ESG_V_1_5)
ESG_VS6 <- cosine(ESG_V_1_6)

# ESG Voluntary 2
ESG_VS12 <- cosine(ESG_V_2_1)
ESG_VS22 <- cosine(ESG_V_2_2)
ESG_VS32 <- cosine(ESG_V_2_3)
ESG_VS42 <- cosine(ESG_V_2_4)
ESG_VS52 <- cosine(ESG_V_2_5)
ESG_VS62 <- cosine(ESG_V_2_6)

# G Mandatory 1
G_MS1 <- cosine(G_M_1_1)
G_MS2 <- cosine(G_M_1_2)
G_MS3 <- cosine(G_M_1_3)
G_MS4 <- cosine(G_M_1_4)
G_MS5 <- cosine(G_M_1_5)
G_MS6 <- cosine(G_M_1_6)

# G Mandatory 2
G_MS12 <- cosine(G_M_2_1)
G_MS22 <- cosine(G_M_2_2)
G_MS32 <- cosine(G_M_2_3)
G_MS42 <- cosine(G_M_2_4)
G_MS52 <- cosine(G_M_2_5)
G_MS62 <- cosine(G_M_2_6)

# E Voluntary 1
E_VS1 <- cosine(E_V_1_1)
E_VS2 <- cosine(E_V_1_2)
E_VS3 <- cosine(E_V_1_3)
E_VS4 <- cosine(E_V_1_4)
E_VS5 <- cosine(E_V_1_5)
E_VS6 <- cosine(E_V_1_6)

# E Voluntary 2
E_VS12 <- cosine(E_V_2_1)
E_VS22 <- cosine(E_V_2_2)
E_VS32 <- cosine(E_V_2_3)
E_VS42 <- cosine(E_V_2_4)
E_VS52 <- cosine(E_V_2_5)
E_VS62 <- cosine(E_V_2_6)

# ESG Both 1
ESG_BS1 <- cosine(ESG_B_1_1)
ESG_BS2 <- cosine(ESG_B_1_2)
ESG_BS3 <- cosine(ESG_B_1_3)
ESG_BS4 <- cosine(ESG_B_1_4)
ESG_BS5 <- cosine(ESG_B_1_5)
ESG_BS6 <- cosine(ESG_B_1_6)

# ESG Both 2
ESG_BS12 <- cosine(ESG_B_2_1)
ESG_BS22 <- cosine(ESG_B_2_2)
ESG_BS32 <- cosine(ESG_B_2_3)
ESG_BS42 <- cosine(ESG_B_2_4)
ESG_BS52 <- cosine(ESG_B_2_5)
ESG_BS62 <- cosine(ESG_B_2_6)
```

## Visualization - heat maps
The results can be visualized by showing the cosine similarity matrices as a heat map.Most important results is to compare ESG mandatory heat maps with ESG voluntary heat maps. And make them for all 6 models.  
```{r}
# Create new matrices, and change the row and colnames to region, instead of GROUP ID for better interpretation
ESG_MS1h <- ESG_MS1
ESG_MS2h <- ESG_MS2
ESG_MS3h <- ESG_MS3
ESG_MS4h <- ESG_MS4
ESG_MS5h <- ESG_MS5
ESG_MS6h <- ESG_MS6

# ESG Voluntary
ESG_VS1h <- ESG_VS1
ESG_VS2h <- ESG_VS2
ESG_VS3h <- ESG_VS3
ESG_VS4h <- ESG_VS4
ESG_VS5h <- ESG_VS5
ESG_VS6h <- ESG_VS6

# Changes column names
colnames(ESG_MS1h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS1h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
colnames(ESG_MS2h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS2h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
colnames(ESG_MS3h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS3h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
colnames(ESG_MS4h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS4h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
colnames(ESG_MS5h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS5h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
colnames(ESG_MS6h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
colnames(ESG_VS6h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")

# Change row names
rownames(ESG_MS1h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS1h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
rownames(ESG_MS2h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS2h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
rownames(ESG_MS3h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS3h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
rownames(ESG_MS4h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS4h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
rownames(ESG_MS5h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS5h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")
rownames(ESG_MS6h) <- c("Hong Kong", "India_gov", "India_SEB", "Nigeria", "Singapore", "United Kingdom", "United States_SEC", "United States_gov_p", "European Union") 
rownames(ESG_VS6h) <- c("Greece", "Hong Kong", "Hungary", "India", "Australia",  "Japan", "Luxembourg", "Nasdaq Stock Markets", "New Zealand", "Nigeria", 
                        "Poland", "Spain", "South Africa", "United Kingdom", "United States", "Chile",  "Euronext Stock Markets",  "European Union",  "Germany")

## **************************************************************************************************************************************************** ##
## reshape the data to create a heatmap
library(reshape2)
library(ggplot2)
library(ggpubr)

# function to get only half of the matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

# function to reorder the matrix
reorder_cormat <- function(cormat){
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

###################################################################
ESG_MS1h <- reorder_cormat(ESG_MS1h)
upper_ESG_MS1h <- get_upper_tri(ESG_MS1h)

melted_ESG_MS1h <- melt(upper_ESG_MS1h, na.rm = TRUE)

# Create the heat maps
heatmap1M <- ggplot(data=melted_ESG_MS1h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

####################################################################
ESG_MS2h <- reorder_cormat(ESG_MS2h)
upper_ESG_MS2h <- get_upper_tri(ESG_MS2h)

melted_ESG_MS2h <- melt(upper_ESG_MS2h, na.rm = TRUE)

# Create the heat maps
heatmap2M <- ggplot(data=melted_ESG_MS2h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

#################################################################
ESG_MS3h <- reorder_cormat(ESG_MS3h)
upper_ESG_MS3h <- get_upper_tri(ESG_MS3h)

melted_ESG_MS3h <- melt(upper_ESG_MS3h, na.rm = TRUE)

# Create the heat maps
heatmap3M <- ggplot(data=melted_ESG_MS3h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

####################################################################
ESG_MS4h <- reorder_cormat(ESG_MS4h)
upper_ESG_MS4h <- get_upper_tri(ESG_MS4h)

melted_ESG_MS4h <- melt(upper_ESG_MS4h, na.rm = TRUE)

# Create the heat maps
heatmap4M <- ggplot(data=melted_ESG_MS4h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

##################################################################
ESG_MS5h <- reorder_cormat(ESG_MS5h)
upper_ESG_MS5h <- get_upper_tri(ESG_MS5h)

melted_ESG_MS5h <- melt(upper_ESG_MS5h, na.rm = TRUE)

# Create the heat maps
heatmap5M <- ggplot(data=melted_ESG_MS5h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

################################################################
ESG_MS6h <- reorder_cormat(ESG_MS6h)
upper_ESG_MS6h <- get_upper_tri(ESG_MS6h)

melted_ESG_MS6h <- melt(upper_ESG_MS6h, na.rm = TRUE)

# Create the heat maps
heatmap6M <- ggplot(data=melted_ESG_MS6h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

###################################################################

ESG_VS1h <- reorder_cormat(ESG_VS1h)
upper_ESG_VS1h <- get_upper_tri(ESG_VS1h)

melted_ESG_VS1h <- melt(upper_ESG_VS1h, na.rm = TRUE)

# Create the heat maps
heatmap1V <- ggplot(data=melted_ESG_VS1h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

####################################################################
ESG_VS2h <- reorder_cormat(ESG_VS2h)
upper_ESG_VS2h <- get_upper_tri(ESG_VS2h)

melted_ESG_VS2h <- melt(upper_ESG_VS2h, na.rm = TRUE)

# Create the heat maps
heatmap2V <- ggplot(data=melted_ESG_VS2h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

#################################################################
ESG_VS3h <- reorder_cormat(ESG_VS3h)
upper_ESG_VS3h <- get_upper_tri(ESG_VS3h)

melted_ESG_VS3h <- melt(upper_ESG_VS3h, na.rm = TRUE)

# Create the heat maps
heatmap3V <- ggplot(data=melted_ESG_VS3h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

####################################################################
ESG_VS4h <- reorder_cormat(ESG_VS4h)
upper_ESG_VS4h <- get_upper_tri(ESG_VS4h)

melted_ESG_VS4h <- melt(upper_ESG_VS4h, na.rm = TRUE)

# Create the heat maps
heatmap4V <- ggplot(data=melted_ESG_VS4h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

##################################################################
ESG_VS5h <- reorder_cormat(ESG_VS5h)
upper_ESG_VS5h <- get_upper_tri(ESG_VS5h)

melted_ESG_VS5h <- melt(upper_ESG_VS5h, na.rm = TRUE)

# Create the heat maps
heatmap5V <- ggplot(data=melted_ESG_VS5h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

################################################################
ESG_VS6h <- reorder_cormat(ESG_VS6h)
upper_ESG_VS6h <- get_upper_tri(ESG_VS6h)

melted_ESG_VS6h <- melt(upper_ESG_VS6h, na.rm = TRUE)

# Create the heat maps
heatmap6V <- ggplot(data=melted_ESG_VS6h, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="orange")+
  labs(y= "", x = "") +
  scale_fill_gradient2(low="yellow", high="red", mid="orange",
                       midpoint=0.5, limit=c(0,1), space="Lab",
                       name="Cosine\nSimilarity") +
  theme_minimal()+theme(axis.text.x=element_text(angle=45, vjust=1,
                                                 size=12, hjust=1, family="serif"))+
  coord_fixed()

ggarrange(heatmap1M,heatmap2M,heatmap3M,heatmap4M,heatmap5M,heatmap6M)
ggarrange(heatmap1V,heatmap2V,heatmap3V,heatmap4V,heatmap5V,heatmap6V)

```

## Calculating Difference-in-Means and test for significance (within groups and compared to ESG doc)
Now that the cosine similarity between documents is calculated, the average document similarity within each of the 4 groups is calculated. The difference in average cosine similarity between the different document groups is tested on significance. For the group that also includes documents metrics, the only relevant part is the average cosine similarity between the ESG documents and the other documents. 

Before average similarity can be calculated, the matrices need to be converted back to data frames.
```{r}
# ESG Mandatory
ESGM1 <- data.frame(GROUP_ID1=rownames(ESG_MS1)[row(ESG_MS1)[upper.tri(ESG_MS1)]], 
                     GROUP_ID2=colnames(ESG_MS1)[col(ESG_MS1)[upper.tri(ESG_MS1)]],cosine=ESG_MS1[upper.tri(ESG_MS1)])
ESGM2 <- data.frame(GROUP_ID1=rownames(ESG_MS2)[row(ESG_MS2)[upper.tri(ESG_MS2)]], 
                     GROUP_ID2=colnames(ESG_MS2)[col(ESG_MS2)[upper.tri(ESG_MS2)]],cosine=ESG_MS2[upper.tri(ESG_MS2)])
ESGM3 <- data.frame(GROUP_ID1=rownames(ESG_MS3)[row(ESG_MS3)[upper.tri(ESG_MS3)]], 
                     GROUP_ID2=colnames(ESG_MS3)[col(ESG_MS3)[upper.tri(ESG_MS3)]],cosine=ESG_MS3[upper.tri(ESG_MS3)])
ESGM4 <- data.frame(GROUP_ID1=rownames(ESG_MS4)[row(ESG_MS4)[upper.tri(ESG_MS4)]], 
                     GROUP_ID2=colnames(ESG_MS4)[col(ESG_MS4)[upper.tri(ESG_MS4)]],cosine=ESG_MS4[upper.tri(ESG_MS4)])
ESGM5 <- data.frame(GROUP_ID1=rownames(ESG_MS5)[row(ESG_MS5)[upper.tri(ESG_MS5)]], 
                     GROUP_ID2=colnames(ESG_MS5)[col(ESG_MS5)[upper.tri(ESG_MS5)]],cosine=ESG_MS5[upper.tri(ESG_MS5)])
ESGM6 <- data.frame(GROUP_ID1=rownames(ESG_MS6)[row(ESG_MS6)[upper.tri(ESG_MS6)]], 
                     GROUP_ID2=colnames(ESG_MS6)[col(ESG_MS6)[upper.tri(ESG_MS6)]],cosine=ESG_MS6[upper.tri(ESG_MS6)])

ESGM12 <- data.frame(GROUP_ID1=rownames(ESG_MS12)[row(ESG_MS12)[upper.tri(ESG_MS12)]], 
                     GROUP_ID2=colnames(ESG_MS12)[col(ESG_MS12)[upper.tri(ESG_MS12)]],cosine=ESG_MS12[upper.tri(ESG_MS12)])
ESGM22 <- data.frame(GROUP_ID1=rownames(ESG_MS22)[row(ESG_MS22)[upper.tri(ESG_MS22)]], 
                     GROUP_ID2=colnames(ESG_MS22)[col(ESG_MS22)[upper.tri(ESG_MS22)]],cosine=ESG_MS22[upper.tri(ESG_MS22)])
ESGM32 <- data.frame(GROUP_ID1=rownames(ESG_MS32)[row(ESG_MS32)[upper.tri(ESG_MS32)]], 
                     GROUP_ID2=colnames(ESG_MS32)[col(ESG_MS32)[upper.tri(ESG_MS32)]],cosine=ESG_MS32[upper.tri(ESG_MS32)])
ESGM42 <- data.frame(GROUP_ID1=rownames(ESG_MS42)[row(ESG_MS42)[upper.tri(ESG_MS42)]], 
                     GROUP_ID2=colnames(ESG_MS42)[col(ESG_MS42)[upper.tri(ESG_MS42)]],cosine=ESG_MS42[upper.tri(ESG_MS42)])
ESGM52 <- data.frame(GROUP_ID1=rownames(ESG_MS52)[row(ESG_MS52)[upper.tri(ESG_MS52)]], 
                     GROUP_ID2=colnames(ESG_MS52)[col(ESG_MS52)[upper.tri(ESG_MS52)]],cosine=ESG_MS52[upper.tri(ESG_MS52)])
ESGM62 <- data.frame(GROUP_ID1=rownames(ESG_MS62)[row(ESG_MS62)[upper.tri(ESG_MS62)]], 
                     GROUP_ID2=colnames(ESG_MS62)[col(ESG_MS62)[upper.tri(ESG_MS62)]],cosine=ESG_MS62[upper.tri(ESG_MS62)])
# ESG Voluntary
ESGV1 <- data.frame(GROUP_ID1=rownames(ESG_VS1)[row(ESG_VS1)[upper.tri(ESG_VS1)]], 
                     GROUP_ID2=colnames(ESG_VS1)[col(ESG_VS1)[upper.tri(ESG_VS1)]],cosine=ESG_VS1[upper.tri(ESG_VS1)])
ESGV2 <- data.frame(GROUP_ID1=rownames(ESG_VS2)[row(ESG_VS2)[upper.tri(ESG_VS2)]], 
                     GROUP_ID2=colnames(ESG_VS2)[col(ESG_VS2)[upper.tri(ESG_VS2)]],cosine=ESG_VS2[upper.tri(ESG_VS2)])
ESGV3 <- data.frame(GROUP_ID1=rownames(ESG_VS3)[row(ESG_VS3)[upper.tri(ESG_VS3)]], 
                     GROUP_ID2=colnames(ESG_VS3)[col(ESG_VS3)[upper.tri(ESG_VS3)]],cosine=ESG_VS3[upper.tri(ESG_VS3)])
ESGV4 <- data.frame(GROUP_ID1=rownames(ESG_VS4)[row(ESG_VS4)[upper.tri(ESG_VS4)]], 
                     GROUP_ID2=colnames(ESG_VS4)[col(ESG_VS4)[upper.tri(ESG_VS4)]],cosine=ESG_VS4[upper.tri(ESG_VS4)])
ESGV5 <- data.frame(GROUP_ID1=rownames(ESG_VS5)[row(ESG_VS5)[upper.tri(ESG_VS5)]], 
                     GROUP_ID2=colnames(ESG_VS5)[col(ESG_VS5)[upper.tri(ESG_VS5)]],cosine=ESG_VS5[upper.tri(ESG_VS5)])
ESGV6 <- data.frame(GROUP_ID1=rownames(ESG_VS6)[row(ESG_VS6)[upper.tri(ESG_VS6)]], 
                     GROUP_ID2=colnames(ESG_VS6)[col(ESG_VS6)[upper.tri(ESG_VS6)]],cosine=ESG_VS6[upper.tri(ESG_VS6)])

ESGV12 <- data.frame(GROUP_ID1=rownames(ESG_VS12)[row(ESG_VS12)[upper.tri(ESG_VS12)]], 
                     GROUP_ID2=colnames(ESG_VS12)[col(ESG_VS12)[upper.tri(ESG_VS12)]],cosine=ESG_VS12[upper.tri(ESG_VS12)])
ESGV22 <- data.frame(GROUP_ID1=rownames(ESG_VS22)[row(ESG_VS22)[upper.tri(ESG_VS22)]], 
                     GROUP_ID2=colnames(ESG_VS22)[col(ESG_VS22)[upper.tri(ESG_VS22)]],cosine=ESG_VS22[upper.tri(ESG_VS22)])
ESGV32 <- data.frame(GROUP_ID1=rownames(ESG_VS32)[row(ESG_VS32)[upper.tri(ESG_VS32)]], 
                     GROUP_ID2=colnames(ESG_VS32)[col(ESG_VS32)[upper.tri(ESG_VS32)]],cosine=ESG_VS32[upper.tri(ESG_VS32)])
ESGV42 <- data.frame(GROUP_ID1=rownames(ESG_VS42)[row(ESG_VS42)[upper.tri(ESG_VS42)]], 
                     GROUP_ID2=colnames(ESG_VS42)[col(ESG_VS42)[upper.tri(ESG_VS42)]],cosine=ESG_VS42[upper.tri(ESG_VS42)])
ESGV52 <- data.frame(GROUP_ID1=rownames(ESG_VS52)[row(ESG_VS52)[upper.tri(ESG_VS52)]], 
                     GROUP_ID2=colnames(ESG_VS52)[col(ESG_VS52)[upper.tri(ESG_VS52)]],cosine=ESG_VS52[upper.tri(ESG_VS52)])
ESGV62 <- data.frame(GROUP_ID1=rownames(ESG_VS62)[row(ESG_VS62)[upper.tri(ESG_VS62)]], 
                     GROUP_ID2=colnames(ESG_VS62)[col(ESG_VS62)[upper.tri(ESG_VS62)]],cosine=ESG_VS62[upper.tri(ESG_VS62)])

# G Mandatory
GM1 <- data.frame(GROUP_ID1=rownames(G_MS1)[row(G_MS1)[upper.tri(G_MS1)]], 
                     GROUP_ID2=colnames(G_MS1)[col(G_MS1)[upper.tri(G_MS1)]],cosine=G_MS1[upper.tri(G_MS1)])
GM2 <- data.frame(GROUP_ID1=rownames(G_MS2)[row(G_MS2)[upper.tri(G_MS2)]], 
                     GROUP_ID2=colnames(G_MS2)[col(G_MS2)[upper.tri(G_MS2)]],cosine=G_MS2[upper.tri(G_MS2)])
GM3 <- data.frame(GROUP_ID1=rownames(G_MS3)[row(G_MS3)[upper.tri(G_MS3)]], 
                     GROUP_ID2=colnames(G_MS3)[col(G_MS3)[upper.tri(G_MS3)]],cosine=G_MS3[upper.tri(G_MS3)])
GM4 <- data.frame(GROUP_ID1=rownames(G_MS4)[row(G_MS4)[upper.tri(G_MS4)]], 
                     GROUP_ID2=colnames(G_MS4)[col(G_MS4)[upper.tri(G_MS4)]],cosine=G_MS4[upper.tri(G_MS4)])
GM5 <- data.frame(GROUP_ID1=rownames(G_MS5)[row(G_MS5)[upper.tri(G_MS5)]], 
                     GROUP_ID2=colnames(G_MS5)[col(G_MS5)[upper.tri(G_MS5)]],cosine=G_MS5[upper.tri(G_MS5)])
GM6 <- data.frame(GROUP_ID1=rownames(G_MS6)[row(G_MS6)[upper.tri(G_MS6)]], 
                     GROUP_ID2=colnames(G_MS6)[col(G_MS6)[upper.tri(G_MS6)]],cosine=G_MS6[upper.tri(G_MS6)])

GM12 <- data.frame(GROUP_ID1=rownames(G_MS12)[row(G_MS12)[upper.tri(G_MS12)]], 
                     GROUP_ID2=colnames(G_MS12)[col(G_MS12)[upper.tri(G_MS12)]],cosine=G_MS12[upper.tri(G_MS12)])
GM22 <- data.frame(GROUP_ID1=rownames(G_MS22)[row(G_MS22)[upper.tri(G_MS22)]], 
                     GROUP_ID2=colnames(G_MS22)[col(G_MS22)[upper.tri(G_MS22)]],cosine=G_MS22[upper.tri(G_MS22)])
GM32 <- data.frame(GROUP_ID1=rownames(G_MS32)[row(G_MS32)[upper.tri(G_MS32)]], 
                     GROUP_ID2=colnames(G_MS32)[col(G_MS32)[upper.tri(G_MS32)]],cosine=G_MS32[upper.tri(G_MS32)])
GM42 <- data.frame(GROUP_ID1=rownames(G_MS42)[row(G_MS42)[upper.tri(G_MS42)]], 
                     GROUP_ID2=colnames(G_MS42)[col(G_MS42)[upper.tri(G_MS42)]],cosine=G_MS42[upper.tri(G_MS42)])
GM52 <- data.frame(GROUP_ID1=rownames(G_MS52)[row(G_MS52)[upper.tri(G_MS52)]], 
                     GROUP_ID2=colnames(G_MS52)[col(G_MS52)[upper.tri(G_MS52)]],cosine=G_MS52[upper.tri(G_MS52)])
GM62 <- data.frame(GROUP_ID1=rownames(G_MS62)[row(G_MS62)[upper.tri(G_MS62)]], 
                     GROUP_ID2=colnames(G_MS62)[col(G_MS62)[upper.tri(G_MS62)]],cosine=G_MS62[upper.tri(G_MS62)])

# E Voluntary
EV1 <- data.frame(GROUP_ID1=rownames(E_VS1)[row(E_VS1)[upper.tri(E_VS1)]], 
                     GROUP_ID2=colnames(E_VS1)[col(E_VS1)[upper.tri(E_VS1)]],cosine=E_VS1[upper.tri(E_VS1)])
EV2 <- data.frame(GROUP_ID1=rownames(E_VS2)[row(E_VS2)[upper.tri(E_VS2)]], 
                     GROUP_ID2=colnames(E_VS2)[col(E_VS2)[upper.tri(E_VS2)]],cosine=E_VS2[upper.tri(E_VS2)])
EV3 <- data.frame(GROUP_ID1=rownames(E_VS3)[row(E_VS3)[upper.tri(E_VS3)]], 
                     GROUP_ID2=colnames(E_VS3)[col(E_VS3)[upper.tri(E_VS3)]],cosine=E_VS3[upper.tri(E_VS3)])
EV4 <- data.frame(GROUP_ID1=rownames(E_VS4)[row(E_VS4)[upper.tri(E_VS4)]], 
                     GROUP_ID2=colnames(E_VS4)[col(E_VS4)[upper.tri(E_VS4)]],cosine=E_VS4[upper.tri(E_VS4)])
EV5 <- data.frame(GROUP_ID1=rownames(E_VS5)[row(E_VS5)[upper.tri(E_VS5)]], 
                     GROUP_ID2=colnames(E_VS5)[col(E_VS5)[upper.tri(E_VS5)]],cosine=E_VS5[upper.tri(E_VS5)])
EV6 <- data.frame(GROUP_ID1=rownames(E_VS6)[row(E_VS6)[upper.tri(E_VS6)]], 
                     GROUP_ID2=colnames(E_VS6)[col(E_VS6)[upper.tri(E_VS6)]],cosine=E_VS6[upper.tri(E_VS6)])

EV12 <- data.frame(GROUP_ID1=rownames(E_VS12)[row(E_VS12)[upper.tri(E_VS12)]], 
                     GROUP_ID2=colnames(E_VS12)[col(E_VS12)[upper.tri(E_VS12)]],cosine=E_VS12[upper.tri(E_VS12)])
EV22 <- data.frame(GROUP_ID1=rownames(E_VS22)[row(E_VS22)[upper.tri(E_VS22)]], 
                     GROUP_ID2=colnames(E_VS22)[col(E_VS22)[upper.tri(E_VS22)]],cosine=E_VS22[upper.tri(E_VS22)])
EV32 <- data.frame(GROUP_ID1=rownames(E_VS32)[row(E_VS32)[upper.tri(E_VS32)]], 
                     GROUP_ID2=colnames(E_VS32)[col(E_VS32)[upper.tri(E_VS32)]],cosine=E_VS32[upper.tri(E_VS32)])
EV42 <- data.frame(GROUP_ID1=rownames(E_VS42)[row(E_VS42)[upper.tri(E_VS42)]], 
                     GROUP_ID2=colnames(E_VS42)[col(E_VS42)[upper.tri(E_VS42)]],cosine=E_VS42[upper.tri(E_VS42)])
EV52 <- data.frame(GROUP_ID1=rownames(E_VS52)[row(E_VS52)[upper.tri(E_VS52)]], 
                     GROUP_ID2=colnames(E_VS52)[col(E_VS52)[upper.tri(E_VS52)]],cosine=E_VS52[upper.tri(E_VS52)])
EV62 <- data.frame(GROUP_ID1=rownames(E_VS62)[row(E_VS62)[upper.tri(E_VS62)]], 
                     GROUP_ID2=colnames(E_VS62)[col(E_VS62)[upper.tri(E_VS62)]],cosine=E_VS62[upper.tri(E_VS62)])


# ESG Both
ESGB1 <- data.frame(GROUP_ID1=rownames(ESG_BS1)[row(ESG_BS1)[upper.tri(ESG_BS1)]], 
                     GROUP_ID2=colnames(ESG_BS1)[col(ESG_BS1)[upper.tri(ESG_BS1)]],cosine=ESG_BS1[upper.tri(ESG_BS1)])
ESGB2 <- data.frame(GROUP_ID1=rownames(ESG_BS2)[row(ESG_BS2)[upper.tri(ESG_BS2)]], 
                     GROUP_ID2=colnames(ESG_BS2)[col(ESG_BS2)[upper.tri(ESG_BS2)]],cosine=ESG_BS2[upper.tri(ESG_BS2)])
ESGB3 <- data.frame(GROUP_ID1=rownames(ESG_BS3)[row(ESG_BS3)[upper.tri(ESG_BS3)]], 
                     GROUP_ID2=colnames(ESG_BS3)[col(ESG_BS3)[upper.tri(ESG_BS3)]],cosine=ESG_BS3[upper.tri(ESG_BS3)])
ESGB4 <- data.frame(GROUP_ID1=rownames(ESG_BS4)[row(ESG_BS4)[upper.tri(ESG_BS4)]], 
                     GROUP_ID2=colnames(ESG_BS4)[col(ESG_BS4)[upper.tri(ESG_BS4)]],cosine=ESG_BS4[upper.tri(ESG_BS4)])
ESGB5 <- data.frame(GROUP_ID1=rownames(ESG_BS5)[row(ESG_BS5)[upper.tri(ESG_BS5)]], 
                     GROUP_ID2=colnames(ESG_BS5)[col(ESG_BS5)[upper.tri(ESG_BS5)]],cosine=ESG_BS5[upper.tri(ESG_BS5)])
ESGB6 <- data.frame(GROUP_ID1=rownames(ESG_BS6)[row(ESG_BS6)[upper.tri(ESG_BS6)]], 
                     GROUP_ID2=colnames(ESG_BS6)[col(ESG_BS6)[upper.tri(ESG_BS6)]],cosine=ESG_BS6[upper.tri(ESG_BS6)])

ESGB12 <- data.frame(GROUP_ID1=rownames(ESG_BS12)[row(ESG_BS12)[upper.tri(ESG_BS12)]], 
                     GROUP_ID2=colnames(ESG_BS12)[col(ESG_BS12)[upper.tri(ESG_BS12)]],cosine=ESG_BS12[upper.tri(ESG_BS12)])
ESGB22 <- data.frame(GROUP_ID1=rownames(ESG_BS22)[row(ESG_BS22)[upper.tri(ESG_BS22)]], 
                     GROUP_ID2=colnames(ESG_BS22)[col(ESG_BS22)[upper.tri(ESG_BS22)]],cosine=ESG_BS22[upper.tri(ESG_BS22)])
ESGB32 <- data.frame(GROUP_ID1=rownames(ESG_BS32)[row(ESG_BS32)[upper.tri(ESG_BS32)]], 
                     GROUP_ID2=colnames(ESG_BS32)[col(ESG_BS32)[upper.tri(ESG_BS32)]],cosine=ESG_BS32[upper.tri(ESG_BS32)])
ESGB42 <- data.frame(GROUP_ID1=rownames(ESG_BS42)[row(ESG_BS42)[upper.tri(ESG_BS42)]], 
                     GROUP_ID2=colnames(ESG_BS42)[col(ESG_BS42)[upper.tri(ESG_BS42)]],cosine=ESG_BS42[upper.tri(ESG_BS42)])
ESGB52 <- data.frame(GROUP_ID1=rownames(ESG_BS52)[row(ESG_BS52)[upper.tri(ESG_BS52)]], 
                     GROUP_ID2=colnames(ESG_BS52)[col(ESG_BS52)[upper.tri(ESG_BS52)]],cosine=ESG_BS52[upper.tri(ESG_BS52)])
ESGB62 <- data.frame(GROUP_ID1=rownames(ESG_BS62)[row(ESG_BS62)[upper.tri(ESG_BS62)]], 
                     GROUP_ID2=colnames(ESG_BS62)[col(ESG_BS62)[upper.tri(ESG_BS62)]],cosine=ESG_BS62[upper.tri(ESG_BS62)])
```

Before analysis on significance can be done, meta data variables need to be added. Therefore, the data is merged with Group_Data (this is done twice because a document pair consists of 2 documents). The data is merged by group ID. This way, a regression can be made to calculate the significance of the differences. 

```{r}
# ESG mandatory and ESG voluntary --------------------------------------------------------------------
# Row bind
ESGMV1 <- rbind(ESGM1,ESGV1)
ESGMV2 <- rbind(ESGM2,ESGV2)
ESGMV3 <- rbind(ESGM3,ESGV3)
ESGMV4 <- rbind(ESGM4,ESGV4)
ESGMV5 <- rbind(ESGM5,ESGV5)
ESGMV6 <- rbind(ESGM6,ESGV6)

ESGMV12 <- rbind(ESGM12,ESGV12)
ESGMV22 <- rbind(ESGM22,ESGV22)
ESGMV32 <- rbind(ESGM32,ESGV32)
ESGMV42 <- rbind(ESGM42,ESGV42)
ESGMV52 <- rbind(ESGM52,ESGV52)
ESGMV62 <- rbind(ESGM62,ESGV62)

# Merge with metadata
ESGMV1 <- merge(ESGMV1,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV1 <- merge(ESGMV1,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV2 <- merge(ESGMV2,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV2 <- merge(ESGMV2,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV3 <- merge(ESGMV3,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV3 <- merge(ESGMV3,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV4 <- merge(ESGMV4,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV4 <- merge(ESGMV4,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV5 <- merge(ESGMV5,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV5 <- merge(ESGMV5,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV6 <- merge(ESGMV6,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV6 <- merge(ESGMV6,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

ESGMV12 <- merge(ESGMV12,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV12 <- merge(ESGMV12,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV22 <- merge(ESGMV22,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV22 <- merge(ESGMV22,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV32 <- merge(ESGMV32,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV32 <- merge(ESGMV32,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV42 <- merge(ESGMV42,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV42 <- merge(ESGMV42,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV52 <- merge(ESGMV52,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV52 <- merge(ESGMV52,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV62 <- merge(ESGMV62,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGMV62 <- merge(ESGMV62,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

#subset
ESGMV12 <- ESGMV12[ESGMV12$GROUP_ID1=="42" | ESGMV12$GROUP_ID1=="43" | ESGMV12$GROUP_ID1=="44" | 
                     ESGMV12$GROUP_ID2=="42" | ESGMV12$GROUP_ID2=="43" | ESGMV12$GROUP_ID2=="44" , ]
ESGMV22 <- ESGMV22[ESGMV22$GROUP_ID1=="42" | ESGMV22$GROUP_ID1=="43" | ESGMV22$GROUP_ID1=="44" | 
                     ESGMV22$GROUP_ID2=="42" | ESGMV22$GROUP_ID2=="43" | ESGMV22$GROUP_ID2=="44" , ]
ESGMV32 <- ESGMV32[ESGMV32$GROUP_ID1=="42" | ESGMV32$GROUP_ID1=="43" | ESGMV32$GROUP_ID1=="44" | 
                     ESGMV32$GROUP_ID2=="42" | ESGMV32$GROUP_ID2=="43" | ESGMV32$GROUP_ID2=="44" , ]
ESGMV42 <- ESGMV42[ESGMV42$GROUP_ID1=="42" | ESGMV42$GROUP_ID1=="43" | ESGMV42$GROUP_ID1=="44" | 
                     ESGMV42$GROUP_ID2=="42" | ESGMV42$GROUP_ID2=="43" | ESGMV42$GROUP_ID2=="44" , ]
ESGMV52 <- ESGMV52[ESGMV52$GROUP_ID1=="42" | ESGMV52$GROUP_ID1=="43" | ESGMV52$GROUP_ID1=="44" | 
                     ESGMV52$GROUP_ID2=="42" | ESGMV52$GROUP_ID2=="43" | ESGMV52$GROUP_ID2=="44" , ]
ESGMV62 <- ESGMV62[ESGMV62$GROUP_ID1=="42" | ESGMV62$GROUP_ID1=="43" | ESGMV62$GROUP_ID1=="44" | 
                     ESGMV62$GROUP_ID2=="42" | ESGMV62$GROUP_ID2=="43" | ESGMV62$GROUP_ID2=="44" , ]

# Delete cosine similarity between ESG docs themselves
ESGMV12$filter1 <- ifelse(ESGMV12$GROUP_TYPE.x=="ESG",1,0)
ESGMV12$filter2 <- ifelse(ESGMV12$GROUP_TYPE.y=="ESG",1,0)
ESGMV12 <- ESGMV12[ESGMV12$filter1>0 | ESGMV12$filter2>0, ]

ESGMV22$filter1 <- ifelse(ESGMV22$GROUP_TYPE.x=="ESG",1,0)
ESGMV22$filter2 <- ifelse(ESGMV22$GROUP_TYPE.y=="ESG",1,0)
ESGMV22 <- ESGMV22[ESGMV22$filter1>0 | ESGMV22$filter2>0, ]

ESGMV32$filter1 <- ifelse(ESGMV32$GROUP_TYPE.x=="ESG",1,0)
ESGMV32$filter2 <- ifelse(ESGMV32$GROUP_TYPE.y=="ESG",1,0)
ESGMV32 <- ESGMV32[ESGMV32$filter1>0 | ESGMV32$filter2>0, ]

ESGMV42$filter1 <- ifelse(ESGMV42$GROUP_TYPE.x=="ESG",1,0)
ESGMV42$filter2 <- ifelse(ESGMV42$GROUP_TYPE.y=="ESG",1,0)
ESGMV42 <- ESGMV42[ESGMV42$filter1>0 | ESGMV42$filter2>0, ]

ESGMV52$filter1 <- ifelse(ESGMV52$GROUP_TYPE.x=="ESG",1,0)
ESGMV52$filter2 <- ifelse(ESGMV52$GROUP_TYPE.y=="ESG",1,0)
ESGMV52 <- ESGMV52[ESGMV52$filter1>0 | ESGMV52$filter2>0, ]

ESGMV62$filter1 <- ifelse(ESGMV62$GROUP_TYPE.x=="ESG",1,0)
ESGMV62$filter2 <- ifelse(ESGMV62$GROUP_TYPE.y=="ESG",1,0)
ESGMV62 <- ESGMV62[ESGMV62$filter1>0 | ESGMV62$filter2>0, ]

# Set the Mandatory variable right (M)
ESGMV12$M <- ifelse(ESGMV12$REGION.y=="International",ESGMV12$M.x,ESGMV12$M.y)
ESGMV12$M <- ifelse(ESGMV12$M==1,0,1)
ESGMV12$M <- as.factor(ESGMV12$M)

ESGMV22$M <- ifelse(ESGMV22$REGION.y=="International",ESGMV22$M.x,ESGMV22$M.y)
ESGMV22$M <- ifelse(ESGMV22$M==1,0,1)
ESGMV22$M <- as.factor(ESGMV22$M)

ESGMV32$M <- ifelse(ESGMV32$REGION.y=="International",ESGMV32$M.x,ESGMV32$M.y)
ESGMV32$M <- ifelse(ESGMV32$M==1,0,1)
ESGMV32$M <- as.factor(ESGMV32$M)

ESGMV42$M <- ifelse(ESGMV42$REGION.y=="International",ESGMV42$M.x,ESGMV42$M.y)
ESGMV42$M <- ifelse(ESGMV42$M==1,0,1)
ESGMV42$M <- as.factor(ESGMV42$M)

ESGMV52$M <- ifelse(ESGMV52$REGION.y=="International",ESGMV52$M.x,ESGMV52$M.y)
ESGMV52$M <- ifelse(ESGMV52$M==1,0,1)
ESGMV52$M <- as.factor(ESGMV52$M)

ESGMV62$M <- ifelse(ESGMV62$REGION.y=="International",ESGMV62$M.x,ESGMV62$M.y)
ESGMV62$M <- ifelse(ESGMV62$M==1,0,1)
ESGMV62$M <- as.factor(ESGMV62$M)

# Set the group type variable right (METRIC_TYPE)
ESGMV12$METRIC_TYPE <- ifelse(ESGMV12$REGION.y=="International",ESGMV12$GROUP_TYPE.y,ESGMV12$GROUP_TYPE.x)
ESGMV12$METRIC_TYPE <- ifelse(ESGMV12$METRIC_TYPE==1,"E",ifelse(ESGMV12$METRIC_TYPE==3,"G","S"))
ESGMV12$METRIC_TYPE <- as.factor(ESGMV12$METRIC_TYPE)

ESGMV22$METRIC_TYPE <- ifelse(ESGMV22$REGION.y=="International",ESGMV22$GROUP_TYPE.y,ESGMV22$GROUP_TYPE.x)
ESGMV22$METRIC_TYPE <- ifelse(ESGMV22$METRIC_TYPE==1, "E",ifelse(ESGMV22$METRIC_TYPE==3,"G","S"))
ESGMV22$METRIC_TYPE <- as.factor(ESGMV22$METRIC_TYPE)

ESGMV32$METRIC_TYPE <- ifelse(ESGMV32$REGION.y=="International",ESGMV32$GROUP_TYPE.y,ESGMV32$GROUP_TYPE.x)
ESGMV32$METRIC_TYPE <- ifelse(ESGMV32$METRIC_TYPE==1, "E",ifelse(ESGMV32$METRIC_TYPE==3,"G","S"))
ESGMV32$METRIC_TYPE <- as.factor(ESGMV32$METRIC_TYPE)

ESGMV42$METRIC_TYPE <- ifelse(ESGMV42$REGION.y=="International",ESGMV42$GROUP_TYPE.y,ESGMV42$GROUP_TYPE.y)
ESGMV42$METRIC_TYPE <- ifelse(ESGMV42$METRIC_TYPE==1, "E",ifelse(ESGMV42$METRIC_TYPE==3,"G","S"))
ESGMV42$METRIC_TYPE <- as.factor(ESGMV42$METRIC_TYPE)

ESGMV52$METRIC_TYPE <- ifelse(ESGMV52$REGION.y=="International",ESGMV52$GROUP_TYPE.y,ESGMV52$GROUP_TYPE.x)
ESGMV52$METRIC_TYPE <- ifelse(ESGMV52$METRIC_TYPE==1, "E",ifelse(ESGMV52$METRIC_TYPE==3,"G","S"))
ESGMV52$METRIC_TYPE <- as.factor(ESGMV52$METRIC_TYPE)

ESGMV62$METRIC_TYPE <- ifelse(ESGMV62$REGION.y=="International",ESGMV62$GROUP_TYPE.y,ESGMV62$GROUP_TYPE.x)
ESGMV62$METRIC_TYPE <- ifelse(ESGMV62$METRIC_TYPE==1, "E",ifelse(ESGMV62$METRIC_TYPE==3,"G","S"))
ESGMV62$METRIC_TYPE <- as.factor(ESGMV62$METRIC_TYPE)

# Calculate average
AESGMV1 <- ESGMV1 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))
AESGMV2 <- ESGMV2 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))
AESGMV3 <- ESGMV3 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))
AESGMV4 <- ESGMV4 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))
AESGMV5 <- ESGMV5 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))
AESGMV6 <- ESGMV6 %>% group_by(M.x) %>% summarise(avg_cosine=mean(cosine))

AESGMV12 <- ESGMV12 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGMV22 <- ESGMV22 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGMV32 <- ESGMV32 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGMV42 <- ESGMV42 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGMV52 <- ESGMV52 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGMV62 <- ESGMV62 %>% group_by(M, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))

# ESG Mandatory and G Mandatory -----------------------------------------------------------------------------------------------------
ESGGM1 <- rbind(ESGM1,GM1)
ESGGM2 <- rbind(ESGM2,GM2)
ESGGM3 <- rbind(ESGM3,GM3)
ESGGM4 <- rbind(ESGM4,GM4)
ESGGM5 <- rbind(ESGM5,GM5)
ESGGM6 <- rbind(ESGM6,GM6)

ESGGM12 <- rbind(ESGM12,GM12)
ESGGM22 <- rbind(ESGM22,GM22)
ESGGM32 <- rbind(ESGM32,GM32)
ESGGM42 <- rbind(ESGM42,GM42)
ESGGM52 <- rbind(ESGM52,GM52)
ESGGM62 <- rbind(ESGM62,GM62)

# Merge with metadata
ESGGM1 <- merge(ESGGM1,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM1 <- merge(ESGGM1,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM2 <- merge(ESGGM2,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM2 <- merge(ESGGM2,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM3 <- merge(ESGGM3,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM3 <- merge(ESGGM3,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM4 <- merge(ESGGM4,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM4 <- merge(ESGGM4,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM5 <- merge(ESGGM5,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM5 <- merge(ESGGM5,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM6 <- merge(ESGGM6,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM6 <- merge(ESGGM6,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

ESGGM12 <- merge(ESGGM12,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM12 <- merge(ESGGM12,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM22 <- merge(ESGGM22,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM22 <- merge(ESGGM22,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM32 <- merge(ESGGM32,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM32 <- merge(ESGGM32,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM42 <- merge(ESGGM42,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM42 <- merge(ESGGM42,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM52 <- merge(ESGGM52,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM52 <- merge(ESGGM52,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM62 <- merge(ESGGM62,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGGM62 <- merge(ESGGM62,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

#subset
ESGGM12 <- ESGGM12[ESGGM12$GROUP_ID1=="42" | ESGGM12$GROUP_ID1=="43" | ESGGM12$GROUP_ID1=="44" | 
                     ESGGM12$GROUP_ID2=="42" | ESGGM12$GROUP_ID2=="43" | ESGGM12$GROUP_ID2=="44" , ]
ESGGM22 <- ESGGM22[ESGGM22$GROUP_ID1=="42" | ESGGM22$GROUP_ID1=="43" | ESGGM22$GROUP_ID1=="44" | 
                     ESGGM22$GROUP_ID2=="42" | ESGGM22$GROUP_ID2=="43" | ESGGM22$GROUP_ID2=="44" , ]
ESGGM32 <- ESGGM32[ESGGM32$GROUP_ID1=="42" | ESGGM32$GROUP_ID1=="43" | ESGGM32$GROUP_ID1=="44" | 
                     ESGGM32$GROUP_ID2=="42" | ESGGM32$GROUP_ID2=="43" | ESGGM32$GROUP_ID2=="44" , ]
ESGGM42 <- ESGGM42[ESGGM42$GROUP_ID1=="42" | ESGGM42$GROUP_ID1=="43" | ESGGM42$GROUP_ID1=="44" | 
                     ESGGM42$GROUP_ID2=="42" | ESGGM42$GROUP_ID2=="43" | ESGGM42$GROUP_ID2=="44" , ]
ESGGM52 <- ESGGM52[ESGGM52$GROUP_ID1=="42" | ESGGM52$GROUP_ID1=="43" | ESGGM52$GROUP_ID1=="44" | 
                     ESGGM52$GROUP_ID2=="42" | ESGGM52$GROUP_ID2=="43" | ESGGM52$GROUP_ID2=="44" , ]
ESGGM62 <- ESGGM62[ESGGM62$GROUP_ID1=="42" | ESGGM62$GROUP_ID1=="43" | ESGGM62$GROUP_ID1=="44" | 
                     ESGGM62$GROUP_ID2=="42" | ESGGM62$GROUP_ID2=="43" | ESGGM62$GROUP_ID2=="44" , ]

# Delete cosine similarity between ESG docs themselves
ESGGM12$filter1 <- ifelse(ESGGM12$REGION.x=="International",0,1)
ESGGM12$filter2 <- ifelse(ESGGM12$REGION.y=="International",0,1)
ESGGM12 <- ESGGM12[ESGGM12$filter1>0 | ESGGM12$filter2>0, ]

ESGGM22$filter1 <- ifelse(ESGGM22$REGION.x=="International",0,1)
ESGGM22$filter2 <- ifelse(ESGGM22$REGION.y=="International",0,1)
ESGGM22 <- ESGGM22[ESGGM22$filter1>0 | ESGGM22$filter2>0, ]

ESGGM32$filter1 <- ifelse(ESGGM32$REGION.x=="International",0,1)
ESGGM32$filter2 <- ifelse(ESGGM32$REGION.y=="International",0,1)
ESGGM32 <- ESGGM32[ESGGM32$filter1>0 | ESGGM32$filter2>0, ]

ESGGM42$filter1 <- ifelse(ESGGM42$REGION.x=="International",0,1)
ESGGM42$filter2 <- ifelse(ESGGM42$REGION.y=="International",0,1)
ESGGM42 <- ESGGM42[ESGGM42$filter1>0 | ESGGM42$filter2>0, ]

ESGGM52$filter1 <- ifelse(ESGGM52$REGION.x=="International",0,1)
ESGGM52$filter2 <- ifelse(ESGGM52$REGION.y=="International",0,1)
ESGGM52 <- ESGGM52[ESGGM52$filter1>0 | ESGGM52$filter2>0, ]

ESGGM62$filter1 <- ifelse(ESGGM62$REGION.x=="International",0,1)
ESGGM62$filter2 <- ifelse(ESGGM62$REGION.y=="International",0,1)
ESGGM62 <- ESGGM62[ESGGM62$filter1>0 | ESGGM62$filter2>0, ]

# Set the GROUP TYPE variable right (ESG or G)
ESGGM12$GROUP_TYPE <- ifelse(ESGGM12$REGION.y=="International",ESGGM12$GROUP_TYPE.x,ESGGM12$GROUP_TYPE.y)
ESGGM12$GROUP_TYPE <- ifelse(ESGGM12$GROUP_TYPE==2,"ESG","G")
ESGGM12$GROUP_TYPE <- as.factor(ESGGM12$GROUP_TYPE)

ESGGM22$GROUP_TYPE <- ifelse(ESGGM22$REGION.y=="International",ESGGM22$GROUP_TYPE.x,ESGGM22$GROUP_TYPE.y)
ESGGM22$GROUP_TYPE <- ifelse(ESGGM22$GROUP_TYPE==2,"ESG","G")
ESGGM22$GROUP_TYPE <- as.factor(ESGGM22$GROUP_TYPE)

ESGGM32$GROUP_TYPE <- ifelse(ESGGM32$REGION.y=="International",ESGGM32$GROUP_TYPE.x,ESGGM32$GROUP_TYPE.y)
ESGGM32$GROUP_TYPE <- ifelse(ESGGM32$GROUP_TYPE==2,"ESG","G")
ESGGM32$GROUP_TYPE <- as.factor(ESGGM32$GROUP_TYPE)

ESGGM42$GROUP_TYPE <- ifelse(ESGGM42$REGION.y=="International",ESGGM42$GROUP_TYPE.x,ESGGM42$GROUP_TYPE.y)
ESGGM42$GROUP_TYPE <- ifelse(ESGGM42$GROUP_TYPE==2,"ESG","G")
ESGGM42$GROUP_TYPE <- as.factor(ESGGM42$GROUP_TYPE)

ESGGM52$GROUP_TYPE <- ifelse(ESGGM52$REGION.y=="International",ESGGM52$GROUP_TYPE.x,ESGGM52$GROUP_TYPE.y)
ESGGM52$GROUP_TYPE <- ifelse(ESGGM52$GROUP_TYPE==2,"ESG","G")
ESGGM52$GROUP_TYPE <- as.factor(ESGGM52$GROUP_TYPE)

ESGGM62$GROUP_TYPE <- ifelse(ESGGM62$REGION.y=="International",ESGGM62$GROUP_TYPE.x,ESGGM62$GROUP_TYPE.y)
ESGGM62$GROUP_TYPE <- ifelse(ESGGM62$GROUP_TYPE==2,"ESG","G")
ESGGM62$GROUP_TYPE <- as.factor(ESGGM62$GROUP_TYPE)

# Set the group type variable right (METRIC_TYPE)
ESGGM12$METRIC_TYPE <- ifelse(ESGGM12$REGION.y=="International",ESGGM12$GROUP_TYPE.y,ESGGM12$GROUP_TYPE.x)
ESGGM12$METRIC_TYPE <- ifelse(ESGGM12$METRIC_TYPE==1,"E",ifelse(ESGGM12$METRIC_TYPE==3,"G","S"))
ESGGM12$METRIC_TYPE <- as.factor(ESGGM12$METRIC_TYPE)

ESGGM22$METRIC_TYPE <- ifelse(ESGGM22$REGION.y=="International",ESGGM22$GROUP_TYPE.y,ESGGM22$GROUP_TYPE.x)
ESGGM22$METRIC_TYPE <- ifelse(ESGGM22$METRIC_TYPE==1, "E",ifelse(ESGGM22$METRIC_TYPE==3,"G","S"))
ESGGM22$METRIC_TYPE <- as.factor(ESGGM22$METRIC_TYPE)

ESGGM32$METRIC_TYPE <- ifelse(ESGGM32$REGION.y=="International",ESGGM32$GROUP_TYPE.y,ESGGM32$GROUP_TYPE.x)
ESGGM32$METRIC_TYPE <- ifelse(ESGGM32$METRIC_TYPE==1, "E",ifelse(ESGGM32$METRIC_TYPE==3,"G","S"))
ESGGM32$METRIC_TYPE <- as.factor(ESGGM32$METRIC_TYPE)

ESGGM42$METRIC_TYPE <- ifelse(ESGGM42$REGION.y=="International",ESGGM42$GROUP_TYPE.y,ESGGM42$GROUP_TYPE.y)
ESGGM42$METRIC_TYPE <- ifelse(ESGGM42$METRIC_TYPE==1, "E",ifelse(ESGGM42$METRIC_TYPE==3,"G","S"))
ESGGM42$METRIC_TYPE <- as.factor(ESGGM42$METRIC_TYPE)

ESGGM52$METRIC_TYPE <- ifelse(ESGGM52$REGION.y=="International",ESGGM52$GROUP_TYPE.y,ESGGM52$GROUP_TYPE.x)
ESGGM52$METRIC_TYPE <- ifelse(ESGGM52$METRIC_TYPE==1, "E",ifelse(ESGGM52$METRIC_TYPE==3,"G","S"))
ESGGM52$METRIC_TYPE <- as.factor(ESGGM52$METRIC_TYPE)

ESGGM62$METRIC_TYPE <- ifelse(ESGGM62$REGION.y=="International",ESGGM62$GROUP_TYPE.y,ESGGM62$GROUP_TYPE.x)
ESGGM62$METRIC_TYPE <- ifelse(ESGGM62$METRIC_TYPE==1, "E",ifelse(ESGGM62$METRIC_TYPE==3,"G","S"))
ESGGM62$METRIC_TYPE <- as.factor(ESGGM62$METRIC_TYPE)

# Calculate average
AESGGM1 <- ESGGM1 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGGM2 <- ESGGM2 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGGM3 <- ESGGM3 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGGM4 <- ESGGM4 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGGM5 <- ESGGM5 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGGM6 <- ESGGM6 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))

AESGGM12 <- ESGGM12 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGGM22 <- ESGGM22 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGGM32 <- ESGGM32 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGGM42 <- ESGGM42 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGGM52 <- ESGGM52 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGGM62 <- ESGGM62 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))

# ESG Voluntary and E voluntary -------------------------------------------------------------------------------------------------------------------
ESGEV1 <- rbind(ESGV1,EV1)
ESGEV2 <- rbind(ESGV2,EV2)
ESGEV3 <- rbind(ESGV3,EV3)
ESGEV4 <- rbind(ESGV4,EV4)
ESGEV5 <- rbind(ESGV5,EV5)
ESGEV6 <- rbind(ESGV6,EV6)

ESGEV12 <- rbind(ESGV12,EV12)
ESGEV22 <- rbind(ESGV22,EV22)
ESGEV32 <- rbind(ESGV32,EV32)
ESGEV42 <- rbind(ESGV42,EV42)
ESGEV52 <- rbind(ESGV52,EV52)
ESGEV62 <- rbind(ESGV62,EV62)

# Merge with metadata
ESGEV1 <- merge(ESGEV1,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV1 <- merge(ESGEV1,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV2 <- merge(ESGEV2,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV2 <- merge(ESGEV2,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV3 <- merge(ESGEV3,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV3 <- merge(ESGEV3,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV4 <- merge(ESGEV4,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV4 <- merge(ESGEV4,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV5 <- merge(ESGEV5,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV5 <- merge(ESGEV5,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV6 <- merge(ESGEV6,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV6 <- merge(ESGEV6,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

ESGEV12 <- merge(ESGEV12,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV12 <- merge(ESGEV12,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV22 <- merge(ESGEV22,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV22 <- merge(ESGEV22,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV32 <- merge(ESGEV32,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV32 <- merge(ESGEV32,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV42 <- merge(ESGEV42,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV42 <- merge(ESGEV42,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV52 <- merge(ESGEV52,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV52 <- merge(ESGEV52,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV62 <- merge(ESGEV62,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGEV62 <- merge(ESGEV62,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

#subset
ESGEV12 <- ESGEV12[ESGEV12$GROUP_ID1=="42" | ESGEV12$GROUP_ID1=="43" | ESGEV12$GROUP_ID1=="44" | 
                     ESGEV12$GROUP_ID2=="42" | ESGEV12$GROUP_ID2=="43" | ESGEV12$GROUP_ID2=="44" , ]
ESGEV22 <- ESGEV22[ESGEV22$GROUP_ID1=="42" | ESGEV22$GROUP_ID1=="43" | ESGEV22$GROUP_ID1=="44" | 
                     ESGEV22$GROUP_ID2=="42" | ESGEV22$GROUP_ID2=="43" | ESGEV22$GROUP_ID2=="44" , ]
ESGEV32 <- ESGEV32[ESGEV32$GROUP_ID1=="42" | ESGEV32$GROUP_ID1=="43" | ESGEV32$GROUP_ID1=="44" | 
                     ESGEV32$GROUP_ID2=="42" | ESGEV32$GROUP_ID2=="43" | ESGEV32$GROUP_ID2=="44" , ]
ESGEV42 <- ESGEV42[ESGEV42$GROUP_ID1=="42" | ESGEV42$GROUP_ID1=="43" | ESGEV42$GROUP_ID1=="44" | 
                     ESGEV42$GROUP_ID2=="42" | ESGEV42$GROUP_ID2=="43" | ESGEV42$GROUP_ID2=="44" , ]
ESGEV52 <- ESGEV52[ESGEV52$GROUP_ID1=="42" | ESGEV52$GROUP_ID1=="43" | ESGEV52$GROUP_ID1=="44" | 
                     ESGEV52$GROUP_ID2=="42" | ESGEV52$GROUP_ID2=="43" | ESGEV52$GROUP_ID2=="44" , ]
ESGEV62 <- ESGEV62[ESGEV62$GROUP_ID1=="42" | ESGEV62$GROUP_ID1=="43" | ESGEV62$GROUP_ID1=="44" | 
                     ESGEV62$GROUP_ID2=="42" | ESGEV62$GROUP_ID2=="43" | ESGEV62$GROUP_ID2=="44" , ]

# Delete cosine similarity between ESG docs themselves
ESGEV12$filter1 <- ifelse(ESGEV12$REGION.x=="International",0,1)
ESGEV12$filter2 <- ifelse(ESGEV12$REGION.y=="International",0,1)
ESGEV12 <- ESGEV12[ESGEV12$filter1>0 | ESGEV12$filter2>0, ]

ESGEV22$filter1 <- ifelse(ESGEV22$REGION.x=="International",0,1)
ESGEV22$filter2 <- ifelse(ESGEV22$REGION.y=="International",0,1)
ESGEV22 <- ESGEV22[ESGEV22$filter1>0 | ESGEV22$filter2>0, ]

ESGEV32$filter1 <- ifelse(ESGEV32$REGION.x=="International",0,1)
ESGEV32$filter2 <- ifelse(ESGEV32$REGION.y=="International",0,1)
ESGEV32 <- ESGEV32[ESGEV32$filter1>0 | ESGEV32$filter2>0, ]

ESGEV42$filter1 <- ifelse(ESGEV42$REGION.x=="International",0,1)
ESGEV42$filter2 <- ifelse(ESGEV42$REGION.y=="International",0,1)
ESGEV42 <- ESGEV42[ESGEV42$filter1>0 | ESGEV42$filter2>0, ]

ESGEV52$filter1 <- ifelse(ESGEV52$REGION.x=="International",0,1)
ESGEV52$filter2 <- ifelse(ESGEV52$REGION.y=="International",0,1)
ESGEV52 <- ESGEV52[ESGEV52$filter1>0 | ESGEV52$filter2>0, ]

ESGEV62$filter1 <- ifelse(ESGEV62$REGION.x=="International",0,1)
ESGEV62$filter2 <- ifelse(ESGEV62$REGION.y=="International",0,1)
ESGEV62 <- ESGEV62[ESGEV62$filter1>0 | ESGEV62$filter2>0, ]

# Set the GROUP TYPE variable right (ESG or E)
ESGEV12$GROUP_TYPE <- ifelse(ESGEV12$REGION.y=="International",ESGEV12$GROUP_TYPE.x,ESGEV12$GROUP_TYPE.y)
ESGEV12$GROUP_TYPE <- ifelse(ESGEV12$GROUP_TYPE==2,"ESG","E")
ESGEV12$GROUP_TYPE <- as.factor(ESGEV12$GROUP_TYPE)

ESGEV22$GROUP_TYPE <- ifelse(ESGEV22$REGION.y=="International",ESGEV22$GROUP_TYPE.x,ESGEV22$GROUP_TYPE.y)
ESGEV22$GROUP_TYPE <- ifelse(ESGEV22$GROUP_TYPE==2,"ESG","E")
ESGEV22$GROUP_TYPE <- as.factor(ESGEV22$GROUP_TYPE)

ESGEV32$GROUP_TYPE <- ifelse(ESGEV32$REGION.y=="International",ESGEV32$GROUP_TYPE.x,ESGEV32$GROUP_TYPE.y)
ESGEV32$GROUP_TYPE <- ifelse(ESGEV32$GROUP_TYPE==2,"ESG","E")
ESGEV32$GROUP_TYPE <- as.factor(ESGEV32$GROUP_TYPE)

ESGEV42$GROUP_TYPE <- ifelse(ESGEV42$REGION.y=="International",ESGEV42$GROUP_TYPE.x,ESGEV42$GROUP_TYPE.y)
ESGEV42$GROUP_TYPE <- ifelse(ESGEV42$GROUP_TYPE==2,"ESG","E")
ESGEV42$GROUP_TYPE <- as.factor(ESGEV42$GROUP_TYPE)

ESGEV52$GROUP_TYPE <- ifelse(ESGEV52$REGION.y=="International",ESGEV52$GROUP_TYPE.x,ESGEV52$GROUP_TYPE.y)
ESGEV52$GROUP_TYPE <- ifelse(ESGEV52$GROUP_TYPE==2,"ESG","E")
ESGEV52$GROUP_TYPE <- as.factor(ESGEV52$GROUP_TYPE)

ESGEV62$GROUP_TYPE <- ifelse(ESGEV62$REGION.y=="International",ESGEV62$GROUP_TYPE.x,ESGEV62$GROUP_TYPE.y)
ESGEV62$GROUP_TYPE <- ifelse(ESGEV62$GROUP_TYPE==2,"ESG","E")
ESGEV62$GROUP_TYPE <- as.factor(ESGEV62$GROUP_TYPE)

# Set the group type variable right (METRIC_TYPE)
ESGEV12$METRIC_TYPE <- ifelse(ESGEV12$REGION.y=="International",ESGEV12$GROUP_TYPE.y,ESGEV12$GROUP_TYPE.x)
ESGEV12$METRIC_TYPE <- ifelse(ESGEV12$METRIC_TYPE==1,"E",ifelse(ESGEV12$METRIC_TYPE==3,"G","S"))
ESGEV12$METRIC_TYPE <- as.factor(ESGEV12$METRIC_TYPE)

ESGEV22$METRIC_TYPE <- ifelse(ESGEV22$REGION.y=="International",ESGEV22$GROUP_TYPE.y,ESGEV22$GROUP_TYPE.x)
ESGEV22$METRIC_TYPE <- ifelse(ESGEV22$METRIC_TYPE==1, "E",ifelse(ESGEV22$METRIC_TYPE==3,"G","S"))
ESGEV22$METRIC_TYPE <- as.factor(ESGEV22$METRIC_TYPE)

ESGEV32$METRIC_TYPE <- ifelse(ESGEV32$REGION.y=="International",ESGEV32$GROUP_TYPE.y,ESGEV32$GROUP_TYPE.x)
ESGEV32$METRIC_TYPE <- ifelse(ESGEV32$METRIC_TYPE==1, "E",ifelse(ESGEV32$METRIC_TYPE==3,"G","S"))
ESGEV32$METRIC_TYPE <- as.factor(ESGEV32$METRIC_TYPE)

ESGEV42$METRIC_TYPE <- ifelse(ESGEV42$REGION.y=="International",ESGEV42$GROUP_TYPE.y,ESGEV42$GROUP_TYPE.y)
ESGEV42$METRIC_TYPE <- ifelse(ESGEV42$METRIC_TYPE==1, "E",ifelse(ESGEV42$METRIC_TYPE==3,"G","S"))
ESGEV42$METRIC_TYPE <- as.factor(ESGEV42$METRIC_TYPE)

ESGEV52$METRIC_TYPE <- ifelse(ESGEV52$REGION.y=="International",ESGEV52$GROUP_TYPE.y,ESGEV52$GROUP_TYPE.x)
ESGEV52$METRIC_TYPE <- ifelse(ESGEV52$METRIC_TYPE==1, "E",ifelse(ESGEV52$METRIC_TYPE==3,"G","S"))
ESGEV52$METRIC_TYPE <- as.factor(ESGEV52$METRIC_TYPE)

ESGEV62$METRIC_TYPE <- ifelse(ESGEV62$REGION.y=="International",ESGEV62$GROUP_TYPE.y,ESGEV62$GROUP_TYPE.x)
ESGEV62$METRIC_TYPE <- ifelse(ESGEV62$METRIC_TYPE==1, "E",ifelse(ESGEV62$METRIC_TYPE==3,"G","S"))
ESGEV62$METRIC_TYPE <- as.factor(ESGEV62$METRIC_TYPE)

# Calculate average
AESGEV1 <- ESGEV1 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGEV2 <- ESGEV2 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGEV3 <- ESGEV3 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGEV4 <- ESGEV4 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGEV5 <- ESGEV5 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))
AESGEV6 <- ESGEV6 %>% group_by(GROUP_TYPE.x) %>% summarise(avg_cosine=mean(cosine))

AESGEV12 <- ESGEV12 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGEV22 <- ESGEV22 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGEV32 <- ESGEV32 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGEV42 <- ESGEV42 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGEV52 <- ESGEV52 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGEV62 <- ESGEV62 %>% group_by(GROUP_TYPE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))


# ESG Both ----------------------------------------------------------------------------------------------------------------------------------
# Merge with metadata
ESGB1 <- merge(ESGB1,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB1 <- merge(ESGB1,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB2 <- merge(ESGB2,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB2 <- merge(ESGB2,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB3 <- merge(ESGB3,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB3 <- merge(ESGB3,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB4 <- merge(ESGB4,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB4 <- merge(ESGB4,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB5 <- merge(ESGB5,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB5 <- merge(ESGB5,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB6 <- merge(ESGB6,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB6 <- merge(ESGB6,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

ESGB12 <- merge(ESGB12,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB12 <- merge(ESGB12,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB22 <- merge(ESGB22,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB22 <- merge(ESGB22,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB32 <- merge(ESGB32,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB32 <- merge(ESGB32,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB42 <- merge(ESGB42,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB42 <- merge(ESGB42,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB52 <- merge(ESGB52,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB52 <- merge(ESGB52,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB62 <- merge(ESGB62,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGB62 <- merge(ESGB62,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

#subset
ESGB12 <- ESGB12[ESGB12$GROUP_ID1=="42" | ESGB12$GROUP_ID1=="43" | ESGB12$GROUP_ID1=="44" | 
                     ESGB12$GROUP_ID2=="42" | ESGB12$GROUP_ID2=="43" | ESGB12$GROUP_ID2=="44" , ]
ESGB22 <- ESGB22[ESGB22$GROUP_ID1=="42" | ESGB22$GROUP_ID1=="43" | ESGB22$GROUP_ID1=="44" | 
                     ESGB22$GROUP_ID2=="42" | ESGB22$GROUP_ID2=="43" | ESGB22$GROUP_ID2=="44" , ]
ESGB32 <- ESGB32[ESGB32$GROUP_ID1=="42" | ESGB32$GROUP_ID1=="43" | ESGB32$GROUP_ID1=="44" | 
                     ESGB32$GROUP_ID2=="42" | ESGB32$GROUP_ID2=="43" | ESGB32$GROUP_ID2=="44" , ]
ESGB42 <- ESGB42[ESGB42$GROUP_ID1=="42" | ESGB42$GROUP_ID1=="43" | ESGB42$GROUP_ID1=="44" | 
                     ESGB42$GROUP_ID2=="42" | ESGB42$GROUP_ID2=="43" | ESGB42$GROUP_ID2=="44" , ]
ESGB52 <- ESGB52[ESGB52$GROUP_ID1=="42" | ESGB52$GROUP_ID1=="43" | ESGB52$GROUP_ID1=="44" | 
                     ESGB52$GROUP_ID2=="42" | ESGB52$GROUP_ID2=="43" | ESGB52$GROUP_ID2=="44" , ]
ESGB62 <- ESGB62[ESGB62$GROUP_ID1=="42" | ESGB62$GROUP_ID1=="43" | ESGB62$GROUP_ID1=="44" | 
                     ESGB62$GROUP_ID2=="42" | ESGB62$GROUP_ID2=="43" | ESGB62$GROUP_ID2=="44" , ]

# Delete cosine similarity between ESG docs themselves
ESGB12$filter1 <- ifelse(ESGB12$GROUP_TYPE.x=="ESG",1,0)
ESGB12$filter2 <- ifelse(ESGB12$GROUP_TYPE.y=="ESG",1,0)
ESGB12 <- ESGB12[ESGB12$filter1>0 | ESGB12$filter2>0, ]

ESGB22$filter1 <- ifelse(ESGB22$GROUP_TYPE.x=="ESG",1,0)
ESGB22$filter2 <- ifelse(ESGB22$GROUP_TYPE.y=="ESG",1,0)
ESGB22 <- ESGB22[ESGB22$filter1>0 | ESGB22$filter2>0, ]

ESGB32$filter1 <- ifelse(ESGB32$GROUP_TYPE.x=="ESG",1,0)
ESGB32$filter2 <- ifelse(ESGB32$GROUP_TYPE.y=="ESG",1,0)
ESGB32 <- ESGB32[ESGB32$filter1>0 | ESGB32$filter2>0, ]

ESGB42$filter1 <- ifelse(ESGB42$GROUP_TYPE.x=="ESG",1,0)
ESGB42$filter2 <- ifelse(ESGB42$GROUP_TYPE.y=="ESG",1,0)
ESGB42 <- ESGB42[ESGB42$filter1>0 | ESGB42$filter2>0, ]

ESGB52$filter1 <- ifelse(ESGB52$GROUP_TYPE.x=="ESG",1,0)
ESGB52$filter2 <- ifelse(ESGB52$GROUP_TYPE.y=="ESG",1,0)
ESGB52 <- ESGB52[ESGB52$filter1>0 | ESGB52$filter2>0, ]

ESGB62$filter1 <- ifelse(ESGB62$GROUP_TYPE.x=="ESG",1,0)
ESGB62$filter2 <- ifelse(ESGB62$GROUP_TYPE.y=="ESG",1,0)
ESGB62 <- ESGB62[ESGB62$filter1>0 | ESGB62$filter2>0, ]

# Set the group type variable right (METRIC_TYPE)
ESGB12$METRIC_TYPE <- ifelse(ESGB12$REGION.y=="International",ESGB12$GROUP_TYPE.y,ESGB12$GROUP_TYPE.x)
ESGB12$METRIC_TYPE <- ifelse(ESGB12$METRIC_TYPE==1,"E",ifelse(ESGB12$METRIC_TYPE==3,"G","S"))
ESGB12$METRIC_TYPE <- as.factor(ESGB12$METRIC_TYPE)

ESGB22$METRIC_TYPE <- ifelse(ESGB22$REGION.y=="International",ESGB22$GROUP_TYPE.y,ESGB22$GROUP_TYPE.x)
ESGB22$METRIC_TYPE <- ifelse(ESGB22$METRIC_TYPE==1, "E",ifelse(ESGB22$METRIC_TYPE==3,"G","S"))
ESGB22$METRIC_TYPE <- as.factor(ESGB22$METRIC_TYPE)

ESGB32$METRIC_TYPE <- ifelse(ESGB32$REGION.y=="International",ESGB32$GROUP_TYPE.y,ESGB32$GROUP_TYPE.x)
ESGB32$METRIC_TYPE <- ifelse(ESGB32$METRIC_TYPE==1, "E",ifelse(ESGB32$METRIC_TYPE==3,"G","S"))
ESGB32$METRIC_TYPE <- as.factor(ESGB32$METRIC_TYPE)

ESGB42$METRIC_TYPE <- ifelse(ESGB42$REGION.y=="International",ESGB42$GROUP_TYPE.y,ESGB42$GROUP_TYPE.y)
ESGB42$METRIC_TYPE <- ifelse(ESGB42$METRIC_TYPE==1, "E",ifelse(ESGB42$METRIC_TYPE==3,"G","S"))
ESGB42$METRIC_TYPE <- as.factor(ESGB42$METRIC_TYPE)

ESGB52$METRIC_TYPE <- ifelse(ESGB52$REGION.y=="International",ESGB52$GROUP_TYPE.y,ESGB52$GROUP_TYPE.x)
ESGB52$METRIC_TYPE <- ifelse(ESGB52$METRIC_TYPE==1, "E",ifelse(ESGB52$METRIC_TYPE==3,"G","S"))
ESGB52$METRIC_TYPE <- as.factor(ESGB52$METRIC_TYPE)

ESGB62$METRIC_TYPE <- ifelse(ESGB62$REGION.y=="International",ESGB62$GROUP_TYPE.y,ESGB62$GROUP_TYPE.x)
ESGB62$METRIC_TYPE <- ifelse(ESGB62$METRIC_TYPE==1, "E",ifelse(ESGB62$METRIC_TYPE==3,"G","S"))
ESGB62$METRIC_TYPE <- as.factor(ESGB62$METRIC_TYPE)

# Calculate average
AESGB1 <- ESGB1 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB2 <- ESGB2 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB3 <- ESGB3 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB4 <- ESGB4 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB5 <- ESGB5 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB6 <- ESGB6 %>% group_by(M.x, M.y) %>% summarise(avg_cosine=mean(cosine))

AESGB12 <- ESGB12 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB22 <- ESGB22 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB32 <- ESGB32 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB42 <- ESGB42 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB52 <- ESGB52 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))
AESGB62 <- ESGB62 %>% group_by(METRIC_TYPE, M.x, M.y) %>% summarise(avg_cosine=mean(cosine))

# ESG Voluntary ---------------------------------------------------------------------
# Merge with metadata
ESGV1 <- merge(ESGV1,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV1 <- merge(ESGV1,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV2 <- merge(ESGV2,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV2 <- merge(ESGV2,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV3 <- merge(ESGV3,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV3 <- merge(ESGV3,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV4 <- merge(ESGV4,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV4 <- merge(ESGV4,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV5 <- merge(ESGV5,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV5 <- merge(ESGV5,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV6 <- merge(ESGV6,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV6 <- merge(ESGV6,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

ESGV12 <- merge(ESGV12,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV12 <- merge(ESGV12,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV22 <- merge(ESGV22,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV22 <- merge(ESGV22,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV32 <- merge(ESGV32,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV32 <- merge(ESGV32,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV42 <- merge(ESGV42,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV42 <- merge(ESGV42,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV52 <- merge(ESGV52,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV52 <- merge(ESGV52,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV62 <- merge(ESGV62,Group_Data, by.x="GROUP_ID1",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)
ESGV62 <- merge(ESGV62,Group_Data, by.x="GROUP_ID2",by.y="GROUP_ID",all.x=TRUE,all.y=FALSE)

#subset
ESGV12 <- ESGV12[ESGV12$GROUP_ID1=="42" | ESGV12$GROUP_ID1=="43" | ESGV12$GROUP_ID1=="44" | 
                     ESGV12$GROUP_ID2=="42" | ESGV12$GROUP_ID2=="43" | ESGV12$GROUP_ID2=="44" , ]
ESGV22 <- ESGV22[ESGV22$GROUP_ID1=="42" | ESGV22$GROUP_ID1=="43" | ESGV22$GROUP_ID1=="44" | 
                     ESGV22$GROUP_ID2=="42" | ESGV22$GROUP_ID2=="43" | ESGV22$GROUP_ID2=="44" , ]
ESGV32 <- ESGV32[ESGV32$GROUP_ID1=="42" | ESGV32$GROUP_ID1=="43" | ESGV32$GROUP_ID1=="44" | 
                     ESGV32$GROUP_ID2=="42" | ESGV32$GROUP_ID2=="43" | ESGV32$GROUP_ID2=="44" , ]
ESGV42 <- ESGV42[ESGV42$GROUP_ID1=="42" | ESGV42$GROUP_ID1=="43" | ESGV42$GROUP_ID1=="44" | 
                     ESGV42$GROUP_ID2=="42" | ESGV42$GROUP_ID2=="43" | ESGV42$GROUP_ID2=="44" , ]
ESGV52 <- ESGV52[ESGV52$GROUP_ID1=="42" | ESGV52$GROUP_ID1=="43" | ESGV52$GROUP_ID1=="44" | 
                     ESGV52$GROUP_ID2=="42" | ESGV52$GROUP_ID2=="43" | ESGV52$GROUP_ID2=="44" , ]
ESGV62 <- ESGV62[ESGV62$GROUP_ID1=="42" | ESGV62$GROUP_ID1=="43" | ESGV62$GROUP_ID1=="44" | 
                     ESGV62$GROUP_ID2=="42" | ESGV62$GROUP_ID2=="43" | ESGV62$GROUP_ID2=="44" , ]

# Delete cosine similarity between ESG docs themselves
ESGV12$filter1 <- ifelse(ESGV12$GROUP_TYPE.x=="ESG",1,0)
ESGV12$filter2 <- ifelse(ESGV12$GROUP_TYPE.y=="ESG",1,0)
ESGV12 <- ESGV12[ESGV12$filter1>0 | ESGV12$filter2>0, ]

ESGV22$filter1 <- ifelse(ESGV22$GROUP_TYPE.x=="ESG",1,0)
ESGV22$filter2 <- ifelse(ESGV22$GROUP_TYPE.y=="ESG",1,0)
ESGV22 <- ESGV22[ESGV22$filter1>0 | ESGV22$filter2>0, ]

ESGV32$filter1 <- ifelse(ESGV32$GROUP_TYPE.x=="ESG",1,0)
ESGV32$filter2 <- ifelse(ESGV32$GROUP_TYPE.y=="ESG",1,0)
ESGV32 <- ESGV32[ESGV32$filter1>0 | ESGV32$filter2>0, ]

ESGV42$filter1 <- ifelse(ESGV42$GROUP_TYPE.x=="ESG",1,0)
ESGV42$filter2 <- ifelse(ESGV42$GROUP_TYPE.y=="ESG",1,0)
ESGV42 <- ESGV42[ESGV42$filter1>0 | ESGV42$filter2>0, ]

ESGV52$filter1 <- ifelse(ESGV52$GROUP_TYPE.x=="ESG",1,0)
ESGV52$filter2 <- ifelse(ESGV52$GROUP_TYPE.y=="ESG",1,0)
ESGV52 <- ESGV52[ESGV52$filter1>0 | ESGV52$filter2>0, ]

ESGV62$filter1 <- ifelse(ESGV62$GROUP_TYPE.x=="ESG",1,0)
ESGV62$filter2 <- ifelse(ESGV62$GROUP_TYPE.y=="ESG",1,0)
ESGV62 <- ESGV62[ESGV62$filter1>0 | ESGV62$filter2>0, ]

# Set the ESG listing variable right (ESG_LISTING_RULE)
ESGV12$ESG_LISTING_RULE <- ifelse(ESGV12$REGION.y=="International",ESGV12$ESG_LISTING_RULE.x,ESGV12$ESG_LISTING_RULE.y)
ESGV12$ESG_LISTING_RULE <- ifelse(ESGV12$ESG_LISTING_RULE==1,0,1)
ESGV12$ESG_LISTING_RULE <- as.factor(ESGV12$ESG_LISTING_RULE)

ESGV22$ESG_LISTING_RULE <- ifelse(ESGV22$REGION.y=="International",ESGV22$ESG_LISTING_RULE.x,ESGV22$ESG_LISTING_RULE.y)
ESGV22$ESG_LISTING_RULE <- ifelse(ESGV22$ESG_LISTING_RULE==1,0,1)
ESGV22$ESG_LISTING_RULE <- as.factor(ESGV22$ESG_LISTING_RULE)

ESGV32$ESG_LISTING_RULE <- ifelse(ESGV32$REGION.y=="International",ESGV32$ESG_LISTING_RULE.x,ESGV32$ESG_LISTING_RULE.y)
ESGV32$ESG_LISTING_RULE <- ifelse(ESGV32$ESG_LISTING_RULE==1,0,1)
ESGV32$ESG_LISTING_RULE <- as.factor(ESGV32$ESG_LISTING_RULE)

ESGV42$ESG_LISTING_RULE <- ifelse(ESGV42$REGION.y=="International",ESGV42$ESG_LISTING_RULE.x,ESGV42$ESG_LISTING_RULE.y)
ESGV42$ESG_LISTING_RULE <- ifelse(ESGV42$ESG_LISTING_RULE==1,0,1)
ESGV42$ESG_LISTING_RULE <- as.factor(ESGV42$ESG_LISTING_RULE)

ESGV52$ESG_LISTING_RULE <- ifelse(ESGV52$REGION.y=="International",ESGV52$ESG_LISTING_RULE.x,ESGV52$ESG_LISTING_RULE.y)
ESGV52$ESG_LISTING_RULE <- ifelse(ESGV52$ESG_LISTING_RULE==1,0,1)
ESGV52$ESG_LISTING_RULE <- as.factor(ESGV52$ESG_LISTING_RULE)

ESGV62$ESG_LISTING_RULE <- ifelse(ESGV62$REGION.y=="International",ESGV62$ESG_LISTING_RULE.x,ESGV62$ESG_LISTING_RULE.y)
ESGV62$ESG_LISTING_RULE <- ifelse(ESGV62$ESG_LISTING_RULE==1,0,1)
ESGV62$ESG_LISTING_RULE <- as.factor(ESGV62$ESG_LISTING_RULE)

# Set the group type variable right (METRIC_TYPE)
ESGV12$METRIC_TYPE <- ifelse(ESGV12$REGION.y=="International",ESGV12$GROUP_TYPE.y,ESGV12$GROUP_TYPE.x)
ESGV12$METRIC_TYPE <- ifelse(ESGV12$METRIC_TYPE==1,"E",ifelse(ESGV12$METRIC_TYPE==3,"G","S"))
ESGV12$METRIC_TYPE <- as.factor(ESGV12$METRIC_TYPE)

ESGV22$METRIC_TYPE <- ifelse(ESGV22$REGION.y=="International",ESGV22$GROUP_TYPE.y,ESGV22$GROUP_TYPE.x)
ESGV22$METRIC_TYPE <- ifelse(ESGV22$METRIC_TYPE==1, "E",ifelse(ESGV22$METRIC_TYPE==3,"G","S"))
ESGV22$METRIC_TYPE <- as.factor(ESGV22$METRIC_TYPE)

ESGV32$METRIC_TYPE <- ifelse(ESGV32$REGION.y=="International",ESGV32$GROUP_TYPE.y,ESGV32$GROUP_TYPE.x)
ESGV32$METRIC_TYPE <- ifelse(ESGV32$METRIC_TYPE==1, "E",ifelse(ESGV32$METRIC_TYPE==3,"G","S"))
ESGV32$METRIC_TYPE <- as.factor(ESGV32$METRIC_TYPE)

ESGV42$METRIC_TYPE <- ifelse(ESGV42$REGION.y=="International",ESGV42$GROUP_TYPE.y,ESGV42$GROUP_TYPE.y)
ESGV42$METRIC_TYPE <- ifelse(ESGV42$METRIC_TYPE==1, "E",ifelse(ESGV42$METRIC_TYPE==3,"G","S"))
ESGV42$METRIC_TYPE <- as.factor(ESGV42$METRIC_TYPE)

ESGV52$METRIC_TYPE <- ifelse(ESGV52$REGION.y=="International",ESGV52$GROUP_TYPE.y,ESGV52$GROUP_TYPE.x)
ESGV52$METRIC_TYPE <- ifelse(ESGV52$METRIC_TYPE==1, "E",ifelse(ESGV52$METRIC_TYPE==3,"G","S"))
ESGV52$METRIC_TYPE <- as.factor(ESGV52$METRIC_TYPE)

ESGV62$METRIC_TYPE <- ifelse(ESGV62$REGION.y=="International",ESGV62$GROUP_TYPE.y,ESGV62$GROUP_TYPE.x)
ESGV62$METRIC_TYPE <- ifelse(ESGV62$METRIC_TYPE==1, "E",ifelse(ESGV62$METRIC_TYPE==3,"G","S"))
ESGV62$METRIC_TYPE <- as.factor(ESGV62$METRIC_TYPE)


# Calculate average
AESGV1 <- ESGV1 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))
AESGV2 <- ESGV2 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))
AESGV3 <- ESGV3 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))
AESGV4 <- ESGV4 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))
AESGV5 <- ESGV5 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))
AESGV6 <- ESGV6 %>% group_by(ESG_LISTING_RULE.y) %>% summarise(avg_cosine=mean(cosine))

AESGV12 <- ESGV12 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGV22 <- ESGV22 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGV32 <- ESGV32 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGV42 <- ESGV42 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGV52 <- ESGV52 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))
AESGV62 <- ESGV62 %>% group_by(ESG_LISTING_RULE, METRIC_TYPE) %>% summarise(avg_cosine=mean(cosine))

```

Show the results:
```{r}
# ESG mandatory and ESG voluntary --------------------------------------------------------------------

AESGMV1 
AESGMV2 
AESGMV3 
AESGMV4 
AESGMV5  
AESGMV6  

AESGMV12 
AESGMV22 
AESGMV32 
AESGMV42 
AESGMV52 
AESGMV62 

# ESG Mandatory and G Mandatory -----------------------------------------------------------------------------------------------------

AESGGM1 
AESGGM2 
AESGGM3 
AESGGM4 
AESGGM5
AESGGM6

AESGGM12
AESGGM22 
AESGGM32
AESGGM42 
AESGGM52 
AESGGM62

# ESG Voluntary and E voluntary -----------------------------------------------------------------------------------------------------------------

AESGEV1 
AESGEV2 
AESGEV3
AESGEV4
AESGEV5
AESGEV6 

AESGEV12 
AESGEV22 
AESGEV32
AESGEV42
AESGEV52 
AESGEV62 

# ESG BOTH (cross similarity) ----------------------------------------------------------------

AESGB1
AESGB2 
AESGB3
AESGB4
AESGB5
AESGB6

AESGB12
AESGB22
AESGB32 
AESGB42 
AESGB52 
AESGB62


# ESG Voluntary (listing rule) ---------------------------------------------------------------------

AESGV1
AESGV2 
AESGV3
AESGV4
AESGV5
AESGV6

AESGV12
AESGV22
AESGV32 
AESGV42 
AESGV52 
AESGV62 
```

## Regression
Perform a regression to test for significance in differences
```{r}
# ESG Mandatory and ESG Voluntary
model1 <- lm(cosine~M.x, data = ESGMV1)
model2 <- lm(cosine~M.x, data = ESGMV2)
model3 <- lm(cosine~M.x, data = ESGMV3)
model4 <- lm(cosine~M.x, data = ESGMV4)
model5 <- lm(cosine~M.x, data = ESGMV5)
model6 <- lm(cosine~M.x, data = ESGMV6)

# E
model12e <- lm(cosine~M, data = ESGMV12, subset=(METRIC_TYPE=="E"))
model22e <- lm(cosine~M, data = ESGMV22, subset=(METRIC_TYPE=="E"))
model32e <- lm(cosine~M, data = ESGMV32, subset=(METRIC_TYPE=="E"))
model42e <- lm(cosine~M, data = ESGMV42, subset=(METRIC_TYPE=="E"))
model52e <- lm(cosine~M, data = ESGMV52, subset=(METRIC_TYPE=="E"))
model62e <- lm(cosine~M, data = ESGMV62, subset=(METRIC_TYPE=="E"))

# S
model12s <- lm(cosine~M, data = ESGMV12, subset=(METRIC_TYPE=="S"))
model22s <- lm(cosine~M, data = ESGMV22, subset=(METRIC_TYPE=="S"))
model32s <- lm(cosine~M, data = ESGMV32, subset=(METRIC_TYPE=="S"))
model42s <- lm(cosine~M, data = ESGMV42, subset=(METRIC_TYPE=="S"))
model52s <- lm(cosine~M, data = ESGMV52, subset=(METRIC_TYPE=="S"))
model62s <- lm(cosine~M, data = ESGMV62, subset=(METRIC_TYPE=="S"))

# G
model12g <- lm(cosine~M, data = ESGMV12, subset=(METRIC_TYPE=="G"))
model22g <- lm(cosine~M, data = ESGMV22, subset=(METRIC_TYPE=="G"))
model32g <- lm(cosine~M, data = ESGMV32, subset=(METRIC_TYPE=="G"))
model42g <- lm(cosine~M, data = ESGMV42, subset=(METRIC_TYPE=="G"))
model52g <- lm(cosine~M, data = ESGMV52, subset=(METRIC_TYPE=="G"))
model62g <- lm(cosine~M, data = ESGMV62, subset=(METRIC_TYPE=="G"))

summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
summary(model6)

summary(model12e)
summary(model22e)
summary(model32e)
summary(model42e)
summary(model52e)
summary(model62e)

summary(model12s)
summary(model22s)
summary(model32s)
summary(model42s)
summary(model52s)
summary(model62s)

summary(model12g)
summary(model22g)
summary(model32g)
summary(model42g)
summary(model52g)
summary(model62g)

# ESG Mandatory and G Mandatory
modelx1 <- lm(cosine~GROUP_TYPE.x, data = ESGGM1)
modelx2 <- lm(cosine~GROUP_TYPE.x, data = ESGGM2)
modelx3 <- lm(cosine~GROUP_TYPE.x, data = ESGGM3)
modelx4 <- lm(cosine~GROUP_TYPE.x, data = ESGGM4)
modelx5 <- lm(cosine~GROUP_TYPE.x, data = ESGGM5)
modelx6 <- lm(cosine~GROUP_TYPE.x, data = ESGGM6)

# G
modelx12g <- lm(cosine~GROUP_TYPE, data = ESGGM12, subset=(METRIC_TYPE=="G"))
modelx22g <- lm(cosine~GROUP_TYPE, data = ESGGM22, subset=(METRIC_TYPE=="G"))
modelx32g <- lm(cosine~GROUP_TYPE, data = ESGGM32, subset=(METRIC_TYPE=="G"))
modelx42g <- lm(cosine~GROUP_TYPE, data = ESGGM42, subset=(METRIC_TYPE=="G"))
modelx52g <- lm(cosine~GROUP_TYPE, data = ESGGM52, subset=(METRIC_TYPE=="G"))
modelx62g <- lm(cosine~GROUP_TYPE, data = ESGGM62, subset=(METRIC_TYPE=="G"))

summary(modelx1)
summary(modelx2)
summary(modelx3)
summary(modelx4)
summary(modelx5)
summary(modelx6)

summary(modelx12g)
summary(modelx22g)
summary(modelx32g)
summary(modelx42g)
summary(modelx52g)
summary(modelx62g)

# ESG Voluntary and E Voluntary
modely1 <- lm(cosine~GROUP_TYPE.x, data = ESGEV1)
modely2 <- lm(cosine~GROUP_TYPE.x, data = ESGEV2)
modely3 <- lm(cosine~GROUP_TYPE.x, data = ESGEV3)
modely4 <- lm(cosine~GROUP_TYPE.x, data = ESGEV4)
modely5 <- lm(cosine~GROUP_TYPE.x, data = ESGEV5)
modely6 <- lm(cosine~GROUP_TYPE.x, data = ESGEV6)

summary(modely1)
summary(modely2)
summary(modely3)
summary(modely4)
summary(modely5)
summary(modely6)

# E
modely12e <- lm(cosine~GROUP_TYPE, data = ESGEV12, subset=(METRIC_TYPE=="E"))
modely22e <- lm(cosine~GROUP_TYPE, data = ESGEV22, subset=(METRIC_TYPE=="E"))
modely32e <- lm(cosine~GROUP_TYPE, data = ESGEV32, subset=(METRIC_TYPE=="E"))
modely42e <- lm(cosine~GROUP_TYPE, data = ESGEV42, subset=(METRIC_TYPE=="E"))
modely52e <- lm(cosine~GROUP_TYPE, data = ESGEV52, subset=(METRIC_TYPE=="E"))
modely62e <- lm(cosine~GROUP_TYPE, data = ESGEV62, subset=(METRIC_TYPE=="E"))

summary(modely12e)
summary(modely22e)
summary(modely32e)
summary(modely42e)
summary(modely52e)
summary(modely62e)


# ESG Voluntary with focus on ESG listing rule
modela1 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV1)
modela2 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV2)
modela3 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV3)
modela4 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV4)
modela5 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV5)
modela6 <- lm(cosine~ESG_LISTING_RULE.y, data = ESGV6)

summary(modela1)
summary(modela2)
summary(modela3)
summary(modela4)
summary(modela5)
summary(modela6)

```

#H4. ESG keywords analysis
Hypothesis 4 focuses on the frequency of ESG key topics among the 4 groups (ESG-M, ESG-V, E-V, G-V). It is examined if certain document groups contain significantly more ESG key topics. In order to construct a list with ESG key topics, a document with either E, S, or G metrics is used. Metrics in this document are categorized by theme and type (E/S/G). Instead of using all the words that are used to describe the metric, the text is tokenized and only the most important terms are kept. This is to make sure that the data does not contain too much generic words that do not specifically identify the metric (for example stop words like "the" "and" or generic verbs like "have" "can"). The importance of words is determined by calculating the log_TFIDF of every token in an ESG metric text document. Subsequently, the highest ranked words are selected. This is done manually, to avoid that there are still generic words in the ESG key word list. Selecting only the top results, is what distincts this exercise from what was done at hypothesis 3 (cosine similarity between an E, S, or G document containing multiple metrics). A total of 41 ESG metrics is used, and they are categorized among 15 ESG themes. So, analysis can be done per theme, which therefore can give more detailed insights. The meta data on the metrics is contained in the file "Meta_Data_Metrics.csv" and will be merged with the tokenized text. After the key ESG terms are determined per metric, they are saved in a list "Metrics_Keywords.csv". A next step is to use this list as a filter on the whole corpus of ESG, E, and G regulations (Processed_Data). There are no separate sub-samples created for this task (as opposed to H3). This is because there is no global weighting variable used on the regulatory documents, which can be influenced by the overall frequency of tokens in the sample. Instead, the total frequency of words, per metric, per GROUP_ID document is calculated, and transformed to log2. Log transformation is applied because of the varying document length. 

## Select ESG key topics
Use the Metrics_Data.RData to define the key words for every ESG metric. Importance of an ESG key word is determined by looking at the key expressions with the highest log TFIDF. The final selection is checked manually, to avoid generic terms being included as an ESG key term. 
```{r include=FALSE}
library(readr)
Meta_Data_Metrics <- read_delim("Meta_Data_Metrics.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
```

The meta data is merged with the metrics data
```{r}
# Final removal of special characters within lemma
Metrics_Data$lemma <- gsub('[\'’]','', Metrics_Data$lemma)
Metrics_Data$lemma <- gsub("[^A-Za-z]","", Metrics_Data$lemma)
Metrics_Data$lemma <- as.factor(Metrics_Data$lemma)
Metrics_Data <- Metrics_Data[!(is.na(Metrics_Data$lemma) | Metrics_Data$lemma==""), ]

# Set variables to factor variables
Meta_Data_Metrics <- lapply(Meta_Data_Metrics, as.character)
Meta_Data_Metrics <- lapply(Meta_Data_Metrics, factor)
Meta_Data_Metrics <- data.frame(Meta_Data_Metrics)

Metrics_Data <- lapply(Metrics_Data, as.character)
Metrics_Data <- lapply(Metrics_Data, factor)
Metrics_Data <- data.frame(Metrics_Data)

# Merge data
Metrics_Data <- merge(Metrics_Data,Meta_Data_Metrics,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)
```

Calculate the term frequencies and global weights, and make a final list with key words per metric based on this. 
```{r}
# Calculate local weights
Metrics_Data_Grouped <- Metrics_Data %>% group_by(doc_id, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(doc_id))

# Calculate global weights
Metrics_Data_Grouped <- Metrics_Data_Grouped %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

# Determine which to keep by creating a list of most important key terms per metric, based on log TFIDF. 
Metrics_Data_Grouped <- Metrics_Data_Grouped[order(Metrics_Data_Grouped$doc_id, -Metrics_Data_Grouped$LOG_TFIDF),]
Metrics_Data_Grouped$row_num <- seq.int(nrow(Metrics_Data_Grouped)) 
Metrics_Data_Grouped <- merge(Metrics_Data_Grouped,Meta_Data_Metrics,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)
Metrics_Data_Grouped <- Metrics_Data_Grouped[Metrics_Data_Grouped$lemma!="can", ]

# Load in list to filter on
Metrics_Keywords <- read_delim("Metrics_Keywords.csv",
    delim = ";", escape_double = FALSE, trim_ws=TRUE)

# Filter the data frame based on the list with the most important key terms 
Metrics_Data_Grouped <- merge(Metrics_Data_Grouped,Metrics_Keywords, by.x="doc_id", by.y ="doc_id",all.x = TRUE)

Metrics_Data_Grouped$lemma <- as.character(Metrics_Data_Grouped$lemma)
Metrics_Data_Grouped$filter <- ifelse(str_detect(Metrics_Data_Grouped$keywords, Metrics_Data_Grouped$lemma), 1, 0)
Metrics_Data_Grouped <- Metrics_Data_Grouped[Metrics_Data_Grouped$filter==1, ]
Metrics_Data_Grouped$lemma <- as.factor(Metrics_Data_Grouped$lemma)

# Change column name and subset to keep only columns that are useful for further analysis
colnames(Metrics_Data_Grouped)[1] <- "METRIC_ID"
colnames(Metrics_Data_Grouped)[18] <- "THEME_TYPE"
Metrics_Data_Grouped <- Metrics_Data_Grouped[ ,c("METRIC_ID","lemma","THEME_ID","CORE","THEME_TYPE","THEME","METRIC")]
```

Subsequently, this data is merged with the Regulations data by using the lemma (the data is Total_Sample.RData (calculated for H3) and already on term level and has counted term per group_id, and their corresponding global weight and overall weight). Filter out observations that do not contain a lemma from the keyword list. Subsequently, summarize by summing up frequencies that belong to the same GROUP_ID and the same THEME.
```{r}
# Merge total sample with ESG key words. Lemma's that are not an ESG keywords are dropped from the sample (sample goes from 46574 to 9300 obs.)
Keywords_Sample <- merge(Metrics_Data_Grouped,Total_Sample,by.x = "lemma",by.y = "lemma",all.x = FALSE, all.y=FALSE)

# Remove duplicate lemma's within the same metric theme and the same doc group
Keywords_Sample <- Keywords_Sample %>% distinct(GROUP_ID, lemma, THEME_ID, .keep_all= TRUE)

# Summarize to get the frequency per THEME per GROUP_ID
Keywords_Sample <- Keywords_Sample %>% group_by(GROUP_ID, THEME_ID) %>% summarise(
                  NTF = sum(TF),
                  Total_TF=max(Total_TF),
                    Max_TF=max(Max_TF),
                    N_DOC=max(N_DOC),
                    R_TF=sum(R_TF), 
                    A_TF=(0.5+((NTF/Max_TF)*0.5)),
                    L_TF=(log2(NTF+1)),
                    DF=mean(DF)) %>% ungroup()

Keywords_Sample <- Keywords_Sample %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

# Merge with group data
Group_Data <- Group_Data %>% distinct(GROUP_ID, .keep_all = TRUE)
Keywords_Sample <- merge(Keywords_Sample,Group_Data,by.x = "GROUP_ID", by.y = "GROUP_ID")

# Merge with metrics meta data
Theme_Data <- Meta_Data_Metrics %>% distinct(THEME_ID, .keep_all = TRUE)
colnames(Theme_Data)[1] <- "METRIC_ID"
colnames(Theme_Data)[4] <- "THEME_TYPE"

Keywords_Sample <- merge(Keywords_Sample, Theme_Data, by.x = "THEME_ID", by.y = "THEME_ID")

# Drop theme/group combinations if theme does not match (e.g., governance metric matched with environmental document)
Keywords_Sample <- subset(Keywords_Sample, GROUP_TYPE=="G" & THEME_TYPE=="G"  | 
                             GROUP_TYPE=="E" & THEME_TYPE=="E" | 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="E"| 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="S" | 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="G", select = THEME_ID:METRIC)

```

## Calculate averages and visualize the results
First, the average log term frequencies are calculated for different groups. 
```{r}
# Average Log TF per THEME
Total_THEME <- Keywords_Sample %>% group_by(THEME) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average Log TF per THEME_TYPE, Theme, M
Total_THEME_TYPE <- Keywords_Sample %>% group_by(THEME_TYPE, THEME, M) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average Log TF per GROUP_TYPE+M, THEME, M
Average_THEME <- Keywords_Sample %>% group_by(GROUP_TYPE, M, THEME) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average Log TF per GROUP_TYPE+M, by THEME_TYPE
Average_THEME_TYPE <- Keywords_Sample %>% group_by(GROUP_TYPE, M, THEME_TYPE) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

Total_THEME
Total_THEME_TYPE
Average_THEME
Average_THEME_TYPE
```

The results are visualized, to see the most important ESG key topics. In order to do this, a grouping variable is created to identify one of the 4 groups (ESG Mandatory, ESG Voluntary, E Voluntary, and G Mandatory).
```{r}
# Get the GROUP_TYPE-M variable to identify each of the 4 groups easily when making graphs
Average_THEME$GROUP <- paste(Average_THEME$GROUP_TYPE,"_",Average_THEME$M)
Average_THEME_TYPE$GROUP <- paste(Average_THEME_TYPE$GROUP_TYPE,"_",Average_THEME_TYPE$M)

library(ggplot2)
library(ggpubr)

# Bar chart of average log frequency per one of the 4 groups by theme (THEME data)
graph1 <-ggplot(Average_THEME_TYPE, aes(x=GROUP, y=avgTF, fill=THEME_TYPE)) +
  geom_col(position=position_dodge2(preserve = "single")) +
  scale_fill_brewer(palette="Set2") +
  labs(y="Average TF", x="Group Type") +
  theme(text=element_text(size=12, face = "bold",  family="serif")) + 
  theme(axis.text.x = element_text(size=12, family="serif"),
          axis.text.y = element_text(size=12, family = "serif"))

graph2 <-ggplot(Average_THEME_TYPE, aes(x=GROUP, y=avgL_TF, fill=THEME_TYPE)) +
  geom_col(position=position_dodge2(preserve = "single")) +
  scale_fill_brewer(palette="Set2") +
  labs(y="Average Log TF", x="Group Type") +
  theme(text=element_text(size=12,  face="bold", family="serif")) + 
  theme(axis.text.x = element_text(size=12, family="serif"),
          axis.text.y = element_text(size=12, family = "serif"))

ggarrange(graph1, graph2)

# Bar chart of average log frequency per Theme type, per Theme, per Mandatory/voluntary
graph3 <- ggplot(Total_THEME_TYPE, aes(x=avgTF, y=reorder(THEME, avgTF), group=THEME_TYPE, fill=M)) +
  geom_col(position=position_dodge2(preserve = "single")) +
  scale_fill_brewer(palette="Set2") +
  labs(y="Theme", x="Average TF") +
  theme(text=element_text(size=12, face = "bold",  family="serif")) + 
  theme(axis.text.x = element_text(size=12, family="serif"),
          axis.text.y = element_text(size=12, family = "serif"))

graph3

graph4 <- ggplot(Total_THEME_TYPE, aes(x=avgL_TF, y=reorder(THEME, avgL_TF), group=THEME_TYPE, fill=M)) +
  geom_col(position=position_dodge2(preserve = "single")) +
  scale_fill_brewer(palette="Set2") +
  labs(y="Theme", x="Average Log TF") +
  theme(text=element_text(size=12, face = "bold",  family="serif")) + 
  theme(axis.text.x = element_text(size=12, family="serif"),
          axis.text.y = element_text(size=12, family = "serif"))

graph4

ggarrange(graph3, graph4)
```

## Regression
Regression models are made to analyze average frequency of ESG key topics between mandatory and voluntary regulations. Controls are added for ESG metric (on an ESG level and on a theme level) and for the GROUP TYPE (E,G, ESG), and if there is a stock exchange that has ESG reporting as a ESG listing rule in the region that the document applies to.  
```{r}
# Inspect the distribution of the dependent variable
hist(Keywords_Sample$NTF)
hist(Keywords_Sample$L_TF)
```

```{r}
# Set base variable for the dummy variables in the regression for easier interpretation
Keywords_Sample <- droplevels(Keywords_Sample)

Keywords_Sample <- Keywords_Sample %>%
  mutate(GROUP_TYPE = relevel(GROUP_TYPE, ref = "ESG"),
         THEME_TYPE = relevel(THEME_TYPE, ref = "G"),
         THEME=relevel(THEME, ref = "Governing purpose"))
         
# TF as dependent variable
Modelesg1 <- lm(NTF~M, data = Keywords_Sample)
Modelesg2 <- lm(NTF~M+GROUP_TYPE, data = Keywords_Sample)
Modelesg3 <- lm(NTF~M+THEME, data = Keywords_Sample)
Modelesg4 <- lm(NTF~M+GROUP_TYPE+THEME_TYPE, data = Keywords_Sample)
Modelesg5 <- lm(NTF~M+GROUP_TYPE+THEME, data = Keywords_Sample)
Modelesg6 <- lm(NTF~M+GROUP_TYPE+THEME+ESG_LISTING_RULE, data = Keywords_Sample)

# LOG TF as dependent variable (control for large documents)
Modelesg7 <- lm(L_TF~M, data = Keywords_Sample)
Modelesg8 <- lm(L_TF~M+GROUP_TYPE, data = Keywords_Sample)
Modelesg9 <- lm(L_TF~M+THEME, data = Keywords_Sample)
Modelesg10 <- lm(L_TF~M+GROUP_TYPE+THEME_TYPE, data = Keywords_Sample)
Modelesg11 <- lm(L_TF~M+GROUP_TYPE+THEME, data = Keywords_Sample)
Modelesg12 <- lm(L_TF~M+GROUP_TYPE+THEME+ESG_LISTING_RULE, data = Keywords_Sample)

# Get the results
summary(Modelesg1)
summary(Modelesg2)
summary(Modelesg3)
summary(Modelesg4)
summary(Modelesg5)
summary(Modelesg6)

summary(Modelesg7)
summary(Modelesg8)
summary(Modelesg9)
summary(Modelesg10)
summary(Modelesg11)
summary(Modelesg12)

```

Get the results in a table. 
```{r}
stargazer(Modelesg1, Modelesg2, Modelesg3, Modelesg4, Modelesg5, Modelesg6, type = 'text')
stargazer(Modelesg7, Modelesg8, Modelesg9, Modelesg10, Modelesg11, Modelesg12, type = 'text')
```

As a final check, the same regression models are calculated with robust standard errors. Robust standard errors do not influence the value of the coefficient, but can influence the significance of a coefficient. It is a more conservative standard error and can be used in case of heteroscedasticity among the residual errors. To test if there may be hetereskedacity, the Breusch-Pagan test is applied(Breusch & Pagan, 1979)

T.S. Breusch & A.R. Pagan (1979), A Simple Test for Heteroscedasticity and Random Coefficient Variation. Econometrica 47, 1287--1294
```{r}
### Testing for heteroskedasticity and accounting for it in the SE
Modelesg11
par(mfrow=c(2,2)) # get 4 charts in 1 panel
plot(Modelesg11)


# Breusch-Pagan test against heteroskedasticity. H0 assumes homoskedacity under the residual errors. If rejected, there is heteroscedasticity and too much variance is explained by additional explanatory variables. 
lmtest::bptest(Modelesg11)

# Remedy for heteroskedasticity: Use robust standard error. 
library(sandwich)

seBasic <- sqrt (diag ( vcov(Modelesg11)))
sewhite <- sqrt (diag ( vcovHC(Modelesg11, type="HC0")))
seClust <- sqrt (diag ( vcovHC(Modelesg11, cluster="GROUP_TYPE")))

stargazer(Modelesg11, Modelesg11, Modelesg11, se=list(seBasic, sewhite, seClust), type="text")
```

#Robustness Checks
The same analysis can be done with modifications to the processed data (only filtering noun POS). These alternate results can be found in Data_Analysis_Robustness

