---
title: "Data_Analysis_H3_H4"
author: "Susanne_Rehorst"
date: "3-6-2022"
output: html_document
---

# Data Analysis H3 H4
In the documents Data_Processing_Regulations.Rmd and Data_Processing_Metrics.Rmd, the data was cleaned and processed. In this markdown, analysis will be performed on this processed data for Hypothesis 3 (Document similarity) and Hypothesis 4 (Keyword analysis).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load or install packages:
```{r warning=FALSE}
library(dplyr)
library(stringr)
library(stargazer)
```

Set Working Directory
```{r}
setwd("~/Thesis")
```

## Load in the data
There are 3 data files used for this analysis. The first one is Descriptive_Data.RData, which contains the meta data for each document and descriptive statistics, like the amount of words and the readability of the document. The second one is Processed_Data.RData. This data file contains the tokenized regulations data, so that each row contains a token. The third data file that is loaded is Metrics_Data.RData. This file also contains tokenized data, but in this case it contains ESG metrics data.  
```{r}
load("Descriptive_Data.RData")
load("Processed_Data.RData")
load("Metrics_Data.RData")
```

# Hypothesis 3: Document Similarity

## Merging on group level
Documents are merged if they belong to the same group. In order to do this, group id and other metadata are merged with the processed_data file. 
```{r}
# Create subset of descriptive data to get meta data for groups
Group_Data <- Descriptive_Data[,c("DOC_ID", "ESG_LISTING_RULE","GROUP_ID","GROUP_TYPE","REGION","M")]

Group_Data <- lapply(Group_Data, as.character)
Group_Data <- lapply(Group_Data, factor)
Processed_Data$doc_id <- as.factor(Processed_Data$doc_id)
Group_Data <- data.frame(Group_Data)

Processed_Data <- merge(Processed_Data,Group_Data,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)

Group_Data <- Group_Data[,c("ESG_LISTING_RULE","GROUP_ID","GROUP_TYPE","REGION","M")]
Group_Data <- Group_Data %>% distinct(GROUP_ID, .keep_all = TRUE)

# Final removal of special characters within lemma
Processed_Data$lemma <- gsub('[\'’]','', Processed_Data$lemma)
Processed_Data$lemma <- gsub("[^A-Za-z]","", Processed_Data$lemma)
Processed_Data$lemma <- as.factor(Processed_Data$lemma)
Processed_Data <- Processed_Data[!(is.na(Processed_Data$lemma) | Processed_Data$lemma==""), ]
```

## Prepare sub-samples
Sub-samples need to be created, as document similarity can only be calculated between documents that belong to the same group. These groups are EGS Mandatory, ESG Voluntary, E Voluntary, and G Mandatory. For all 4 groups, an additional corpus is created that include the group + a document with E, S,and/or G key metrics, depending on the group. This allows to calculate the average similarity between these documents and ESG key metrics. After similarities are calculated, average similarities are compared across groups and tested for significance.  
```{r}
# ESG Mandatory (1 is without ESG metrics, and 2 is with ESG metrics)
ESG_Mandatory_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="ESG" & Processed_Data$M=="1" | Processed_Data$GROUP_ID=="42" 
                                  | Processed_Data$GROUP_ID=="43" | Processed_Data$GROUP_ID=="44", ] 
ESG_Mandatory_1 <- ESG_Mandatory_2[ESG_Mandatory_2$GROUP_ID!="42" & ESG_Mandatory_2$GROUP_ID!="43" & ESG_Mandatory_2$GROUP_ID!="44", ]
  
# G Mandatory
G_Mandatory_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="G" & Processed_Data$M=="1" | Processed_Data$GROUP_ID=="42", ] 
G_Mandatory_1 <- G_Mandatory_2[G_Mandatory_2$GROUP_ID!="42", ]

# ESG Voluntary
ESG_Voluntary_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="ESG" & Processed_Data$M=="0" | Processed_Data$GROUP_ID=="42" 
                                  | Processed_Data$GROUP_ID=="43" | Processed_Data$GROUP_ID=="44", ] 
ESG_Voluntary_1 <- ESG_Voluntary_2[ESG_Voluntary_2$GROUP_ID!="42" & ESG_Voluntary_2$GROUP_ID!="43" & ESG_Voluntary_2$GROUP_ID!="44", ]
  
# E Voluntary
E_Voluntary_2 <- Processed_Data[Processed_Data$GROUP_TYPE=="E" & Processed_Data$M=="0" | Processed_Data$GROUP_ID=="43", ] 
E_Voluntary_1 <- E_Voluntary_2[E_Voluntary_2$GROUP_ID!="43", ]

# ESG Mandatory + ESG Voluntary
ESG_Both1 <- rbind(ESG_Mandatory_1, ESG_Voluntary_1)
ESG_Both2 <- rbind(ESG_Mandatory_2, ESG_Voluntary_2)

# Sample for H4 (includes all documents except the ESG keyword documents, as ESG key word matching is done at later stage)
Total_Sample <- Processed_Data[Processed_Data$GROUP_ID!="42" & Processed_Data$GROUP_ID!="43" & Processed_Data$GROUP_ID!="44", ]

Total_Sample <- droplevels(Total_Sample)
ESG_Mandatory_1 <- droplevels(ESG_Mandatory_1)
ESG_Mandatory_2 <- droplevels(ESG_Mandatory_2)
G_Mandatory_1 <- droplevels(G_Mandatory_1)
G_Mandatory_2 <- droplevels(G_Mandatory_2)
ESG_Voluntary_1 <- droplevels(ESG_Voluntary_1)
ESG_Voluntary_2 <- droplevels(ESG_Voluntary_2)
E_Voluntary_1 <- droplevels(E_Voluntary_1)
E_Voluntary_2 <- droplevels(E_Voluntary_2)
ESG_Both1 <- droplevels(ESG_Both1)
ESG_Both2 <- droplevels(ESG_Both2)
```

## Local and Global weighting function
First, it is counted within each group, how many times a term occurs. Several local weighting functions are calculated, including Term frequency (TF), Total term frequency (Total_TF), Maximum term frequency (Max_TF), Relative term frequency (R_TF), Augmented term frequency (A_TF), and log term frequency (L_TF). In the first part of hypothesis 1, it was concluded that there is a wide variation in the length of documents. To control for different lengths of documents, normalization should be applied. This can be in the form of relative, log, or augmented form. Subsequently, the IDF controls weights globally. Words that appear very frequently in all of the documents get a lower global weight. Log2 is used instead of log10 as the range of data is not very large. 
```{r}
ESG_Mandatory_1 <- ESG_Mandatory_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Mandatory_1 <- ESG_Mandatory_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))
                        
ESG_Mandatory_2 <- ESG_Mandatory_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Mandatory_2 <- ESG_Mandatory_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

G_Mandatory_1 <- G_Mandatory_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
G_Mandatory_1 <- G_Mandatory_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

G_Mandatory_2 <- G_Mandatory_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
G_Mandatory_2 <- G_Mandatory_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Voluntary_1 <- ESG_Voluntary_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Voluntary_1 <- ESG_Voluntary_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Voluntary_2 <- ESG_Voluntary_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
ESG_Voluntary_2 <- ESG_Voluntary_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

E_Voluntary_1 <- E_Voluntary_1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
E_Voluntary_1 <- E_Voluntary_1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

E_Voluntary_2 <- E_Voluntary_2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))
                       
E_Voluntary_2 <- E_Voluntary_2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Both1 <- ESG_Both1 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

ESG_Both1 <- ESG_Both1 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

ESG_Both2 <- ESG_Both2 %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

ESG_Both2 <- ESG_Both2 %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

Total_Sample <- Total_Sample %>% group_by(GROUP_ID, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(GROUP_ID))

Total_Sample <- Total_Sample %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

```

## Document Term Matrix
Create document term matrix with different weighting schemes. Additional weight is calculated with Entropy functionality. 
```{r}
library(reshape2)
library(lsa)
# ESG Mandatory 1
ESG_M_1_0 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var ="TF")
ESG_M_1_1 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="L_TF")
ESG_M_1_2 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_M_1_3 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_M_1_4 <- acast(ESG_Mandatory_1, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_M_1_5 <- lw_tf(ESG_M_1_1)*entropy(ESG_M_1_0)
ESG_M_1_6 <- lw_tf(ESG_M_1_1)*gw_entropy(ESG_M_1_0)

ESG_M_1_1[is.na(ESG_M_1_1)] <- 0
ESG_M_1_2[is.na(ESG_M_1_2)] <- 0
ESG_M_1_3[is.na(ESG_M_1_3)] <- 0
ESG_M_1_4[is.na(ESG_M_1_4)] <- 0.5
ESG_M_1_5[is.na(ESG_M_1_5)] <- 0
ESG_M_1_6[is.na(ESG_M_1_6)] <- 0

# ESG Mandatory 2
ESG_M_2_0 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var ="TF")
ESG_M_2_1 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="L_TF")
ESG_M_2_2 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_M_2_3 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_M_2_4 <- acast(ESG_Mandatory_2, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_M_2_5 <- lw_tf(ESG_M_2_1)*entropy(ESG_M_2_0)
ESG_M_2_6 <- lw_tf(ESG_M_2_1)*gw_entropy(ESG_M_2_0)

ESG_M_2_1[is.na(ESG_M_2_1)] <- 0
ESG_M_2_2[is.na(ESG_M_2_2)] <- 0
ESG_M_2_3[is.na(ESG_M_2_3)] <- 0
ESG_M_2_4[is.na(ESG_M_2_4)] <- 0.5
ESG_M_2_5[is.na(ESG_M_2_5)] <- 0
ESG_M_2_6[is.na(ESG_M_2_6)] <- 0

# ESG Voluntary 1
ESG_V_1_0 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var ="TF")
ESG_V_1_1 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="L_TF")
ESG_V_1_2 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_V_1_3 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_V_1_4 <- acast(ESG_Voluntary_1, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_V_1_5 <- lw_tf(ESG_V_1_1)*entropy(ESG_V_1_0)
ESG_V_1_6 <- lw_tf(ESG_V_1_1)*gw_entropy(ESG_V_1_0)

ESG_V_1_1[is.na(ESG_V_1_1)] <- 0
ESG_V_1_2[is.na(ESG_V_1_2)] <- 0
ESG_V_1_3[is.na(ESG_V_1_3)] <- 0
ESG_V_1_4[is.na(ESG_V_1_4)] <- 0.5
ESG_V_1_5[is.na(ESG_V_1_5)] <- 0
ESG_V_1_6[is.na(ESG_V_1_6)] <- 0

# ESG Voluntary 2
ESG_V_2_0 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var ="TF")
ESG_V_2_1 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="L_TF")
ESG_V_2_2 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_V_2_3 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_V_2_4 <- acast(ESG_Voluntary_2, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_V_2_5 <- lw_tf(ESG_V_2_1)*entropy(ESG_V_2_0)
ESG_V_2_6 <- lw_tf(ESG_V_2_1)*gw_entropy(ESG_V_2_0)

ESG_V_2_1[is.na(ESG_V_2_1)] <- 0
ESG_V_2_2[is.na(ESG_V_2_2)] <- 0
ESG_V_2_3[is.na(ESG_V_2_3)] <- 0
ESG_V_2_4[is.na(ESG_V_2_4)] <- 0.5
ESG_V_2_5[is.na(ESG_V_2_5)] <- 0
ESG_V_2_6[is.na(ESG_V_2_6)] <- 0

# G Mandatory 1
G_M_1_0 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var ="TF")
G_M_1_1 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="L_TF")
G_M_1_2 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
G_M_1_3 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="R_TFIDF")
G_M_1_4 <- acast(G_Mandatory_1, lemma~GROUP_ID, value.var="A_TFIDF")
G_M_1_5 <- lw_tf(G_M_1_1)*entropy(G_M_1_0)
G_M_1_6 <- lw_tf(G_M_1_1)*gw_entropy(G_M_1_0)

G_M_1_1[is.na(G_M_1_1)] <- 0
G_M_1_2[is.na(G_M_1_2)] <- 0
G_M_1_3[is.na(G_M_1_3)] <- 0
G_M_1_4[is.na(G_M_1_4)] <- 0.5
G_M_1_5[is.na(G_M_1_5)] <- 0
G_M_1_6[is.na(G_M_1_6)] <- 0

# G Mandatory 2
G_M_2_0 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var ="TF")
G_M_2_1 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="L_TF")
G_M_2_2 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
G_M_2_3 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="R_TFIDF")
G_M_2_4 <- acast(G_Mandatory_2, lemma~GROUP_ID, value.var="A_TFIDF")
G_M_2_5 <- lw_tf(G_M_2_1)*entropy(G_M_2_0)
G_M_2_6 <- lw_tf(G_M_2_1)*gw_entropy(G_M_2_0)

G_M_2_1[is.na(G_M_2_1)] <- 0
G_M_2_2[is.na(G_M_2_2)] <- 0
G_M_2_3[is.na(G_M_2_3)] <- 0
G_M_2_4[is.na(G_M_2_4)] <- 0.5
G_M_2_5[is.na(G_M_2_5)] <- 0
G_M_2_6[is.na(G_M_2_6)] <- 0

# E Voluntary 1
E_V_1_0 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var ="TF")
E_V_1_1 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="L_TF")
E_V_1_2 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="LOG_TFIDF")
E_V_1_3 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="R_TFIDF")
E_V_1_4 <- acast(E_Voluntary_1, lemma~GROUP_ID, value.var="A_TFIDF")
E_V_1_5 <- lw_tf(E_V_1_1)*entropy(E_V_1_0)
E_V_1_6 <- lw_tf(E_V_1_1)*gw_entropy(E_V_1_0)

E_V_1_1[is.na(E_V_1_1)] <- 0
E_V_1_2[is.na(E_V_1_2)] <- 0
E_V_1_3[is.na(E_V_1_3)] <- 0
E_V_1_4[is.na(E_V_1_4)] <- 0.5
E_V_1_5[is.na(E_V_1_5)] <- 0
E_V_1_6[is.na(E_V_1_6)] <- 0

# E Voluntary 2
E_V_2_0 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var ="TF")
E_V_2_1 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="L_TF")
E_V_2_2 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="LOG_TFIDF")
E_V_2_3 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="R_TFIDF")
E_V_2_4 <- acast(E_Voluntary_2, lemma~GROUP_ID, value.var="A_TFIDF")
E_V_2_5 <- lw_tf(E_V_2_1)*entropy(E_V_2_0)
E_V_2_6 <- lw_tf(E_V_2_1)*gw_entropy(E_V_2_0)

E_V_2_1[is.na(E_V_2_1)] <- 0
E_V_2_2[is.na(E_V_2_2)] <- 0
E_V_2_3[is.na(E_V_2_3)] <- 0
E_V_2_4[is.na(E_V_2_4)] <- 0.5
E_V_2_5[is.na(E_V_2_5)] <- 0
E_V_2_6[is.na(E_V_2_6)] <- 0

# ESG Both 1
ESG_B_1_0 <- acast(ESG_Both1, lemma~GROUP_ID, value.var ="TF")
ESG_B_1_1 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="L_TF")
ESG_B_1_2 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_B_1_3 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_B_1_4 <- acast(ESG_Both1, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_B_1_5 <- lw_tf(ESG_B_1_1)*entropy(ESG_B_1_0)
ESG_B_1_6 <- lw_tf(ESG_B_1_1)*gw_entropy(ESG_B_1_0)

ESG_B_1_1[is.na(ESG_B_1_1)] <- 0
ESG_B_1_2[is.na(ESG_B_1_2)] <- 0
ESG_B_1_3[is.na(ESG_B_1_3)] <- 0
ESG_B_1_4[is.na(ESG_B_1_4)] <- 0.5
ESG_B_1_5[is.na(ESG_B_1_5)] <- 0
ESG_B_1_6[is.na(ESG_B_1_6)] <- 0

# ESG Both 2
ESG_B_2_0 <- acast(ESG_Both2, lemma~GROUP_ID, value.var ="TF")
ESG_B_2_1 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="L_TF")
ESG_B_2_2 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="LOG_TFIDF")
ESG_B_2_3 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="R_TFIDF")
ESG_B_2_4 <- acast(ESG_Both2, lemma~GROUP_ID, value.var="A_TFIDF")
ESG_B_2_5 <- lw_tf(ESG_B_2_1)*entropy(ESG_B_2_0)
ESG_B_2_6 <- lw_tf(ESG_B_2_1)*gw_entropy(ESG_B_2_0)

ESG_B_2_1[is.na(ESG_B_2_1)] <- 0
ESG_B_2_2[is.na(ESG_B_2_2)] <- 0
ESG_B_2_3[is.na(ESG_B_2_3)] <- 0
ESG_B_2_4[is.na(ESG_B_2_4)] <- 0.5
ESG_B_2_5[is.na(ESG_B_2_5)] <- 0
ESG_B_2_6[is.na(ESG_B_2_6)] <- 0
```

# Cosine similarity Matrix
```{r}
# ESG Mandatory 1
ESG_MS1 <- cosine(ESG_M_1_1)
ESG_MS2 <- cosine(ESG_M_1_2)
ESG_MS3 <- cosine(ESG_M_1_3)
ESG_MS4 <- cosine(ESG_M_1_4)
ESG_MS5 <- cosine(ESG_M_1_5)
ESG_MS6 <- cosine(ESG_M_1_6)

# ESG Mandatory 2
ESG_MS12 <- cosine(ESG_M_2_1)
ESG_MS22 <- cosine(ESG_M_2_2)
ESG_MS32 <- cosine(ESG_M_2_3)
ESG_MS42 <- cosine(ESG_M_2_4)
ESG_MS52 <- cosine(ESG_M_2_5)
ESG_MS62 <- cosine(ESG_M_2_6)

# ESG Voluntary 1
ESG_VS1 <- cosine(ESG_V_1_1)
ESG_VS2 <- cosine(ESG_V_1_2)
ESG_VS3 <- cosine(ESG_V_1_3)
ESG_VS4 <- cosine(ESG_V_1_4)
ESG_VS5 <- cosine(ESG_V_1_5)
ESG_VS6 <- cosine(ESG_V_1_6)

# ESG Voluntary 2
ESG_VS12 <- cosine(ESG_V_2_1)
ESG_VS22 <- cosine(ESG_V_2_2)
ESG_VS32 <- cosine(ESG_V_2_3)
ESG_VS42 <- cosine(ESG_V_2_4)
ESG_VS52 <- cosine(ESG_V_2_5)
ESG_VS62 <- cosine(ESG_V_2_6)

# G Mandatory 1
G_MS1 <- cosine(G_M_1_1)
G_MS2 <- cosine(G_M_1_2)
G_MS3 <- cosine(G_M_1_3)
G_MS4 <- cosine(G_M_1_4)
G_MS5 <- cosine(G_M_1_5)
G_MS6 <- cosine(G_M_1_6)

# G Mandatory 2
G_MS12 <- cosine(G_M_2_1)
G_MS22 <- cosine(G_M_2_2)
G_MS32 <- cosine(G_M_2_3)
G_MS42 <- cosine(G_M_2_4)
G_MS52 <- cosine(G_M_2_5)
G_MS62 <- cosine(G_M_2_6)

# E Voluntary 1
E_VS1 <- cosine(E_V_1_1)
E_VS2 <- cosine(E_V_1_2)
E_VS3 <- cosine(E_V_1_3)
E_VS4 <- cosine(E_V_1_4)
E_VS5 <- cosine(E_V_1_5)
E_VS6 <- cosine(E_V_1_6)

# E Voluntary 2
E_VS12 <- cosine(E_V_2_1)
E_VS22 <- cosine(E_V_2_2)
E_VS32 <- cosine(E_V_2_3)
E_VS42 <- cosine(E_V_2_4)
E_VS52 <- cosine(E_V_2_5)
E_VS62 <- cosine(E_V_2_6)

# ESG Both 1
ESG_BS1 <- cosine(ESG_B_1_1)
ESG_BS2 <- cosine(ESG_B_1_2)
ESG_BS3 <- cosine(ESG_B_1_3)
ESG_BS4 <- cosine(ESG_B_1_4)
ESG_BS5 <- cosine(ESG_B_1_5)
ESG_BS6 <- cosine(ESG_B_1_6)

# ESG Both 2
ESG_BS12 <- cosine(ESG_B_2_1)
ESG_BS22 <- cosine(ESG_B_2_2)
ESG_BS32 <- cosine(ESG_B_2_3)
ESG_BS42 <- cosine(ESG_B_2_4)
ESG_BS52 <- cosine(ESG_B_2_5)
ESG_BS62 <- cosine(ESG_B_2_6)


```

## Visualization
Results can be visualized with a heat map.
```{r}
heatmap(ESG_MS1)
```

## Calculating Difference-in-Means and test for significance (within groups and compared to ESG doc)
Now that the cosine similarity between documents is calculated, the average document similarity within each of the 4 groups is calculated. This difference is also tested on significance. For the group that also includes ESG metrics, the average cosine similarity is only calculated between the ESG documents and the other documents. 

Before average similarity can be calculated, the matrices need to be converted back to data frames. Also, they are merged with the Group_Data so that meta data can be added (this is done twice because a document pair consists of 2 documents). 
```{r}
# ESG Mandatory
ESGM1 <- data.frame(GROUP_ID1=rownames(ESG_MS1)[row(ESG_MS1)[upper.tri(ESG_MS1)]], 
                     GROUP_ID2=colnames(ESG_MS1)[col(ESG_MS1)[upper.tri(ESG_MS1)]],cosine=ESG_MS1[upper.tri(ESG_MS1)])
ESGM2 <- data.frame(GROUP_ID1=rownames(ESG_MS2)[row(ESG_MS2)[upper.tri(ESG_MS2)]], 
                     GROUP_ID2=colnames(ESG_MS2)[col(ESG_MS2)[upper.tri(ESG_MS2)]],cosine=ESG_MS2[upper.tri(ESG_MS2)])
ESGM3 <- data.frame(GROUP_ID1=rownames(ESG_MS3)[row(ESG_MS3)[upper.tri(ESG_MS3)]], 
                     GROUP_ID2=colnames(ESG_MS3)[col(ESG_MS3)[upper.tri(ESG_MS3)]],cosine=ESG_MS3[upper.tri(ESG_MS3)])
ESGM4 <- data.frame(GROUP_ID1=rownames(ESG_MS4)[row(ESG_MS4)[upper.tri(ESG_MS4)]], 
                     GROUP_ID2=colnames(ESG_MS4)[col(ESG_MS4)[upper.tri(ESG_MS4)]],cosine=ESG_MS4[upper.tri(ESG_MS4)])
ESGM5 <- data.frame(GROUP_ID1=rownames(ESG_MS5)[row(ESG_MS5)[upper.tri(ESG_MS5)]], 
                     GROUP_ID2=colnames(ESG_MS5)[col(ESG_MS5)[upper.tri(ESG_MS5)]],cosine=ESG_MS5[upper.tri(ESG_MS5)])
ESGM6 <- data.frame(GROUP_ID1=rownames(ESG_MS6)[row(ESG_MS6)[upper.tri(ESG_MS6)]], 
                     GROUP_ID2=colnames(ESG_MS6)[col(ESG_MS6)[upper.tri(ESG_MS6)]],cosine=ESG_MS6[upper.tri(ESG_MS6)])

ESGM12 <- data.frame(GROUP_ID1=rownames(ESG_MS12)[row(ESG_MS12)[upper.tri(ESG_MS12)]], 
                     GROUP_ID2=colnames(ESG_MS12)[col(ESG_MS12)[upper.tri(ESG_MS12)]],cosine=ESG_MS12[upper.tri(ESG_MS12)])
ESGM22 <- data.frame(GROUP_ID1=rownames(ESG_MS22)[row(ESG_MS22)[upper.tri(ESG_MS22)]], 
                     GROUP_ID2=colnames(ESG_MS22)[col(ESG_MS22)[upper.tri(ESG_MS22)]],cosine=ESG_MS22[upper.tri(ESG_MS22)])
ESGM32 <- data.frame(GROUP_ID1=rownames(ESG_MS32)[row(ESG_MS32)[upper.tri(ESG_MS32)]], 
                     GROUP_ID2=colnames(ESG_MS32)[col(ESG_MS32)[upper.tri(ESG_MS32)]],cosine=ESG_MS32[upper.tri(ESG_MS32)])
ESGM42 <- data.frame(GROUP_ID1=rownames(ESG_MS42)[row(ESG_MS42)[upper.tri(ESG_MS42)]], 
                     GROUP_ID2=colnames(ESG_MS42)[col(ESG_MS42)[upper.tri(ESG_MS42)]],cosine=ESG_MS42[upper.tri(ESG_MS42)])
ESGM52 <- data.frame(GROUP_ID1=rownames(ESG_MS52)[row(ESG_MS52)[upper.tri(ESG_MS52)]], 
                     GROUP_ID2=colnames(ESG_MS52)[col(ESG_MS52)[upper.tri(ESG_MS52)]],cosine=ESG_MS52[upper.tri(ESG_MS52)])
ESGM62 <- data.frame(GROUP_ID1=rownames(ESG_MS62)[row(ESG_MS62)[upper.tri(ESG_MS62)]], 
                     GROUP_ID2=colnames(ESG_MS62)[col(ESG_MS62)[upper.tri(ESG_MS62)]],cosine=ESG_MS62[upper.tri(ESG_MS62)])
# ESG Voluntary
ESGV1 <- data.frame(GROUP_ID1=rownames(ESG_VS1)[row(ESG_VS1)[upper.tri(ESG_VS1)]], 
                     GROUP_ID2=colnames(ESG_VS1)[col(ESG_VS1)[upper.tri(ESG_VS1)]],cosine=ESG_VS1[upper.tri(ESG_VS1)])
ESGV2 <- data.frame(GROUP_ID1=rownames(ESG_VS2)[row(ESG_VS2)[upper.tri(ESG_VS2)]], 
                     GROUP_ID2=colnames(ESG_VS2)[col(ESG_VS2)[upper.tri(ESG_VS2)]],cosine=ESG_VS2[upper.tri(ESG_VS2)])
ESGV3 <- data.frame(GROUP_ID1=rownames(ESG_VS3)[row(ESG_VS3)[upper.tri(ESG_VS3)]], 
                     GROUP_ID2=colnames(ESG_VS3)[col(ESG_VS3)[upper.tri(ESG_VS3)]],cosine=ESG_VS3[upper.tri(ESG_VS3)])
ESGV4 <- data.frame(GROUP_ID1=rownames(ESG_VS4)[row(ESG_VS4)[upper.tri(ESG_VS4)]], 
                     GROUP_ID2=colnames(ESG_VS4)[col(ESG_VS4)[upper.tri(ESG_VS4)]],cosine=ESG_VS4[upper.tri(ESG_VS4)])
ESGV5 <- data.frame(GROUP_ID1=rownames(ESG_VS5)[row(ESG_VS5)[upper.tri(ESG_VS5)]], 
                     GROUP_ID2=colnames(ESG_VS5)[col(ESG_VS5)[upper.tri(ESG_VS5)]],cosine=ESG_VS5[upper.tri(ESG_VS5)])
ESGV6 <- data.frame(GROUP_ID1=rownames(ESG_VS6)[row(ESG_VS6)[upper.tri(ESG_VS6)]], 
                     GROUP_ID2=colnames(ESG_VS6)[col(ESG_VS6)[upper.tri(ESG_VS6)]],cosine=ESG_VS6[upper.tri(ESG_VS6)])

ESGV12 <- data.frame(GROUP_ID1=rownames(ESG_VS12)[row(ESG_VS12)[upper.tri(ESG_VS12)]], 
                     GROUP_ID2=colnames(ESG_VS12)[col(ESG_VS12)[upper.tri(ESG_VS12)]],cosine=ESG_VS12[upper.tri(ESG_VS12)])
ESGV22 <- data.frame(GROUP_ID1=rownames(ESG_VS22)[row(ESG_VS22)[upper.tri(ESG_VS22)]], 
                     GROUP_ID2=colnames(ESG_VS22)[col(ESG_VS22)[upper.tri(ESG_VS22)]],cosine=ESG_VS22[upper.tri(ESG_VS22)])
ESGV32 <- data.frame(GROUP_ID1=rownames(ESG_VS32)[row(ESG_VS32)[upper.tri(ESG_VS32)]], 
                     GROUP_ID2=colnames(ESG_VS32)[col(ESG_VS32)[upper.tri(ESG_VS32)]],cosine=ESG_VS32[upper.tri(ESG_VS32)])
ESGV42 <- data.frame(GROUP_ID1=rownames(ESG_VS42)[row(ESG_VS42)[upper.tri(ESG_VS42)]], 
                     GROUP_ID2=colnames(ESG_VS42)[col(ESG_VS42)[upper.tri(ESG_VS42)]],cosine=ESG_VS42[upper.tri(ESG_VS42)])
ESGV52 <- data.frame(GROUP_ID1=rownames(ESG_VS52)[row(ESG_VS52)[upper.tri(ESG_VS52)]], 
                     GROUP_ID2=colnames(ESG_VS52)[col(ESG_VS52)[upper.tri(ESG_VS52)]],cosine=ESG_VS52[upper.tri(ESG_VS52)])
ESGV62 <- data.frame(GROUP_ID1=rownames(ESG_VS62)[row(ESG_VS62)[upper.tri(ESG_VS62)]], 
                     GROUP_ID2=colnames(ESG_VS62)[col(ESG_VS62)[upper.tri(ESG_VS62)]],cosine=ESG_VS62[upper.tri(ESG_VS62)])

# G Mandatory
GM1 <- data.frame(GROUP_ID1=rownames(G_MS1)[row(G_MS1)[upper.tri(G_MS1)]], 
                     GROUP_ID2=colnames(G_MS1)[col(G_MS1)[upper.tri(G_MS1)]],cosine=G_MS1[upper.tri(G_MS1)])
GM2 <- data.frame(GROUP_ID1=rownames(G_MS2)[row(G_MS2)[upper.tri(G_MS2)]], 
                     GROUP_ID2=colnames(G_MS2)[col(G_MS2)[upper.tri(G_MS2)]],cosine=G_MS2[upper.tri(G_MS2)])
GM3 <- data.frame(GROUP_ID1=rownames(G_MS3)[row(G_MS3)[upper.tri(G_MS3)]], 
                     GROUP_ID2=colnames(G_MS3)[col(G_MS3)[upper.tri(G_MS3)]],cosine=G_MS3[upper.tri(G_MS3)])
GM4 <- data.frame(GROUP_ID1=rownames(G_MS4)[row(G_MS4)[upper.tri(G_MS4)]], 
                     GROUP_ID2=colnames(G_MS4)[col(G_MS4)[upper.tri(G_MS4)]],cosine=G_MS4[upper.tri(G_MS4)])
GM5 <- data.frame(GROUP_ID1=rownames(G_MS5)[row(G_MS5)[upper.tri(G_MS5)]], 
                     GROUP_ID2=colnames(G_MS5)[col(G_MS5)[upper.tri(G_MS5)]],cosine=G_MS5[upper.tri(G_MS5)])
GM6 <- data.frame(GROUP_ID1=rownames(G_MS6)[row(G_MS6)[upper.tri(G_MS6)]], 
                     GROUP_ID2=colnames(G_MS6)[col(G_MS6)[upper.tri(G_MS6)]],cosine=G_MS6[upper.tri(G_MS6)])

GM12 <- data.frame(GROUP_ID1=rownames(G_MS12)[row(G_MS12)[upper.tri(G_MS12)]], 
                     GROUP_ID2=colnames(G_MS12)[col(G_MS12)[upper.tri(G_MS12)]],cosine=G_MS12[upper.tri(G_MS12)])
GM22 <- data.frame(GROUP_ID1=rownames(G_MS22)[row(G_MS22)[upper.tri(G_MS22)]], 
                     GROUP_ID2=colnames(G_MS22)[col(G_MS22)[upper.tri(G_MS22)]],cosine=G_MS22[upper.tri(G_MS22)])
GM32 <- data.frame(GROUP_ID1=rownames(G_MS32)[row(G_MS32)[upper.tri(G_MS32)]], 
                     GROUP_ID2=colnames(G_MS32)[col(G_MS32)[upper.tri(G_MS32)]],cosine=G_MS32[upper.tri(G_MS32)])
GM42 <- data.frame(GROUP_ID1=rownames(G_MS42)[row(G_MS42)[upper.tri(G_MS42)]], 
                     GROUP_ID2=colnames(G_MS42)[col(G_MS42)[upper.tri(G_MS42)]],cosine=G_MS42[upper.tri(G_MS42)])
GM52 <- data.frame(GROUP_ID1=rownames(G_MS52)[row(G_MS52)[upper.tri(G_MS52)]], 
                     GROUP_ID2=colnames(G_MS52)[col(G_MS52)[upper.tri(G_MS52)]],cosine=G_MS52[upper.tri(G_MS52)])
GM62 <- data.frame(GROUP_ID1=rownames(G_MS62)[row(G_MS62)[upper.tri(G_MS62)]], 
                     GROUP_ID2=colnames(G_MS62)[col(G_MS62)[upper.tri(G_MS62)]],cosine=G_MS62[upper.tri(G_MS62)])

# E Voluntary
EV1 <- data.frame(GROUP_ID1=rownames(E_VS1)[row(E_VS1)[upper.tri(E_VS1)]], 
                     GROUP_ID2=colnames(E_VS1)[col(E_VS1)[upper.tri(E_VS1)]],cosine=E_VS1[upper.tri(E_VS1)])
EV2 <- data.frame(GROUP_ID1=rownames(E_VS2)[row(E_VS2)[upper.tri(E_VS2)]], 
                     GROUP_ID2=colnames(E_VS2)[col(E_VS2)[upper.tri(E_VS2)]],cosine=E_VS2[upper.tri(E_VS2)])
EV3 <- data.frame(GROUP_ID1=rownames(E_VS3)[row(E_VS3)[upper.tri(E_VS3)]], 
                     GROUP_ID2=colnames(E_VS3)[col(E_VS3)[upper.tri(E_VS3)]],cosine=E_VS3[upper.tri(E_VS3)])
EV4 <- data.frame(GROUP_ID1=rownames(E_VS4)[row(E_VS4)[upper.tri(E_VS4)]], 
                     GROUP_ID2=colnames(E_VS4)[col(E_VS4)[upper.tri(E_VS4)]],cosine=E_VS4[upper.tri(E_VS4)])
EV5 <- data.frame(GROUP_ID1=rownames(E_VS5)[row(E_VS5)[upper.tri(E_VS5)]], 
                     GROUP_ID2=colnames(E_VS5)[col(E_VS5)[upper.tri(E_VS5)]],cosine=E_VS5[upper.tri(E_VS5)])
EV6 <- data.frame(GROUP_ID1=rownames(E_VS6)[row(E_VS6)[upper.tri(E_VS6)]], 
                     GROUP_ID2=colnames(E_VS6)[col(E_VS6)[upper.tri(E_VS6)]],cosine=E_VS6[upper.tri(E_VS6)])

EV12 <- data.frame(GROUP_ID1=rownames(E_VS12)[row(E_VS12)[upper.tri(E_VS12)]], 
                     GROUP_ID2=colnames(E_VS12)[col(E_VS12)[upper.tri(E_VS12)]],cosine=E_VS12[upper.tri(E_VS12)])
EV22 <- data.frame(GROUP_ID1=rownames(E_VS22)[row(E_VS22)[upper.tri(E_VS22)]], 
                     GROUP_ID2=colnames(E_VS22)[col(E_VS22)[upper.tri(E_VS22)]],cosine=E_VS22[upper.tri(E_VS22)])
EV32 <- data.frame(GROUP_ID1=rownames(E_VS32)[row(E_VS32)[upper.tri(E_VS32)]], 
                     GROUP_ID2=colnames(E_VS32)[col(E_VS32)[upper.tri(E_VS32)]],cosine=E_VS32[upper.tri(E_VS32)])
EV42 <- data.frame(GROUP_ID1=rownames(E_VS42)[row(E_VS42)[upper.tri(E_VS42)]], 
                     GROUP_ID2=colnames(E_VS42)[col(E_VS42)[upper.tri(E_VS42)]],cosine=E_VS42[upper.tri(E_VS42)])
EV52 <- data.frame(GROUP_ID1=rownames(E_VS52)[row(E_VS52)[upper.tri(E_VS52)]], 
                     GROUP_ID2=colnames(E_VS52)[col(E_VS52)[upper.tri(E_VS52)]],cosine=E_VS52[upper.tri(E_VS52)])
EV62 <- data.frame(GROUP_ID1=rownames(E_VS62)[row(E_VS62)[upper.tri(E_VS62)]], 
                     GROUP_ID2=colnames(E_VS62)[col(E_VS62)[upper.tri(E_VS62)]],cosine=E_VS62[upper.tri(E_VS62)])


# ESG Both
ESGB1 <- data.frame(GROUP_ID1=rownames(ESG_BS1)[row(ESG_BS1)[upper.tri(ESG_BS1)]], 
                     GROUP_ID2=colnames(ESG_BS1)[col(ESG_BS1)[upper.tri(ESG_BS1)]],cosine=ESG_BS1[upper.tri(ESG_BS1)])
ESGB2 <- data.frame(GROUP_ID1=rownames(ESG_BS2)[row(ESG_BS2)[upper.tri(ESG_BS2)]], 
                     GROUP_ID2=colnames(ESG_BS2)[col(ESG_BS2)[upper.tri(ESG_BS2)]],cosine=ESG_BS2[upper.tri(ESG_BS2)])
ESGB3 <- data.frame(GROUP_ID1=rownames(ESG_BS3)[row(ESG_BS3)[upper.tri(ESG_BS3)]], 
                     GROUP_ID2=colnames(ESG_BS3)[col(ESG_BS3)[upper.tri(ESG_BS3)]],cosine=ESG_BS3[upper.tri(ESG_BS3)])
ESGB4 <- data.frame(GROUP_ID1=rownames(ESG_BS4)[row(ESG_BS4)[upper.tri(ESG_BS4)]], 
                     GROUP_ID2=colnames(ESG_BS4)[col(ESG_BS4)[upper.tri(ESG_BS4)]],cosine=ESG_BS4[upper.tri(ESG_BS4)])
ESGB5 <- data.frame(GROUP_ID1=rownames(ESG_BS5)[row(ESG_BS5)[upper.tri(ESG_BS5)]], 
                     GROUP_ID2=colnames(ESG_BS5)[col(ESG_BS5)[upper.tri(ESG_BS5)]],cosine=ESG_BS5[upper.tri(ESG_BS5)])
ESGB6 <- data.frame(GROUP_ID1=rownames(ESG_BS6)[row(ESG_BS6)[upper.tri(ESG_BS6)]], 
                     GROUP_ID2=colnames(ESG_BS6)[col(ESG_BS6)[upper.tri(ESG_BS6)]],cosine=ESG_BS6[upper.tri(ESG_BS6)])

ESGB12 <- data.frame(GROUP_ID1=rownames(ESG_BS12)[row(ESG_BS12)[upper.tri(ESG_BS12)]], 
                     GROUP_ID2=colnames(ESG_BS12)[col(ESG_BS12)[upper.tri(ESG_BS12)]],cosine=ESG_BS12[upper.tri(ESG_BS12)])
ESGB22 <- data.frame(GROUP_ID1=rownames(ESG_BS22)[row(ESG_BS22)[upper.tri(ESG_BS22)]], 
                     GROUP_ID2=colnames(ESG_BS22)[col(ESG_BS22)[upper.tri(ESG_BS22)]],cosine=ESG_BS22[upper.tri(ESG_BS22)])
ESGB32 <- data.frame(GROUP_ID1=rownames(ESG_BS32)[row(ESG_BS32)[upper.tri(ESG_BS32)]], 
                     GROUP_ID2=colnames(ESG_BS32)[col(ESG_BS32)[upper.tri(ESG_BS32)]],cosine=ESG_BS32[upper.tri(ESG_BS32)])
ESGB42 <- data.frame(GROUP_ID1=rownames(ESG_BS42)[row(ESG_BS42)[upper.tri(ESG_BS42)]], 
                     GROUP_ID2=colnames(ESG_BS42)[col(ESG_BS42)[upper.tri(ESG_BS42)]],cosine=ESG_BS42[upper.tri(ESG_BS42)])
ESGB52 <- data.frame(GROUP_ID1=rownames(ESG_BS52)[row(ESG_BS52)[upper.tri(ESG_BS52)]], 
                     GROUP_ID2=colnames(ESG_BS52)[col(ESG_BS52)[upper.tri(ESG_BS52)]],cosine=ESG_BS52[upper.tri(ESG_BS52)])
ESGB62 <- data.frame(GROUP_ID1=rownames(ESG_BS62)[row(ESG_BS62)[upper.tri(ESG_BS62)]], 
                     GROUP_ID2=colnames(ESG_BS62)[col(ESG_BS62)[upper.tri(ESG_BS62)]],cosine=ESG_BS62[upper.tri(ESG_BS62)])
```

## Merge data
The data is merged by group ID. This way, a regression can be made to calculate the significance of the differences. 

----------------- Note: Change the reference in the summarize and regression code to variable "M". -------------------------------------

```{r}
# ESG mandatory and ESG voluntary --------------------------------------------------------------------
# Row bind
ESGMV1 <- rbind(ESGM1,ESGV1)
ESGMV2 <- rbind(ESGM2,ESGV2)
ESGMV3 <- rbind(ESGM3,ESGV3)
ESGMV4 <- rbind(ESGM4,ESGV4)
ESGMV5 <- rbind(ESGM5,ESGV5)
ESGMV6 <- rbind(ESGM6,ESGV6)

ESGMV12 <- rbind(ESGM12,ESGV12)
ESGMV22 <- rbind(ESGM22,ESGV22)
ESGMV32 <- rbind(ESGM32,ESGV32)
ESGMV42 <- rbind(ESGM42,ESGV42)
ESGMV52 <- rbind(ESGM52,ESGV52)
ESGMV62 <- rbind(ESGM62,ESGV62)

# Merge with metadata
ESGMV1 <- merge(ESGMV1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV1 <- merge(ESGMV1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV2 <- merge(ESGMV2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV2 <- merge(ESGMV2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV3 <- merge(ESGMV3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV3 <- merge(ESGMV3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV4 <- merge(ESGMV4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV4 <- merge(ESGMV4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV5 <- merge(ESGMV5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV5 <- merge(ESGMV5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV6 <- merge(ESGMV6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV6 <- merge(ESGMV6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

ESGMV12 <- merge(ESGMV12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV12 <- merge(ESGMV12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV22 <- merge(ESGMV22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV22 <- merge(ESGMV22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV32 <- merge(ESGMV32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV32 <- merge(ESGMV32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV42 <- merge(ESGMV42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV42 <- merge(ESGMV42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV52 <- merge(ESGMV52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV52 <- merge(ESGMV52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGMV62 <- merge(ESGMV62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGMV62 <- merge(ESGMV62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

#subset
ESGMV12 <- ESGMV12[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]
ESGMV22 <- ESGMV22[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]
ESGMV32 <- ESGMV32[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]
ESGMV42 <- ESGMV42[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]
ESGMV52 <- ESGMV52[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]
ESGMV62 <- ESGMV62[ESGMV12$GROUPID1="42" & ESGMV12$GROUPID1="43" & ESGMV12$GROUPID1="44" ,]

# Calculate average
AESGMV1 <- ESGMV1 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV2 <- ESGMV2 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV3 <- ESGMV3 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV4 <- ESGMV4 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV5 <- ESGMV5 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV6 <- ESGMV6 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

AESGMV12 <- ESGMV12 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV22 <- ESGMV22 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV32 <- ESGMV32 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV42 <- ESGMV42 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV52 <- ESGMV52 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGMV62 <- ESGMV62 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

# ESG Mandatory and G Mandatory -----------------------------------------------------------------------------------------------------
ESGGM1 <- rbind(ESGM1,GM1)
ESGGM2 <- rbind(ESGM2,GM2)
ESGGM3 <- rbind(ESGM3,GM3)
ESGGM4 <- rbind(ESGM4,GM4)
ESGGM5 <- rbind(ESGM5,GM5)
ESGGM6 <- rbind(ESGM6,GM6)

ESGGM12 <- rbind(ESGM12,GM12)
ESGGM22 <- rbind(ESGM22,GM22)
ESGGM32 <- rbind(ESGM32,GM32)
ESGGM42 <- rbind(ESGM42,GM42)
ESGGM52 <- rbind(ESGM52,GM52)
ESGGM62 <- rbind(ESGM62,GM62)

# Merge with metadata
ESGGM1 <- merge(ESGGM1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM1 <- merge(ESGGM1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM2 <- merge(ESGGM2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM2 <- merge(ESGGM2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM3 <- merge(ESGGM3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM3 <- merge(ESGGM3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM4 <- merge(ESGGM4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM4 <- merge(ESGGM4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM5 <- merge(ESGGM5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM5 <- merge(ESGGM5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM6 <- merge(ESGGM6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM6 <- merge(ESGGM6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

ESGGM12 <- merge(ESGGM12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM12 <- merge(ESGGM12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM22 <- merge(ESGGM22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM22 <- merge(ESGGM22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM32 <- merge(ESGGM32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM32 <- merge(ESGGM32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM42 <- merge(ESGGM42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM42 <- merge(ESGGM42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM52 <- merge(ESGGM52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM52 <- merge(ESGGM52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGGM62 <- merge(ESGGM62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGGM62 <- merge(ESGGM62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

#subset
ESGGM12 <- ESGGM12[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]
ESGGM22 <- ESGGM22[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]
ESGGM32 <- ESGGM32[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]
ESGGM42 <- ESGGM42[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]
ESGGM52 <- ESGGM52[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]
ESGGM62 <- ESGGM62[ESGGM12$GROUPID1="42" & ESGGM12$GROUPID1="43" & ESGGM12$GROUPID1="44" ,]

# Calculate average
AESGGM1 <- ESGGM1 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM2 <- ESGGM2 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM3 <- ESGGM3 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM4 <- ESGGM4 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM5 <- ESGGM5 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM6 <- ESGGM6 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

AESGGM12 <- ESGGM12 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM22 <- ESGGM22 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM32 <- ESGGM32 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM42 <- ESGGM42 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM52 <- ESGGM52 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGGM62 <- ESGGM62 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

# ESG Voluntary and E voluntary -------------------------------------------------------------------------------------------------------------------
ESGEV1 <- rbind(ESGV1,EV1)
ESGEV2 <- rbind(ESGV2,EV2)
ESGEV3 <- rbind(ESGV3,EV3)
ESGEV4 <- rbind(ESGV4,EV4)
ESGEV5 <- rbind(ESGV5,EV5)
ESGEV6 <- rbind(ESGV6,EV6)

ESGEV12 <- rbind(ESGV12,EV12)
ESGEV22 <- rbind(ESGV22,EV22)
ESGEV32 <- rbind(ESGV32,EV32)
ESGEV42 <- rbind(ESGV42,EV42)
ESGEV52 <- rbind(ESGV52,EV52)
ESGEV62 <- rbind(ESGV62,EV62)

# Merge with metadata
ESGEV1 <- merge(ESGEV1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV1 <- merge(ESGEV1,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV2 <- merge(ESGEV2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV2 <- merge(ESGEV2,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV3 <- merge(ESGEV3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV3 <- merge(ESGEV3,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV4 <- merge(ESGEV4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV4 <- merge(ESGEV4,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV5 <- merge(ESGEV5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV5 <- merge(ESGEV5,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV6 <- merge(ESGEV6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV6 <- merge(ESGEV6,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

ESGEV12 <- merge(ESGEV12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV12 <- merge(ESGEV12,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV22 <- merge(ESGEV22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV22 <- merge(ESGEV22,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV32 <- merge(ESGEV32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV32 <- merge(ESGEV32,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV42 <- merge(ESGEV42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV42 <- merge(ESGEV42,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV52 <- merge(ESGEV52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV52 <- merge(ESGEV52,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)
ESGEV62 <- merge(ESGEV62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID1,all.x=TRUE,all.y=FALSE)
ESGEV62 <- merge(ESGEV62,Group_Data, by.x=GROUP_ID1,by.y=GROUP_ID2,all.x=TRUE,all.y=FALSE)

#subset
ESGEV12 <- ESGEV12[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]
ESGEV22 <- ESGEV22[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]
ESGEV32 <- ESGEV32[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]
ESGEV42 <- ESGEV42[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]
ESGEV52 <- ESGEV52[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]
ESGEV62 <- ESGEV62[ESGEV12$GROUPID1="42" & ESGEV12$GROUPID1="43" & ESGEV12$GROUPID1="44" ,]


# Calculate average
AESGEV1 <- ESGEV1 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV2 <- ESGEV2 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV3 <- ESGEV3 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV4 <- ESGEV4 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV5 <- ESGEV5 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV6 <- ESGEV6 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

AESGEV12 <- ESGEV12 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV22 <- ESGEV22 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV32 <- ESGEV32 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV42 <- ESGEV42 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV52 <- ESGEV52 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGEV62 <- ESGEV62 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

# ESG Both ----------------------------------------------------------------------------------------------------------------------------------
# Merge with metadata
ESGB1 <- merge(ESGB1,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB2 <- merge(ESGB2,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB3 <- merge(ESGB3,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB4 <- merge(ESGB4,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB5 <- merge(ESGB5,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB6 <- merge(ESGB6,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)

ESGB12 <- merge(ESGB12,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB22 <- merge(ESGB22,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB32 <- merge(ESGB32,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB42 <- merge(ESGB42,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB52 <- merge(ESGB52,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGB62 <- merge(ESGB62,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)

#subset
ESGB12 <- ESGB12[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]
ESGB22 <- ESGB22[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]
ESGB32 <- ESGB32[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]
ESGB42 <- ESGB42[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]
ESGB52 <- ESGB52[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]
ESGB62 <- ESGB62[ESGB12$GROUP_ID="42" & ESGB12$GROUP_ID="43" & ESGB12$GROUP_ID="44" ,]

# Calculate average
AESGB1 <- ESGB1 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB2 <- ESGB2 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB3 <- ESGB3 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB4 <- ESGB4 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB5 <- ESGB5 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB6 <- ESGB6 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

AESGB12 <- ESGB12 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB22 <- ESGB22 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB32 <- ESGB32 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB42 <- ESGB42 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB52 <- ESGB52 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))
AESGB62 <- ESGB62 %>% group_by(M) %>% summarise(avg_cosine=mean(cosine))

# ESG Voluntary ---------------------------------------------------------------------
ESGV1 <- merge(ESGV1,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV2 <- merge(ESGV2,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV3 <- merge(ESGV3,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV4 <- merge(ESGV4,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV5 <- merge(ESGV5,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV6 <- merge(ESGV6,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)

ESGV12 <- merge(ESGV12,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV22 <- merge(ESGV22,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV32 <- merge(ESGV32,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV42 <- merge(ESGV42,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV52 <- merge(ESGV52,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)
ESGV62 <- merge(ESGV62,Group_Data, by.x=GROUP_ID,by.y=GROUP_ID,all.x=TRUE,all.y=FALSE)

#subset
ESGV12 <- ESGV12[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]
ESGV22 <- ESGV22[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]
ESGV32 <- ESGV32[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]
ESGV42 <- ESGV42[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]
ESGV52 <- ESGV52[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]
ESGV62 <- ESGV62[ESGV12$GROUP_ID="42" & ESGV12$GROUP_ID="43" & ESGV12$GROUP_ID="44" ,]

# Calculate average
AESGV1 <- ESGV1 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV2 <- ESGV2 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV3 <- ESGV3 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV4 <- ESGV4 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV5 <- ESGV5 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV6 <- ESGV6 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))

AESGV12 <- ESGV12 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV22 <- ESGV22 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV32 <- ESGV32 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV42 <- ESGV42 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV52 <- ESGV52 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))
AESGV62 <- ESGV62 %>% group_by(ESG_LISTING_RULE) %>% summarise(avg_cosine=mean(cosine))

```

## Regression
Perform a regression to test for significance in differences
```{r}
# ESG Mandatory and ESG Voluntary
model1 <- lm(cosine~M, data = ESGMV1)
model2 <- lm(cosine~M, data = ESGMV2)
model3 <- lm(cosine~M, data = ESGMV3)
model4 <- lm(cosine~M, data = ESGMV4)
model5 <- lm(cosine~M, data = ESGMV5)
model6 <- lm(cosine~M, data = ESGMV6)

model12 <- lm(cosine~M, data = ESGMV12)
model22 <- lm(cosine~M, data = ESGMV22)
model32 <- lm(cosine~M, data = ESGMV32)
model42 <- lm(cosine~M, data = ESGMV42)
model52 <- lm(cosine~M, data = ESGMV52)
model62 <- lm(cosine~M, data = ESGMV62)

summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
summary(model6)

summary(model12)
summary(model22)
summary(model32)
summary(model42)
summary(model52)
summary(model62)

# ESG Mandatory and G Mandatory
modelx1 <- lm(cosine~GROUP_TYPE data = ESGGM1)
modelx2 <- lm(cosine~GROUP_TYPE data = ESGGM2)
modelx3 <- lm(cosine~GROUP_TYPE data = ESGGM3)
modelx4 <- lm(cosine~GROUP_TYPE data = ESGGM4)
modelx5 <- lm(cosine~GROUP_TYPE data = ESGGM5)
modelx6 <- lm(cosine~GROUP_TYPE data = ESGGM6)

modelx12 <- lm(cosine~GROUP_TYPE data = ESGGM12)
modelx22 <- lm(cosine~GROUP_TYPE data = ESGGM22)
modelx32 <- lm(cosine~GROUP_TYPE data = ESGGM32)
modelx42 <- lm(cosine~GROUP_TYPE data = ESGGM42)
modelx52 <- lm(cosine~GROUP_TYPE data = ESGGM52)
modelx62 <- lm(cosine~GROUP_TYPE data = ESGGM62)

summary(modelx1)
summary(modelx2)
summary(modelx3)
summary(modelx4)
summary(modelx5)
summary(modelx6)

summary(modelx12)
summary(modelx22)
summary(modelx32)
summary(modelx42)
summary(modelx52)
summary(modelx62)

# ESG Voluntary and E Voluntary
modely1 <- lm(cosine~GROUP_TYPE, data = ESGEV1)
modely2 <- lm(cosine~GROUP_TYPE data = ESGEV2)
modely3 <- lm(cosine~GROUP_TYPE data = ESGEV3)
modely4 <- lm(cosine~GROUP_TYPE data = ESGEV4)
modely5 <- lm(cosine~GROUP_TYPE data = ESGEV5)
modely6 <- lm(cosine~GROUP_TYPE data = ESGEV6)

modely12 <- lm(cosine~GROUP_TYPE data = ESGEV12)
modely22 <- lm(cosine~GROUP_TYPE data = ESGEV22)
modely32 <- lm(cosine~GROUP_TYPE data = ESGEV32)
modely42 <- lm(cosine~GROUP_TYPE data = ESGEV42)
modely52 <- lm(cosine~GROUP_TYPE data = ESGEV52)
modely62 <- lm(cosine~GROUP_TYPE data = ESGEV62)

summary(modely1)
summary(modely2)
summary(modely3)
summary(modely4)
summary(modely5)
summary(modely6)

summary(modely12)
summary(modely22)
summary(modely32)
summary(modely42)
summary(modely52)
summary(modely62)

# ESG Both
# ESG Mandatory and ESG Voluntary
modelz1 <- lm(cosine~M, data = ESGB1)
modelz2 <- lm(cosine~M, data = ESGB2)
modelz3 <- lm(cosine~M, data = ESGB3)
modelz4 <- lm(cosine~M, data = ESGB4)
modelz5 <- lm(cosine~M, data = ESGB5)
modelz6 <- lm(cosine~M, data = ESGB6)

modelz12 <- lm(cosine~M, data = ESGB12)
modelz22 <- lm(cosine~M, data = ESGB22)
modelz32 <- lm(cosine~M, data = ESGB32)
modelz42 <- lm(cosine~M, data = ESGB42)
modelz52 <- lm(cosine~M, data = ESGB52)
modelz62 <- lm(cosine~M, data = ESGB62)

summary(modelz1)
summary(modelz2)
summary(modelz3)
summary(modelz4)
summary(modelz5)
summary(modelz6)

summary(modelz12)
summary(modelz22)
summary(modelz32)
summary(modelz42)
summary(modelz52)
summary(modelz62)

# E Voluntary with focus on ESG listing rule
modela1 <- lm(cosine~ESG_LISTING_RULE, data = ESGV1)
modela2 <- lm(cosine~ESG_LISTING_RULE, data = ESGV2)
modela3 <- lm(cosine~ESG_LISTING_RULE, data = ESGV3)
modela4 <- lm(cosine~ESG_LISTING_RULE, data = ESGV4)
modela5 <- lm(cosine~ESG_LISTING_RULE, data = ESGV5)
modela6 <- lm(cosine~ESG_LISTING_RULE, data = ESGV6)

modela12 <- lm(cosine~ESG_LISTING_RULE, data = ESGV12)
modela22 <- lm(cosine~ESG_LISTING_RULE, data = ESGV22)
modela32 <- lm(cosine~ESG_LISTING_RULE, data = ESGV32)
modela42 <- lm(cosine~ESG_LISTING_RULE, data = ESGV42)
modela52 <- lm(cosine~ESG_LISTING_RULE, data = ESGV52)
modela62 <- lm(cosine~ESG_LISTING_RULE, data = ESGV62)

summary(modela1)
summary(modela2)
summary(modela3)
summary(modela4)
summary(modela5)
summary(modela6)

summary(modela12)
summary(modela22)
summary(modela32)
summary(modela42)
summary(modela52)
summary(modela62)
```

#H4. ESG keywords analysis

## Select ESG key topics
Use the ESG Metrics documents to define the key words for every ESG metric. Importance of a ESG key metric is determined by looking at the key expressions with the highest TF. Use the metrics data for this. 
```{r include=FALSE}
library(readr)
Meta_Data_Metrics <- read_delim("Meta_Data_Metrics.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
Metrics_Keywords <- read_delim("Metrics_Keywords.csv",
    delim = ";", escape_double = FALSE, trim_ws=TRUE)
```

The meta data is merged with the metrics data
```{r}
# Final removal of special characters within lemma
Metrics_Data$lemma <- gsub('[\'’]','', Metrics_Data$lemma)
Metrics_Data$lemma <- gsub("[^A-Za-z]","", Metrics_Data$lemma)
Metrics_Data$lemma <- as.factor(Metrics_Data$lemma)
Metrics_Data <- Metrics_Data[!(is.na(Metrics_Data$lemma) | Metrics_Data$lemma==""), ]

# Set variables to factor variables
Meta_Data_Metrics <- lapply(Meta_Data_Metrics, as.character)
Meta_Data_Metrics <- lapply(Meta_Data_Metrics, factor)
Meta_Data_Metrics <- data.frame(Meta_Data_Metrics)

Metrics_Data <- lapply(Metrics_Data, as.character)
Metrics_Data <- lapply(Metrics_Data, factor)
Metrics_Data <- data.frame(Metrics_Data)

# Merge data
Metrics_Data <- merge(Metrics_Data,Meta_Data_Metrics,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)
```

Calculate the term frequencies and global weights, and make a final list with key words per metric based on this. 
```{r}
# Calculate local weights
Metrics_Data_Grouped <- Metrics_Data %>% group_by(doc_id, lemma) %>% summarize(
                  TF = n()) %>% mutate(
                    Total_TF=sum(TF),
                    Max_TF=max(TF),
                    R_TF=(TF/Total_TF),
                    A_TF=(0.5+((TF/Max_TF)*0.5)),
                    L_TF=(log2(TF+1))) %>% ungroup() %>% mutate(
                        N_DOC=n_distinct(doc_id))

# Calculate global weights
Metrics_Data_Grouped <- Metrics_Data_Grouped %>% group_by(lemma) %>% mutate(
                        DF=n()) %>% ungroup() %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

# Determine which to keep by creating a list of most important key terms per metric, based on log TFIDF. 
Metrics_Data_Grouped <- Metrics_Data_Grouped[order(Metrics_Data_Grouped$doc_id, -Metrics_Data_Grouped$LOG_TFIDF),]
Metrics_Data_Grouped$row_num <- seq.int(nrow(Metrics_Data_Grouped)) 
Metrics_Data_Grouped <- merge(Metrics_Data_Grouped,Meta_Data_Metrics,by.x = "doc_id", by.y = "DOC_ID", all.x = TRUE)
Metrics_Data_Grouped <- Metrics_Data_Grouped[Metrics_Data_Grouped$lemma!="can", ]

# Filter the data frame based on the list with the most important key terms 
Metrics_Data_Grouped <- merge(Metrics_Data_Grouped,Metrics_Keywords, by.x="doc_id", by.y ="doc_id",all.x = TRUE)

Metrics_Data_Grouped$lemma <- as.character(Metrics_Data_Grouped$lemma)
Metrics_Data_Grouped$filter <- ifelse(str_detect(Metrics_Data_Grouped$keywords, Metrics_Data_Grouped$lemma), 1, 0)
Metrics_Data_Grouped <- Metrics_Data_Grouped[Metrics_Data_Grouped$filter==1, ]
Metrics_Data_Grouped$lemma <- as.factor(Metrics_Data_Grouped$lemma)

# Change column name and subset to keep only columns that are useful for further analysis
colnames(Metrics_Data_Grouped)[1] <- "METRIC_ID"
colnames(Metrics_Data_Grouped)[18] <- "THEME_TYPE"
Metrics_Data_Grouped <- Metrics_Data_Grouped[ ,c("METRIC_ID","lemma","THEME_ID","CORE","THEME_TYPE","THEME","METRIC")]
```

Subsequently, this data is merged with the Regulations data by using the lemma (the data that is already on term level and has counted term per group_id, and their corresponding global weight and overall weight). Filter out observations that do not contain a lemma from the keyword list., Subsequently, summarize by summing up frequencies that belong to the same group and the same THEME.
```{r}
# Merge total sample with ESG key words. Lemma's that are not an ESG keywords are dropped from the sample (sample goes from 46574 to 9300)
Keywords_Sample <- merge(Metrics_Data_Grouped,Total_Sample,by.x = "lemma",by.y = "lemma",all.x = FALSE, all.y=FALSE)

# Remove duplicate lemma's within the same metric theme and the same doc group
Keywords_Sample <- Keywords_Sample %>% distinct(GROUP_ID, lemma, THEME_ID, .keep_all= TRUE)

# Summarize to get the frequency THEME per GROUP_ID
Keywords_Sample <- Keywords_Sample %>% group_by(GROUP_ID, THEME_ID) %>% summarise(
                  NTF = sum(TF),
                  Total_TF=max(Total_TF),
                    Max_TF=max(Max_TF),
                    N_DOC=max(N_DOC),
                    R_TF=sum(R_TF), 
                    A_TF=(0.5+((NTF/Max_TF)*0.5)),
                    L_TF=(log2(NTF+1)),
                    DF=mean(DF)) %>% ungroup()

Keywords_Sample <- Keywords_Sample %>% mutate(
                        IDF=1+(log2(N_DOC/(DF))),
                        LOG_TFIDF=((L_TF)*(IDF)),
                        R_TFIDF=(R_TF*IDF),
                        A_TFIDF=(A_TF*IDF))

# Merge with group data
Group_Data <- Group_Data %>% distinct(GROUP_ID, .keep_all = TRUE)
Keywords_Sample <- merge(Keywords_Sample,Group_Data,by.x = "GROUP_ID", by.y = "GROUP_ID")

# Merge with metrics meta data
Theme_Data <- Meta_Data_Metrics %>% distinct(THEME_ID, .keep_all = TRUE)
colnames(Theme_Data)[1] <- "METRIC_ID"
colnames(Theme_Data)[4] <- "THEME_TYPE"

Keywords_Sample <- merge(Keywords_Sample, Theme_Data, by.x = "THEME_ID", by.y = "THEME_ID")

# Drop theme/group combinations if theme does not match (e.g., governance metric matched with environmental document)
Keywords_Sample <- subset(Keywords_Sample, GROUP_TYPE=="G" & THEME_TYPE=="G"  | 
                             GROUP_TYPE=="E" & THEME_TYPE=="E" | 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="E"| 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="S" | 
                             GROUP_TYPE=="ESG" & THEME_TYPE=="G", select = THEME_ID:METRIC)

```

## Calculate averages and visualize the results
First, the average frequencies are calculated, by using several grouping variables.
```{r}
# Average TF per THEME
Total_THEME <- Keywords_Sample %>% group_by(THEME) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average TF per THEME TYPE
Total_THEME_TYPE <- Keywords_Sample %>% group_by(THEME_TYPE) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average Log TF per GROUP_TYPE+M, by THEME
Average_THEME <- Keywords_Sample %>% group_by(GROUP_TYPE, M, THEME, THEME_TYPE) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()

# Average Log TF per GROUP_TYPE+M, by THEME_TYPE
Average_THEME_TYPE <- Keywords_Sample %>% group_by(GROUP_TYPE, M, THEME_TYPE) %>% summarise(
                  avgTF=mean(NTF),
                  avgL_TF=mean(L_TF),
                  avgTFIDF=mean(LOG_TFIDF)) %>% ungroup()
```

The results are visualized, to see the most important ESG key topics. In order to do this, a grouping variable is created to identify one of the 4 groups (ESG Mandatory, ESG Voluntary, E Voluntary, and G Mandatory).
```{r}
library(ggplot2)
# Histogram of average log frequency per theme (TOTAL THEME data)


# Histogram of average log frequency per one of the 4 groups by theme (THEME data)
Average_THEME$GROUP <- paste(Average_THEME$GROUP_TYPE,"_",Average_THEME$M)

graph2 <-ggplot(Average_THEME, aes(x=THEME, y=avgL_TF, fill=THEME_TYPE)) +
  geom_bar(stat="identity")+theme_minimal()

# Histogram of average log frequency per one of the 4 groups by theme type (E/S/G) (THEME TYPE DATA)
Average_THEME_TYPE$GROUP <- paste(Average_THEME_TYPE$GROUP_TYPE,"_",Average_THEME_TYPE$M)
```

## Regression
Regression models are made to analyze frequency of ESG key topics between mandatory and voluntary regulations. Controls are added for ESG metric (on an ESG level and on a theme level), DOC GROUP, and if there is an ESG listing rule in the region of the document. 
```{r}
# Set base variable for the dummy variables in the regression for easier interpretation
Keywords_Sample <- droplevels(Keywords_Sample)

Keywords_Sample <- Keywords_Sample %>%
  mutate(GROUP_TYPE = relevel(GROUP_TYPE, ref = "ESG"),
         THEME_TYPE = relevel(THEME_TYPE, ref = "G"),
         THEME=relevel(THEME, ref = "Governing purpose"))
         
# TF as dependent variable
Modelesg1 <- lm(TF~M, data = Keywords_Sample)
Modelesg2 <- lm(TF~M+GROUP_TYPE, data = Keywords_Sample)
Modelesg3 <- lm(TF~M+GROUP_TYPE+THEME_Type, data = Keywords_Sample)
Modelesg4 <- lm(TF~M+GROUP_TYPE+THEME, data = Keywords_Sample)
Modelesg5 <- lm(TF~M+GROUP_TYPE+THEME_Type+ESG_LISTING_RULE, data = Keywords_Sample)
Modelesg6 <- lm(TF~M+GROUP_TYPE+THEME+ESG_LISTING_RULE, data = Keywords_Sample)

# LOG TF as dependent variable (control for large documents)
Modelesg7 <- lm(L_TF~M, data = Keywords_Sample)
Modelesg8 <- lm(L_TF~M+GROUP_TYPE, data = Keywords_Sample)
Modelesg9 <- lm(L_TF~M+GROUP_TYPE+THEME_Type, data = Keywords_Sample)
Modelesg10 <- lm(L_TF~M+GROUP_TYPE+THEME, data = Keywords_Sample)
Modelesg11 <- lm(L_TF~M+GROUP_TYPE+THEME_Type+ESG_LISTING_RULE, data = Keywords_Sample)
Modelesg12 <- lm(L_TF~M+GROUP_TYPE+THEME+ESG_LISTING_RULE, data = Keywords_Sample)

# Get the results
summary(modelesg1)
summary(modelesg2)
summary(modelesg3)
summary(modelesg4)
summary(modelesg5)
summary(modelesg6)

summary(modelesg7)
summary(modelesg8)
summary(modelesg9)
summary(modelesg10)
summary(modelesg11)
summary(modelesg12)

# Check with Log_TFIDF
# LOG TFIDF as dependent variable (if there are ESG keywords within the theme that appear in a lot of other documents, the TF is adjusted downwards)
Modelesg72 <- lm(LOG_TFIDF~M, data = Keywords_Sample)
Modelesg82 <- lm(LOG_TFIDF~M+GROUP_TYPE, data = Keywords_Sample)
Modelesg92 <- lm(LOG_TFIDF~M+GROUP_TYPE+THEME_Type, data = Keywords_Sample)
Modelesg102 <- lm(LOG_TFIDF~M+GROUP_TYPE+THEME, data = Keywords_Sample)
Modelesg112 <- lm(LOG_TFIDF~M+GROUP_TYPE+THEME_Type+ESG_LISTING_RULE, data = Keywords_Sample)
Modelesg122 <- lm(LOG_TFIDF~M+GROUP_TYPE+THEME+ESG_LISTING_RULE, data = Keywords_Sample)

# Get the results
summary(modelesg12)
summary(modelesg22)
summary(modelesg32)
summary(modelesg42)
summary(modelesg52)
summary(modelesg62)
```

Get the results in a table. 
```{r}
stargazer(modelesg1, modelesg2, modelesg3, modelesg4, modelesg5, modelesg6, type = 'text')
stargazer(modelesg7, modelesg8, modelesg9, modelesg10, modelesg11, modelesg12, type = 'text')
stargazer(modelesg12, modelesg22, modelesg32, modelesg42, modelesg52, modelesg62, type = 'text')
```

Do the same test with robust standard errors.

T.S. Breusch & A.R. Pagan (1979), A Simple Test for Heteroscedasticity and Random Coefficient Variation. Econometrica 47, 1287--1294
```{r}
### Testing for heteroskedasticity and accounting for it in the SE

modelesg1
par(mfrow=c(2,2)) # get 4 charts in 1 panel
plot(modelesg1)

# Breusch-Pagan test against heteroskedasticity. H0 assumes homoskedacity under the residual errors. If rejected, there is heteroskedacity and too much variance is explained by additional explanatory variables. 
lmtest::bptest(modelesg1)
lmtest::bptest(modelesg2)
lmtest::bptest(modelesg3)
lmtest::bptest(modelesg4)
lmtest::bptest(modelesg5)
lmtest::bptest(modelesg6)

# Remedy for heteroskedasticity: Use robust standard error. 

seBasic <- sqrt (diag ( vcov(modelesg1)))
sewhite <- sqrt (diag ( vcovHC(modelesg1, type="HC0")))
seClust1 <- sqrt (diag ( vcovHC(modelesg1, cluster="GROUP_TYPE")))
seClust2 <- sqrt (diag ( vcovHC(modelesg1, cluster="THEME_TYPE")))

stargazer(modelesg1, modelesg1, modelesg1, se=list(seBasic, sewhite, seClust1, seClust2), type="text")
```

#Robustness Checks
The same analysis can be done with modifications to the processed data (stemming and/or only filtering noun POS). These alternate results can be found in Data_Analysis_Robustness.Rmd

