---
title: "Data_Analysis H1 H2"
author: "Susanne_Rehorst"
date: "25-5-2022"
output: html_document
---

# Data Analysis H1 & H2
In the documents Data_Processing_Regulations.Rmd and Data_Processing_Metrics.Rmd, the data was cleaned and processed. In this markdown, analysis will be performed on this processed data for Hypothesis 1 and Hypothesis 2 (readability and linguistic characteristics)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load or install packages:
```{r}
library(dplyr)
library(stringr)
```

Set Working Directory
```{r}
setwd("~/Thesis")
```

## Load in the data
There are 3 data files used for this analysis. The first one is Descriptive_Data.RData, which contains the meta data for each document and descriptive statistics, like the amount of words and the readability of the document. The second one is Processed_Data.RData. This data file contains the tokenized regulations data, so that each row contains a token. The third data file that is loaded is Metrics_Data.RData. This file also contains tokenized data, but in this case it contains ESG metrics data.  
```{r}
load("Descriptive_Data.RData")
load("Processed_Data.RData")
load("Metrics_Data.RData")
```

# Hypothesis 1: Quantity and Readability 

## Quantity
Merge the words and non-words. Happens in case there are list that do not have a period at the end. 
```{r}
Descriptive_Data$totalwords <- rowSums(Descriptive_Data[,c(4,5)])
```

Sum totalwords and sentences if they apply to the same GroupID AND to the same DOC_TYPE and the same M type. In order to do this, a merge ID variable is created that uniquely identifies these groups. 
```{r}
# Create the merge ID variable
names <- c("GROUP_ID","DOC_TYPE","M")
Descriptive_Data[,names] <- lapply(Descriptive_Data[,names], as.character)
Descriptive_Data$MERGE_ID <- paste(Descriptive_Data$GROUP_TYPE, Descriptive_Data$GROUP_ID,Descriptive_Data$DOC_TYPE,Descriptive_Data$M)

# Set variables back to factor
names <- c("MERGE_ID","DOC_ID","GROUP_ID","GROUP_TYPE","DOC_TYPE","M","REGION")
Descriptive_Data[,names] <- lapply(Descriptive_Data[,names], factor)

# Get merged data by grouping on MERGE_ID
DOC_Quantity <- Descriptive_Data %>% group_by(MERGE_ID) %>%
  summarize(totalwords=sum(totalwords),
            sents=sum(sents))

# Split the MERGE_ID variable
DOC_Quantity[c('GROUP_TYPE', 'GROUP_ID', 'DOC_TYPE', 'M')] <- str_split_fixed(DOC_Quantity$MERGE_ID,' ',4)

# Create new merge variable
DOC_Quantity$MERGE_ID <- paste(DOC_Quantity$DOC_TYPE,DOC_Quantity$M)

# Set variables to factor
names <- c("MERGE_ID","GROUP_TYPE", "GROUP_ID","DOC_TYPE","M")
DOC_Quantity[,names] <- lapply(DOC_Quantity[,names], factor)

# Remove Group ID 42, 43, 44, as they do not contain ESG regulations (only key ESG metrics)
DOC_Quantity <- DOC_Quantity[DOC_Quantity$GROUP_ID!="42" & DOC_Quantity$GROUP_ID!="43" & DOC_Quantity$GROUP_ID!="44", ]
DOC_Quantity <- droplevels(DOC_Quantity)
```

Get the summary statistics for the aggregated data set.
```{r}
DOC_Stats <- DOC_Quantity %>%                              
  group_by(MERGE_ID) %>% 
  summarize(N=length(MERGE_ID),
            w_min = min(totalwords),
            w_q1 = quantile(totalwords, 0.25),
            w_median = median(totalwords),
            w_mean = mean(totalwords),
            w_q3 = quantile(totalwords, 0.75),
            w_max = max(totalwords),
            w_SD=sd(totalwords),
            s_min = min(sents),
            s_q1 = quantile(sents, 0.25),
            s_median = median(sents),
            s_mean = mean(sents),
            s_q3 = quantile(sents, 0.75),
            s_max = max(sents),
            s_SD=sd(sents))

DOC_Stats
```

Next, analysis is performed on group level. 
```{r}
# Group the data by Group_ID
Group_Quantity <- Descriptive_Data %>%
  group_by(GROUP_ID, GROUP_TYPE, M) %>%
  summarize(totalwords=sum(totalwords),
            sentences=sum(sents)) %>% ungroup()

# Remove Group ID 42, 43, 44, as they do not contain ESG regulations (only key ESG metrics)
Group_Quantity <- Group_Quantity[Group_Quantity$GROUP_ID!="42" & Group_Quantity$GROUP_ID!="43" & Group_Quantity$GROUP_ID!="44", ]
Group_Quantity <- droplevels(Group_Quantity)

# Get summary statistics 
Group_Stats <- Group_Quantity %>%                              
  group_by(GROUP_TYPE, M) %>% 
  summarize(
            w_min = min(totalwords),
            w_q1 = quantile(totalwords, 0.25),
            w_median = median(totalwords),
            w_mean = mean(totalwords),
            w_q3 = quantile(totalwords, 0.75),
            w_max = max(totalwords),
            w_SD=sd(totalwords),
            s_min = min(sentences),
            s_q1 = quantile(sentences, 0.25),
            s_median = median(sentences),
            s_mean = mean(sentences),
            s_q3 = quantile(sentences, 0.75),
            s_max = max(sentences),
            s_SD=sd(sentences))

Group_Stats
```

It is calculated what percentage of ESG group documents is made out of pure governance documents by combining information from DOC_Quantity and GROUP_Quantity. Also, merge those 2 documents with country to get more insights into countries that have a high amount of regulations and countries that have less. So all this information is summarized in the Results section. 
```{r}
# Create GROUP_ID, REGION identifier
Country_ID <- Descriptive_Data[,c(50,59)]
Country_ID <- distinct(Country_ID)

DOC_Quantity <- merge(DOC_Quantity, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
Group_Quantity <- merge(Group_Quantity, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
```

Test for significance. Also, log of totalwords and sentences is taken to create 2 new variables. In case the data is heavily skewed towards large numbers, these variables can be used. So, models with log transformed variables are included as a robustness check. 
```{r}
# Create log transformed variables
Group_Quantity$logwords <- log(Group_Quantity$totalwords)
Group_Quantity$logsents <- log(Group_Quantity$sentences)

# Significance between M and V (group level)
model1 <- lm(totalwords ~ M, data = Group_Quantity)
model2 <- lm(sentences ~ M, data = Group_Quantity)

# Log version
model3 <- lm(logwords ~ M, data = Group_Quantity)
model4 <- lm(logsents ~ M, data = Group_Quantity)

# Significance between M and V ESG regulations

# Create a sub sample
ESG_Group_Quantity <- Group_Quantity[Group_Quantity$GROUP_TYPE=="ESG", ]

# Significance between M and V (group level)
model5 <- lm(totalwords ~ M, data = ESG_Group_Quantity)
model6 <- lm(sentences ~ M, data = ESG_Group_Quantity)

# Log version
model7 <- lm(logwords ~ M, data = ESG_Group_Quantity)
model8 <- lm(logsents ~ M, data = ESG_Group_Quantity)

# Results
summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
summary(model6)
summary(model7)
summary(model8)
```

## Readability
This section analyzes the differences in readability score between groups. First, there are 7 out of of 70 cases removed where the amount of non-words > 0. This is an indication that the software was not able to correctly identify sentences and words. This is probably due to long lists where terms are summed up, but not separated by a punctuation mark. 
```{r}
Readability <- Descriptive_Data[Descriptive_Data$GROUP_ID!="2"& Descriptive_Data$GROUP_ID!="4"& Descriptive_Data$GROUP_ID!="17"& Descriptive_Data$GROUP_ID!="20"& Descriptive_Data$GROUP_ID!="21"& Descriptive_Data$GROUP_ID!="23"& Descriptive_Data$GROUP_ID!="31", ]

Readability <- Readability[Readability$GROUP_ID!="42" & Readability$GROUP_ID!="43" & Readability$GROUP_ID!="44", ]
```

First, average readability between mandatory and voluntary documents is examined, irrespective of ESG type. 
```{r}
Readability_Total <- Readability %>%
  group_by(M) %>% 
  summarize(average_gl=mean(gl),
            average_ari=mean(ari),
            average_smog=mean(smog),
            average_cl=mean(cl),
            med_gl=median(gl),
            med_ari=median(ari),
            med_smog=median(smog),
            med_cl=median(cl))%>% ungroup()

Readability_Total
```

This difference is also tested for significance (and also with log).
```{r}
# Log transform variables
Readability$log_gl <- log(Readability$gl)
Readability$log_ari <- log(Readability$ari)
Readability$log_smog <- log(Readability$smog)
Readability$log_cl <- log(Readability$cl)

# Test for significance
model10 <- lm(gl~M, data = Readability)
model11 <- lm(log_gl~M, data = Readability)

model12 <- lm(ari~M, data = Readability)
model13 <- lm(log_ari~M, data = Readability)

model14 <- lm(smog~M, data = Readability)
model15 <- lm(log_smog~M, data = Readability)

model16 <- lm(cl~M, data = Readability)
model17 <- lm(log_cl~M, data = Readability)

summary(model10)
summary(model11)
summary(model12)
summary(model13)
summary(model14)
summary(model15)
summary(model16)
summary(model17)
```

While for quantity it is irrelevant to look at quantity differences at document level (as some documents only cover certain topics), it is relevant to do this for readability, as this measure is not influenced by the absolute quantity. 
```{r}
Readability_DOC <- Readability %>%
  group_by(DOC_TYPE, M) %>% 
  summarize(average_gl=mean(gl),
            average_ari=mean(ari),
            average_smog=mean(smog),
            average_cl=mean(cl),
            med_gl=median(gl),
            med_ari=median(ari),
            med_smog=median(smog),
            med_cl=median(cl))%>% ungroup()

Readability_DOC
```

Also, the significance between certain groups on doc level is examined. These are ESG(M)-ESG(V), ESG(M)-G(M), ESG(V)-E(V)
```{r}
# Log transform variables
Readability$log_gl <- log(Readability$gl)
Readability$log_ari <- log(Readability$ari)
Readability$log_smog <- log(Readability$smog)
Readability$log_cl <- log(Readability$cl)

# Create sub sample
ESG_Readability_DOC <- Readability[Readability$DOC_TYPE=="ESG", ]
M_Readability_DOC <- Readability[Readability$M=="1" & Readability$DOC_TYPE=="ESG" & Readability$DOC_TYPE=="G", ]
V_Readability_DOC <- Readability[Readability$M=="0" & Readability$DOC_TYPE=="ESG" & Readability$DOC_TYPE=="E", ]

# Test for significance - ESG M vs ESG V
model101 <- lm(gl~M, data = ESG_Readability_DOC)
model111 <- lm(log_gl~M, data = ESG_Readability_DOC)

model121 <- lm(ari~M, data = ESG_Readability_DOC)
model131 <- lm(log_ari~M, data = ESG_Readability_DOC)

model141 <- lm(smog~M, data = ESG_Readability_DOC)
model151 <- lm(log_smog~M, data = ESG_Readability_DOC)

model161 <- lm(cl~M, data = ESG_Readability_DOC)
model171 <- lm(log_cl~M, data = ESG_Readability_DOC)

summary(model101)
summary(model111)
summary(model121)
summary(model131)
summary(model141)
summary(model151)
summary(model161)
summary(model171)

# Test for significance - ESG M vs G M
model102 <- lm(gl~DOC_TYPE, data = M_Readability_DOC)
model112 <- lm(log_gl~DOC_TYPE, data = M_Readability_DOC)

model122 <- lm(ari~DOC_TYPE, data = M_Readability_DOC)
model132 <- lm(log_ari~DOC_TYPE, data = M_Readability_DOC)

model142 <- lm(smog~DOC_TYPE, data = M_Readability_DOC)
model152 <- lm(log_smog~DOC_TYPE, data = M_Readability_DOC)

model162 <- lm(cl~DOC_TYPE, data = M_Readability_DOC)
model172 <- lm(log_cl~DOC_TYPE, data = M_Readability_DOC)

summary(model102)
summary(model112)
summary(model122)
summary(model132)
summary(model142)
summary(model152)
summary(model162)
summary(model172)


# Test for significance - ESG V vs E V
model103 <- lm(gl~DOC_TYPE, data = V_Readability_DOC)
model113 <- lm(log_gl~DOC_TYPE, data = V_Readability_DOC)

model123 <- lm(ari~DOC_TYPE, data = V_Readability_DOC)
model133 <- lm(log_ari~DOC_TYPE, data = V_Readability_DOC)

model143 <- lm(smog~DOC_TYPE, data = V_Readability_DOC)
model153 <- lm(log_smog~DOC_TYPE, data = V_Readability_DOC)

model163 <- lm(cl~DOC_TYPE, data = V_Readability_DOC)
model173 <- lm(log_cl~DOC_TYPE, data = V_Readability_DOC)

summary(model103)
summary(model113)
summary(model123)
summary(model133)
summary(model143)
summary(model153)
summary(model163)
summary(model173)
```

Subsequently, the same analysis is performed on a group level. 
```{r}
# Group the data by Group_ID
Group_Readability <- Readability %>%
  group_by(GROUP_ID, GROUP_TYPE, M) %>%
  summarize(gl=mean(gl),
            ari=mean(ari),
            smog=mean(smog),
            cl=mean(cl))%>% ungroup()

# Remove Group ID 42, 43, 44, as they do not contain ESG regulations (only key ESG metrics)
Group_Readability <- Group_Readability[Group_Readability$GROUP_ID!="42" & Group_Readability$GROUP_ID!="43" & Group_Readability$GROUP_ID!="44", ]
Group_Readability <- droplevels(Group_Readability)

# Get summary statistics 
Group_R_Stats <- Group_Readability %>%                              
  group_by(GROUP_TYPE, M) %>% 
  summarize(med_gl=median(gl),
            med_ari=median(ari),
            med_smog=median(smog),
            med_cl=median(cl),
            average_gl=mean(gl),
            average_ari=mean(ari),
            average_smog=mean(smog),
            average_cl=mean(cl)) %>% ungroup()

Group_R_Stats
```

Attach Region to the group and doc level analysis, to look for interesting patterns. 
```{r}
Readability_DOC <- merge(Readability_DOC, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
Group_Readability <- merge(Group_Readability, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
```

Lastly, the significance is tested within the group readability. 
```{r}
# Log transform variables
Group_Readability$log_gl <- log(Group_Readability$gl)
Group_Readability$log_ari <- log(Group_Readability$ari)
Group_Readability$log_smog <- log(Group_Readability$smog)
Group_Readability$log_cl <- log(Group_Readability$cl)

# Test for significance - M vs V
model1011 <- lm(gl~M, data = Group_Readability)
model1111 <- lm(log_gl~M, data = Group_Readability)

model1211 <- lm(ari~M, data = Group_Readability)
model1311 <- lm(log_ari~M, data = Group_Readability)

model1411 <- lm(smog~M, data = Group_Readability)
model1511 <- lm(log_smog~M, data = Group_Readability)

model1611 <- lm(cl~M, data = Group_Readability)
model1711 <- lm(log_cl~M, data = Group_Readability)

summary(model1011)
summary(model1111)
summary(model1211)
summary(model1311)
summary(model1411)
summary(model1511)
summary(model1611)
summary(model1711)

# Create sub sample
ESG_Group_Readability <- Group_Readability[Group_Readability$GROUP_TYPE=="ESG", ]
M_Group_Readability <- Group_Readability[Group_Readability$M=="1", ]
V_Group_Readability <- Group_Readability[Group_Readability$M=="0", ]

# Test for significance - ESG M vs ESG V
modelx101 <- lm(gl~M, data = ESG_Group_Readability)
modelx111 <- lm(log_gl~M, data = ESG_Group_Readability)

modelx121 <- lm(ari~M, data = ESG_Group_Readability)
modelx131 <- lm(log_ari~M, data = ESG_Group_Readability)

modelx141 <- lm(smog~M, data = ESG_Group_Readability)
modelx151 <- lm(log_smog~M, data = ESG_Group_Readability)

modelx161 <- lm(cl~M, data = ESG_Group_Readability)
modelx171 <- lm(log_cl~M, data = ESG_Group_Readability)

summary(modelx101)
summary(modelx111)
summary(modelx121)
summary(modelx131)
summary(modelx141)
summary(modelx151)
summary(modelx161)
summary(modelx171)

# Test for significance - ESG M vs G M
modelx102 <- lm(gl~GROUP_TYPE, data = M_Group_Readability)
modelx112 <- lm(log_gl~GROUP_TYPE, data = M_Group_Readability)

modelx122 <- lm(ari~GROUP_TYPE, data = M_Group_Readability)
modelx132 <- lm(log_ari~GROUP_TYPE, data = M_Group_Readability)

modelx142 <- lm(smog~GROUP_TYPE, data = M_Group_Readability)
modelx152 <- lm(log_smog~GROUP_TYPE, data = M_Group_Readability)

modelx162 <- lm(cl~GROUP_TYPE, data = M_Group_Readability)
modelx172 <- lm(log_cl~GROUP_TYPE, data = M_Group_Readability)

summary(modelx102)
summary(modelx112)
summary(modelx122)
summary(modelx132)
summary(modelx142)
summary(modelx152)
summary(modelx162)
summary(modelx172)


# Test for significance - ESG V vs E V
modelx103 <- lm(gl~GROUP_TYPE, data = V_Group_Readability)
modelx113 <- lm(log_gl~GROUP_TYPE, data = V_Group_Readability)

modelx123 <- lm(ari~GROUP_TYPE, data = V_Group_Readability)
modelx133 <- lm(log_ari~GROUP_TYPE, data = V_Group_Readability)

modelx143 <- lm(smog~GROUP_TYPE, data = V_Group_Readability)
modelx153 <- lm(log_smog~GROUP_TYPE, data = V_Group_Readability)

modelx163 <- lm(cl~GROUP_TYPE, data = V_Group_Readability)
modelx173 <- lm(log_cl~GROUP_TYPE, data = V_Group_Readability)

summary(modelx103)
summary(modelx113)
summary(modelx123)
summary(modelx133)
summary(modelx143)
summary(modelx153)
summary(modelx163)
summary(modelx173)
```

#H2. Linguistic Characteristics: Restrictiveness
First, the total number of restrictive words is divided by the total number of words. This prevents a bias where large texts already contain a larger portion of restrictive words. Afterwards, this number is mulitplied by 1000 for better interpretation. So, amount of restrictive words per 1000 words is the new measure that has been created. 
```{r}
R_Data <- Descriptive_Data

R_Data <- R_Data[R_Data$GROUP_ID!="42" & R_Data$GROUP_ID!="43" & R_Data$GROUP_ID!="44", ]

R_Data$negative_strong <- 1000* R_Data$negative_strong/R_Data$totalwords
R_Data$positive_strong <-  1000* R_Data$positive_strong/R_Data$totalwords
R_Data$exemption <-  1000* R_Data$exemption/R_Data$totalwords
R_Data$example <-  1000* R_Data$example/R_Data$totalwords
R_Data$restriction <-  1000* R_Data$restriction/R_Data$totalwords
R_Data$advice <-  1000* R_Data$advice/R_Data$totalwords
R_Data$action<-  1000* R_Data$action/R_Data$totalwords
R_Data$framework<-  1000* R_Data$framework/R_Data$totalwords
```

A deep dive analysis is also done to see which framework is mentioned most of all the 5 frameworks and the Sustainability Development Goals (cdp cdsb gri iirc sasb tcfd sdg)
```{r}
R_Data$cdp <-  1000* R_Data$cdp/R_Data$totalwords
R_Data$cdsb <-  1000* R_Data$cdsb/R_Data$totalwords
R_Data$gri <-  1000* R_Data$gri/R_Data$totalwords
R_Data$sasb<-  1000* R_Data$sasb/R_Data$totalwords
R_Data$tcfd <-  1000* R_Data$tcfd/R_Data$totalwords
R_Data$iirc <-  1000* R_Data$iirc/R_Data$totalwords
R_Data$sdg <-  1000* R_Data$sdg/R_Data$totalwords
```

Next, the same analysis is done as for readability. So, first the overall difference between mandatory and voluntary documents. Then, the differences between documents, while looking at subgroups. Analysis on a document level is done in addition to a group analysis, because sometimes the result in a group can be heavily influenced by one specific document. Lastly, the difference between document groups. Groups are documents that apply to the same source and to the same region. This last measure can give an indication into international convergence. Also, by looking at groups, it can be controlled for country factors. 

First the difference between mandatory and voluntary documents is examined, irrespective of ESG type. 
```{r}
R_Total <- R_Data %>%
  group_by(M) %>% 
  summarize(average_negative_strong=mean(negative_strong),
            average_positive_strong=mean(positive_strong),
            average_exemption=mean(exemption),
            average_example=mean(example),
            average_restriction=mean(restriction),
            average_advice=mean(advice),
            average_action=mean(action),
            average_framework=mean(framework),
            average_cdp=mean(cdp),
            average_cdsb=mean(cdsb),
            average_gri=mean(gri),
            average_sasb=mean(sasb),
            average_tcfd=mean(tcfd),
            average_iirc=mean(iirc),
            average_sdg=mean(sdg),
            median_negative_strong=median(negative_strong),
            median_positive_strong=median(positive_strong),
            median_exemption=median(exemption),
            median_example=median(example),
            median_restriction=median(restriction),
            median_advice=median(advice),
            median_action=median(action),
            median_framework=median(framework),
            median_cdp=median(cdp),
            median_cdsb=median(cdsb),
            median_gri=median(gri),
            median_sasb=median(sasb),
            median_tcfd=median(tcfd),
            median_iirc=median(iirc),
            median_sdg=median(sdg)) %>% ungroup()

R_Total
```

This difference is also tested for significance
```{r}
# Test for significance

# Overall
rmodel10 <- lm(negative_strong~M, data = R_Data)
rmodel11 <- lm(positive_strong~M, data = R_Data)
rmodel12 <- lm(exemption~M, data = R_Data)
rmodel13 <- lm(example~M, data = R_Data)
rmodel14 <- lm(retriction~M, data = R_Data)
rmodel15 <- lm(advice~M, data = R_Data)
rmodel16 <- lm(action~M, data = R_Data)
rmodel17 <- lm(framework~M, data = R_Data)

#frameworks separated
frmodel11 <- lm(cdp~M, data = R_Data)
frmodel12 <- lm(cdsb~M, data = R_Data)
frmodel13 <- lm(gri~M, data = R_Data)
frmodel14 <- lm(sasb~M, data = R_Data)
frmodel15 <- lm(tcfd~M, data = R_Data)
frmodel16 <- lm(iirc~M, data = R_Data)
frmodel17 <- lm(sdg~M, data = R_Data)

summary(rmodel10)
summary(rmodel11)
summary(rmodel12)
summary(rmodel13)
summary(rmodel14)
summary(rmodel15)
summary(rmodel16)
summary(rmodel17)

summary(frmodel11)
summary(frmodel12)
summary(frmodel13)
summary(frmodel14)
summary(frmodel15)
summary(frmodel16)
summary(frmodel17)
```

While for quantity it is irrelevant to look at quantity differences at document level (as some documents only cover certain topics), it is relevant to do this for restrictiveness of words, as this measure is not influenced by another document in the same group (as is the case for analysis on doc group level). 
```{r}
R_DOC <- R_Data %>%
  group_by(DOC_TYPE, M) %>% 
  summarize(average_negative_strong=mean(negative_strong),
            average_positive_strong=mean(positive_strong),
            average_exemption=mean(exemption),
            average_example=mean(example),
            average_restriction=mean(restriction),
            average_advice=mean(advice),
            average_action=mean(action),
            average_framework=mean(framework),
            average_cdp=mean(cdp),
            average_cdsb=mean(cdsb),
            average_gri=mean(gri),
            average_sasb=mean(sasb),
            average_tcfd=mean(tcfd),
            average_iirc=mean(iirc),
            average_sdg=mean(sdg),
            median_negative_strong=median(negative_strong),
            median_positive_strong=median(positive_strong),
            median_exemption=median(exemption),
            median_example=median(example),
            median_restriction=median(restriction),
            median_advice=median(advice),
            median_action=median(action),
            median_framework=median(framework),
            median_cdp=median(cdp),
            median_cdsb=median(cdsb),
            median_gri=median(gri),
            median_sasb=median(sasb),
            median_tcfd=median(tcfd),
            median_iirc=median(iirc),
            median_sdg=median(sdg))%>% ungroup()

R_DOC
```

Also, the significance between certain groups on doc level is examined. These are ESG(M)-ESG(V), ESG(M)-G(M), ESG(V)-E(V)
```{r}
# Create sub sample
ESG_R_DOC <- R_Data[R_Data$DOC_TYPE=="ESG", ]
M_R_DOC <- R_Data[R_Data$M=="1" & R_Data$DOC_TYPE=="ESG" & R_Data$DOC_TYPE=="G", ]
V_R_DOC <- R_Data[R_Data$M=="0" & R_Data$DOC_TYPE=="ESG" & R_Data$DOC_TYPE=="E", ]

# ESG mandatory vs ESG Voluntary #########################
# Overall
ermodel10 <- lm(negative_strong~M, data = ESG_R_DOC)
ermodel11 <- lm(positive_strong~M, data = ESG_R_DOC)
ermodel12 <- lm(exemption~M, data = ESG_R_DOC)
ermodel13 <- lm(example~M, data = ESG_R_DOC)
ermodel14 <- lm(retriction~M, data = ESG_R_DOC)
ermodel15 <- lm(advice~M, data = ESG_R_DOC)
ermodel16 <- lm(action~M, data = ESG_R_DOC)
ermodel17 <- lm(framework~M, data = ESG_R_DOC)

#frameworks separated
fermodel11 <- lm(cdp~M, data = ESG_R_DOC)
fermodel12 <- lm(cdsb~M, data = ESG_R_DOC)
fermodel13 <- lm(gri~M, data = ESG_R_DOC)
fermodel14 <- lm(sasb~M, data = ESG_R_DOC)
fermodel15 <- lm(tcfd~M, data = ESG_R_DOC)
fermodel16 <- lm(iirc~M, data = ESG_R_DOC)
fermodel17 <- lm(sdg~M, data = ESG_R_DOC)

summary(ermodel10)
summary(ermodel11)
summary(ermodel12)
summary(ermodel13)
summary(ermodel14)
summary(ermodel15)
summary(ermodel16)
summary(ermodel17)

summary(fermodel11)
summary(fermodel12)
summary(fermodel13)
summary(fermodel14)
summary(fermodel15)
summary(fermodel16)
summary(fermodel17)

# ESG mandatory vs G Mandatory #########################
# Overall
ermodelx10 <- lm(negative_strong~M, data = M_R_DOC)
ermodelx11 <- lm(positive_strong~M, data = M_R_DOC)
ermodelx12 <- lm(exemption~M, data = M_R_DOC)
ermodelx13 <- lm(example~M, data = M_R_DOC)
ermodelx14 <- lm(retriction~M, data = M_R_DOC)
ermodelx15 <- lm(advice~M, data = M_R_DOC)
ermodelx16 <- lm(action~M, data = M_R_DOC)
ermodelx17 <- lm(framework~M, data = M_R_DOC)

#frameworks separated
fermodelx11 <- lm(cdp~M, data = M_R_DOC)
fermodelx12 <- lm(cdsb~M, data = M_R_DOC)
fermodelx13 <- lm(gri~M, data = M_R_DOC)
fermodelx14 <- lm(sasb~M, data = M_R_DOC)
fermodelx15 <- lm(tcfd~M, data = M_R_DOC)
fermodelx16 <- lm(iirc~M, data = M_R_DOC)
fermodelx17 <- lm(sdg~M, data = M_R_DOC)

summary(ermodelx10)
summary(ermodelx11)
summary(ermodelx12)
summary(ermodelx13)
summary(ermodelx14)
summary(ermodelx15)
summary(ermodelx16)
summary(ermodelx17)

summary(fermodelx11)
summary(fermodelx12)
summary(fermodelx13)
summary(fermodelx14)
summary(fermodelx15)
summary(fermodelx16)
summary(fermodelx17)

# ESG voluntary vs E voluntary #########################
# Overall
ermodelyx10 <- lm(negative_strong~M, data = V_R_DOC)
ermodelyx11 <- lm(positive_strong~M, data = V_R_DOC)
ermodelyx12 <- lm(exemption~M, data = V_R_DOC)
ermodelyx13 <- lm(example~M, data = V_R_DOC)
ermodelyx14 <- lm(retriction~M, data = V_R_DOC)
ermodelyx15 <- lm(advice~M, data = V_R_DOC)
ermodelyx16 <- lm(action~M, data = V_R_DOC)
ermodelyx17 <- lm(framework~M, data = V_R_DOC)

#frameworks separated
fermodelyx11 <- lm(cdp~M, data = V_R_DOC)
fermodelyx12 <- lm(cdsb~M, data = V_R_DOC)
fermodelyx13 <- lm(gri~M, data = V_R_DOC)
fermodelyx14 <- lm(sasb~M, data = V_R_DOC)
fermodelyx15 <- lm(tcfd~M, data = V_R_DOC)
fermodelyx16 <- lm(iirc~M, data = V_R_DOC)
fermodelyx17 <- lm(sdg~M, data = V_R_DOC)

summary(ermodelyx10)
summary(ermodelyx11)
summary(ermodelyx12)
summary(ermodelyx13)
summary(ermodelyx14)
summary(ermodelyx15)
summary(ermodelyx16)
summary(ermodelyx17)

summary(fermodelyx11)
summary(fermodelyx12)
summary(fermodelyx13)
summary(fermodelyx14)
summary(fermodelyx15)
summary(fermodelyx16)
summary(fermodelyx17)
```

Subsequently, the same analysis is performed on a group level. 
```{r}
# Group the data by Group_ID
Group_R <- R_Data %>%
  group_by(GROUP_ID, GROUP_TYPE, M) %>%
  summarize(negative_strong=sum(negative_strong),
            positive_strong=sum(positive_strong),
            exemption=sum(exemption),
            example=sum(example),
            restriction=sum(restriction),
            advice=sum(advice),
            action=sum(action),
            framework=sum(framework),
            cdp=sum(cdp),
            cdsb=sum(cdsb),
            gri=sum(gri),
            sasb=sum(sasb),
            tcfd=sum(tcfd),
            iirc=sum(iirc),
            sdg=sum(sdg))%>% ungroup()

# Get summary statistics 
Group_Restrictions_Stats <- Group_R %>%                              
  group_by(GROUP_TYPE, M) %>% 
  summarize(average_negative_strong=mean(negative_strong),
            average_positive_strong=mean(positive_strong),
            average_exemption=mean(exemption),
            average_example=mean(example),
            average_restriction=mean(restriction),
            average_advice=mean(advice),
            average_action=mean(action),
            average_framework=mean(framework),
            average_cdp=mean(cdp),
            average_cdsb=mean(cdsb),
            average_gri=mean(gri),
            average_sasb=mean(sasb),
            average_tcfd=mean(tcfd),
            average_iirc=mean(iirc),
            average_sdg=mean(sdg),
            median_negative_strong=median(negative_strong),
            median_positive_strong=median(positive_strong),
            median_exemption=median(exemption),
            median_example=median(example),
            median_restriction=median(restriction),
            median_advice=median(advice),
            median_action=median(action),
            median_framework=median(framework),
            median_cdp=median(cdp),
            median_cdsb=median(cdsb),
            median_gri=median(gri),
            median_sasb=median(sasb),
            median_tcfd=median(tcfd),
            median_iirc=median(iirc),
            median_sdg=median(sdg)) %>% ungroup()

Group_Restrictions_Stats
```

Attach Region to the group and doc level analysis, to look for interesting patterns. 
```{r}
R_Data <- merge(R_Data, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
Group_R <- merge(Group_R, Country_ID, by.x = "GROUP_ID", by.y = "GROUP_ID", all.x = TRUE, all.y = FALSE)
```

Lastly, the significance is tested on a group level.  
```{r}
# Test for significance - M vs V
# Overall
rmodelq10 <- lm(negative_strong~M, data = Group_R)
rmodelq11 <- lm(positive_strong~M, data = Group_R)
rmodelq12 <- lm(exemption~M, data = Group_R)
rmodelq13 <- lm(example~M, data = Group_R)
rmodelq14 <- lm(retriction~M, data = Group_R)
rmodelq15 <- lm(advice~M, data = Group_R)
rmodelq16 <- lm(action~M, data = Group_R)
rmodelq17 <- lm(framework~M, data = Group_R)

#frameworks separated
frmodelq11 <- lm(cdp~M, data = Group_R)
frmodelq12 <- lm(cdsb~M, data = Group_R)
frmodelq13 <- lm(gri~M, data = Group_R)
frmodelq14 <- lm(sasb~M, data = Group_R)
frmodelq15 <- lm(tcfd~M, data = Group_R)
frmodelq16 <- lm(iirc~M, data = Group_R)
frmodelq17 <- lm(sdg~M, data = Group_R)

summary(rmodelq10)
summary(rmodelq11)
summary(rmodelq12)
summary(rmodelq13)
summary(rmodelq14)
summary(rmodelq15)
summary(rmodelq16)
summary(rmodelq17)

summary(frmodelq11)
summary(frmodelq12)
summary(frmodelq13)
summary(frmodelq14)
summary(frmodelq15)
summary(frmodelq16)
summary(frmodelq17)

# Test for significance > subsamples
# Create sub sample
ESG_RES_DOC <- Group_R[Group_R$DOC_TYPE=="ESG", ]
M_RES_DOC <- Group_R[Group_R$M=="1" & Group_R$DOC_TYPE=="ESG" & Group_R$DOC_TYPE=="G", ]
V_RES_DOC <- Group_R[Group_R$M=="0" & Group_R$DOC_TYPE=="ESG" & Group_R$DOC_TYPE=="E", ]

# ESG mandatory vs ESG Voluntary #########################
# Overall
ermodelw10 <- lm(negative_strong~M, data = ESG_RES_DOC)
ermodelw11 <- lm(positive_strong~M, data = ESG_RES_DOC)
ermodelw12 <- lm(exemption~M, data = ESG_RES_DOC)
ermodelw13 <- lm(example~M, data = ESG_RES_DOC)
ermodelw14 <- lm(retriction~M, data = ESG_RES_DOC)
ermodelw15 <- lm(advice~M, data = ESG_RES_DOC)
ermodelw16 <- lm(action~M, data = ESG_RES_DOC)
ermodelw17 <- lm(framework~M, data = ESG_RES_DOC)

#frameworks separated
fermodelw11 <- lm(cdp~M, data = ESG_RES_DOC)
fermodelw12 <- lm(cdsb~M, data = ESG_RES_DOC)
fermodelw13 <- lm(gri~M, data = ESG_RES_DOC)
fermodelw14 <- lm(sasb~M, data = ESG_RES_DOC)
fermodelw15 <- lm(tcfd~M, data = ESG_RES_DOC)
fermodelw16 <- lm(iirc~M, data = ESG_RES_DOC)
fermodelw17 <- lm(sdg~M, data = ESG_RES_DOC)

summary(ermodelw10)
summary(ermodelw11)
summary(ermodelw12)
summary(ermodelw13)
summary(ermodelw14)
summary(ermodelw15)
summary(ermodelw16)
summary(ermodelw17)

summary(fermodelw11)
summary(fermodelw12)
summary(fermodelw13)
summary(fermodelw14)
summary(fermodelw15)
summary(fermodelw16)
summary(fermodelw17)

# ESG mandatory vs G Mandatory #########################
# Overall
ermodeldx10 <- lm(negative_strong~M, data = M_RES_DOC)
ermodeldx11 <- lm(positive_strong~M, data = M_RES_DOC)
ermodeldx12 <- lm(exemption~M, data = M_RES_DOC)
ermodeldx13 <- lm(example~M, data = M_RES_DOC)
ermodeldx14 <- lm(retriction~M, data = M_RES_DOC)
ermodeldx15 <- lm(advice~M, data = M_RES_DOC)
ermodeldx16 <- lm(action~M, data = M_RES_DOC)
ermodeldx17 <- lm(framework~M, data = M_RES_DOC)

#frameworks separated
fermodeldx11 <- lm(cdp~M, data = M_RES_DOC)
fermodeldx12 <- lm(cdsb~M, data = M_RES_DOC)
fermodeldx13 <- lm(gri~M, data = M_RES_DOC)
fermodeldx14 <- lm(sasb~M, data = M_RES_DOC)
fermodeldx15 <- lm(tcfd~M, data = M_RES_DOC)
fermodeldx16 <- lm(iirc~M, data = M_RES_DOC)
fermodeldx17 <- lm(sdg~M, data = M_RES_DOC)

summary(ermodeldx10)
summary(ermodeldx11)
summary(ermodeldx12)
summary(ermodeldx13)
summary(ermodeldx14)
summary(ermodeldx15)
summary(ermodeldx16)
summary(ermodeldx17)

summary(fermodeldx11)
summary(fermodeldx12)
summary(fermodeldx13)
summary(fermodeldx14)
summary(fermodeldx15)
summary(fermodeldx16)
summary(fermodeldx17)

# ESG voluntary vs E voluntary #########################
# Overall
ermodelkyx10 <- lm(negative_strong~M, data = V_RES_DOC)
ermodelkyx11 <- lm(positive_strong~M, data = V_RES_DOC)
ermodelkyx12 <- lm(exemption~M, data = V_RES_DOC)
ermodelkyx13 <- lm(example~M, data = V_RES_DOC)
ermodelkyx14 <- lm(retriction~M, data = V_RES_DOC)
ermodelkyx15 <- lm(advice~M, data = V_RES_DOC)
ermodelkyx16 <- lm(action~M, data = V_RES_DOC)
ermodelkyx17 <- lm(framework~M, data = V_RES_DOC)

#frameworks separated
fermodelkyx11 <- lm(cdp~M, data = V_RES_DOC)
fermodelkyx12 <- lm(cdsb~M, data = V_RES_DOC)
fermodelkyx13 <- lm(gri~M, data = V_RES_DOC)
fermodelkyx14 <- lm(sasb~M, data = V_RES_DOC)
fermodelkyx15 <- lm(tcfd~M, data = V_RES_DOC)
fermodelkyx16 <- lm(iirc~M, data = V_RES_DOC)
fermodelkyx17 <- lm(sdg~M, data = V_RES_DOC)

summary(ermodelkyx10)
summary(ermodelkyx11)
summary(ermodelkyx12)
summary(ermodelkyx13)
summary(ermodelkyx14)
summary(ermodelkyx15)
summary(ermodelkyx16)
summary(ermodelkyx17)

summary(fermodelkyx11)
summary(fermodelkyx12)
summary(fermodelkyx13)
summary(fermodelkyx14)
summary(fermodelkyx15)
summary(fermodelkyx16)
summary(fermodelkyx17)
```
